---
title: "Male LBN-ALPS data"
output:
  word_document: default
  html_notebook: default
df-print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# knitr::opts_chunk$set(fig.width=11.5, fig.height=5) 
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
source("./01-scripts/04-filter-datasets.R")
source("./01-scripts/05-make-LBN-plots-manuscript.R")
source("./01-scripts/06-make-LBN-ANOVAs_noLitter.R")
```

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

These mice had very small testicular mass

```{r}
acuteStressFilteredMales <- acuteStressFilteredMales %>%
  filter(
    ! mouseID %in% c(7012, 7032)
  )

maleMatUsedForALPS <- maturationFiltered %>%
  filter(
    mouseID %in% acuteStressFilteredMales$mouseID
  )
```


# AGD for males used for ALPS studies
```{r}
maleMatUsedForALPS %>%
  group_by(
    earlyLifeTrt
  ) %>%
  summarize(
    n()
    , litters = length(unique(damID))
  )
```

```{r}
maleMatUsedForALPS %>%
  scatterPlotLBN(
    yVar = AGD_adult
    , yLab = getNiceName(expr(AGD_adult))
    , textSize = 16
    , dotSize = 3
  )
```
```{r}
lmm <- maleMatUsedForALPS %>%
  runLMM(
    AGD_adult ~ earlyLifeTrt + (1|damID)
  )

summary(lmm$model)

lmm$anova %>% formatLMM_anova()
```





```{r}
acuteStressFilteredMales %>%
  group_by(comboTrt) %>%
  summarize(
    n()
    , litters = length(unique(damID))
  )
```

# Body mass am

There's an effect of early-life treatment according to the ANOVA, not quite significant with the coefficients t-test. Double check the degrees of feedom calculation here

There's a highly significant result of effect of adult treatment, which there shouldn't be because treatment hasn't occurred yet. It's not a massive difference biologically, but because the dam is factored in, I think the differences within the litter get magnified in terms of being able to attribute the differences to adult treatment in the model. Unfortunate, but I think it's real in terms of the stats. 

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    Body_mass_AM
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(Body_mass_AM)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    Body_mass_AM ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Body_mass_AM
    , between = c(earlyLifeTrt, adultTrt)
  )
```

```{r}

```



# Body mass PM

Here, the effect of adult trt goes away, early-life is still significant
But, I don't think that this is the presentation that makes the most sense because we know that the paradigm changes body mass

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    Body_mass_sac
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(Body_mass_sac)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    Body_mass_sac ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Body_mass_sac
    , between = c(earlyLifeTrt, adultTrt)
  )
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Body_mass_sac
    , between = c(earlyLifeTrt, adultTrt)
  )
```

# Body mass change

Adult stress mice lose more mass during the day. No interaction with LBN

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    bodyMass_diff
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(bodyMass_diff)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    bodyMass_diff ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = bodyMass_diff
    , between = c(earlyLifeTrt, adultTrt)
  )
```

# Adrenal mass

The mass itself without accounting for body mass is not different with treatments

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    Adrenal_mass
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(Adrenal_mass)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    Adrenal_mass ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Adrenal_mass
    , between = c(earlyLifeTrt, adultTrt)
  )
```

## Adrenal mass by AM body mass

Adrenal mass corrected for AM body mass is not different

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    Adrenal_mass_perBodyAM_g
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(Adrenal_mass_perBodyAM_g)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    Adrenal_mass_perBodyAM_g ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Adrenal_mass_perBodyAM_g
    , between = c(earlyLifeTrt, adultTrt)
  )
```
## Adrenal mass by PM body mass

Adrenal mass corrected for PM body mass is not different

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    Adrenal_mass_perBody_g
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(Adrenal_mass_perBody_g)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    Adrenal_mass_perBody_g ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Adrenal_mass_perBody_g
    , between = c(earlyLifeTrt, adultTrt)
  )
```

# Testicular mass

There are two mice with very small testicular masses. Going to filter them out - did above, so that they're not included in any of these calculations. Determine if that's what we want to do long-term

mouseIDs 7012 and 7032

There's an effect of both adult treatment and early-life treatment, but no interaction

```{r eval=FALSE, include=FALSE}
acuteStressFilteredMales %>%
  filter(
    Gonad_mass < 150
  )
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    Gonad_mass
  ) %>%
  myDisplay()
```
```{r fig.height=4, fig.width=10}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(Gonad_mass)
    , fontSize = 14
    , dotSize = 2.5
  )() +
  ylab("testicular mass (mg)")

flexSave(
  "testicularMass"
  , width = 3
  , height = 4
)
```
Here, there's a very big difference between the significance with the coefficients and the main effects with the ANOVA. I think that this is because the coefficients basically give you the value for just one of the groups, and then you have to adjust with the interaction coefficient, so if there's not an interaction, it could mess with seeing the main effect if both main effects are significant

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    Gonad_mass ~ earlyLifeTrt * adultTrt + (1|damID)
  )

# summary(lmm$model)
# 
# lmm$formated

lmm$anova %>% formatLMM_anova()
```


```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Gonad_mass
    , between = c(earlyLifeTrt, adultTrt)
  )
```

## Testicular mass by AM body mass

Standardizing for AM body mass removes the difference with early-life treatment, but the effect of adult treatment remains

Chronic stress, but reduction in testis size + mass: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4710837/
Reduction in mass: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4971559/

No difference with 30 days restraint in rats: https://obgyn.onlinelibrary.wiley.com/doi/abs/10.1016/0020-7292(88)90277-9

Chronic, abs testes mass decreases, but relative did not change: https://www.nature.com/articles/s41598-017-09943-2

2h restraint for 7 days, no change testes: https://academic.oup.com/humrep/article/14/7/1806/2913158



```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    Gonad_mass_perBodyAM_g
  ) %>%
  myDisplay()
```
```{r fig.height=4, fig.width=10}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(Gonad_mass_perBodyAM_g)
    , fontSize = 14
    , dotSize = 2.5
  )() +
  ylab("testicular mass / body mass (mg/g)")

flexSave(
  "testicularMass_byBodyMass"
  , width = 3
  , height = 4
)
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    Gonad_mass_perBodyAM_g ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Gonad_mass_perBodyAM_g
    , between = c(earlyLifeTrt, adultTrt)
  )
```

## Testicular mass by PM body mass

Standardizing for PM body mass removes the difference with early-life treatment, but the effect of adult treatment remains

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    Gonad_mass_perBody_g
  ) %>%
  myDisplay()
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(Gonad_mass_perBody_g)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    Gonad_mass_perBody_g ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = Gonad_mass_perBody_g
    , between = c(earlyLifeTrt, adultTrt)
  )
```

# Seminal vesicle mass

The mass itself without accounting for body mass is not different with treatments

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    ReproTract_mass
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(ReproTract_mass)
  )()
```
```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    ReproTract_mass ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```


```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = ReproTract_mass
    , between = c(earlyLifeTrt, adultTrt)
  )
```

## Seminal vesicle mass by AM body mass

seminal vesicle mass corrected for AM body mass is higher in LBN males

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    ReproTract_mass_perBodyAM_g
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(ReproTract_mass_perBodyAM_g)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    ReproTract_mass_perBodyAM_g ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = ReproTract_mass_perBodyAM_g
    , between = c(earlyLifeTrt, adultTrt)
  )
```

## Seminal vesicle mass by PM body mass

Seminal vesicle mass standarized for PM body mass is higher in LBN animals

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
  meanSummary(
    ReproTract_mass_perBody_g
  )
```
```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  plotCatVarFunc(
    expr(ReproTract_mass_perBody_g)
  )()
```

```{r}
lmm <- acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  runLMM(
    ReproTract_mass_perBody_g ~ earlyLifeTrt * adultTrt + (1|damID)
  )

summary(lmm$model)

lmm$formated

lmm$anova %>% formatLMM_anova()
```

```{r}
acuteStressFilteredMales %>%
  filter(
    !is.na(comboTrt)
  ) %>%
  anova_test(
    dv = ReproTract_mass_perBody_g
    , between = c(earlyLifeTrt, adultTrt)
  )
```