---
title: "Nutella - Cort Admin"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

# Source files

```{r include=FALSE}
# If can't find it, be sure that the directory is the project directory
# Arrow between notebook and settings gear -> Knit directory
source("./01-scripts/01-set-up.R") ## IDK why, but doesn't seem to work the first time in new environment
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "cortAdmin-get-datasets.R"))
```


# Set-up
```{r}
figureNum <- 1

pptBaseName <- makeBaseNameFunc("")

plotFolder <- file.path(plotOutputFolder, "cortAdmin_Jan2023")

imgType <-"png"

exportImg <- exportImg_forPurposeFunc(
  imgType = imgType
  , figNumFunc = pptBaseName
  , plotFolder = plotFolder
  , compType = currentCompType
)

exportFullPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 11.5
  #   , height = 5
  # )
}

exportHalfPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 5.67
  #   , height = 5
  # )
}

exportThirdPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 3.6
  #   , height = 5
  # )
}

exportQuarterPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 3.2
  #   , height = 5
  # )
}

editableImgs <- TRUE
pptAddOneGraph <- function(
    title = slideTitle
    , plot = last_plot()
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_oneGraph(
    officer_ppt, 
    title, 
    plot, 
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddOneTable <- function(
    table
    , title = slideTitle
    , officer_ppt = ppt
    , dontFormat = TRUE
){
  officer_ppt <- addSlide_oneTable(
    officer_ppt, 
    title, 
    table, 
    dontFormat = dontFormat
  )
  return(officer_ppt)
}

pptAddTwoTables <- function(
    table1
    , table2
    , title = slideTitle
    , officer_ppt = ppt
    , dontFormat = TRUE
){
  officer_ppt <- addSlide_twoTables(
    officer_ppt, 
    title, 
    table1, 
    table2,
    dontFormat = dontFormat
  )
  return(officer_ppt)
}

pptUneditAddOneGraph <- function(
    title = slideTitle
    , plot = last_plot()
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_oneGraph(
    officer_ppt, 
    title, 
    plot, 
    makeEditable = FALSE
  )
  return(officer_ppt)
}

pptAddTwoGraphs <- function(
    plot1
    , plot2
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_twoGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2,
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddTwoGraphsMoreLeft <- function(
    plot1
    , plot2
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_twoGraphMoreLeft(
    officer_ppt, 
    title, 
    plot1, 
    plot2,
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddGraphTable <- function(
    plot
    , table
    , title = slideTitle
    , officer_ppt = ppt
    , dontFormat = TRUE
){
  officer_ppt <- addSlide_graphTable(
    officer_ppt, 
    title, 
    plot, 
    table,
    makeEditable = editableImgs
    , dontFormat = dontFormat
    , textSize = textSize
  )
  return(officer_ppt)
}

pptAddFourGraphs <- function(
    plot1
    , plot2
    , plot3
    , plot4
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_fourGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2, 
    plot3,
    plot4,
    makeEditable = editableImgs
    )
  return(officer_ppt)
}

pptAddThreeGraphs <- function(
    plot1
    , plot2
    , plot3
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_threeGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2, 
    plot3,
    makeEditable = editableImgs
    )
  return(officer_ppt)
}

pptAddStats <- function(
    statsText
    , officer_ppt = ppt
){
  officer_ppt <- addStatsToBottom(
    officer_ppt,
    statsText
  )
}

pptAddTwoStats <- function(
    statsText1
    , statsText2
    , officer_ppt = ppt
){
  officer_ppt <- addTwoStatsToGraphs(
    officer_ppt,
    statsText1,
    statsText2
  )
}

pptAddSectionHead <- function(
    title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_sectionHead(
    officer_ppt
    , title
  )
}
```

```{r}
# make powerpoint and title slide
ppt <- read_pptx("genericPPT.pptx")
ppt <- add_slide(ppt, layout = "Title Slide")

# layout_properties(ppt, layout="Title Slide")

titleText <- "Effect of oral corticsterone administration on LH surge and ovulation"

ppt <- ph_with(
  ppt,
  value = titleText
  , location = ph_location_label("Title 1")
)

subText <- paste(dateToday)
ppt <- ph_with(
  ppt,
  value = subText,
  location = ph_location_label("Subtitle 2")
)

# Run this function to save the PPT file to the disk
# On windows, don't run if the PPT file is open
savePPT <- makeSavePPTFunc(
  presPPT = ppt
  , presFolder = plotFolder
  , presFileName = "cortAdmin_data"
  , addDate = TRUE
)
```

# Save data frames

```{r}
BD_samplingSave <- BD_sampling %>%
  relocate(
    starts_with("LH")
    , maxLH
    , timeAtMax
    , surged
    , .after = exclude_hr5.5
  ) %>%
  select(
    - c(
      earTag
      , sacDateOff
      , sacNotesOff
      , dam
      , damGeneration
      , damDOB
      , breedDate
      , sire
      , sireStrain
      , plugDate
      , litterSizeWean
      , cyclingFolderPath
    )
  )

BD_LH_save <- BD_LH %>%
  select(
    mouseID
    , dosage
    , sampleID
    , time
    , LH
    , surged
    , ovulated
    , trust
    
  )

BD_cort_save <- BD_cort %>%
  select(
    mouseID
    , dosage
    , time
    , cort
    , surged
    , ovulated
    , trust
  )

cortAdminPilot <- BD_offspringInfo %>%
  filter(
    Sac_date == as_date("2022-05-26") | Sac_date == as_date("2022-05-27")
  )  %>%
  select(
    - c(
      earTag
      , sacDateOff
      , sacNotesOff
      , dam
      , damGeneration
      , damDOB
      , breedDate
      , sire
      , sireStrain
      , plugDate
      , litterSizeWean
      , cyclingFolderPath
    )
  )

BD_samplingSave
cortAdminPilot
BD_LH_save
BD_cort_save
```



# Determining cort dosage

2 mg/kg corticosterone dosage administered at hours 0, 1, and 3h leads
to similar serum corticosterone levels as the ALPS paradigm

```{r}
BD_comboNutALPS <- rbind(
  BD_cortALPS %>%
    mutate(
      atePrevNutella = NA,
      ateNutella = NA,
      cortNutTrt = adultTrt
    ), 
  BD_cort4 %>% 
    filter(Sac_date == as_date("2022-05-27")) %>%
    mutate(
      cortNutTrt = dosage
    )
)

nutellaALPS_cortPlot <- BD_comboNutALPS %>%
  cortPlot(
    pointSize = 3,
    fontSize = 16,
    plotMean = FALSE, # we don't have enough data yet for mean/se to be helpful
    plotSE = FALSE,
    groupVar = cortNutTrt, # group by the dosage; this is why it needs to be a factor
    xBreaks = c(0, 0.5, 1, 3, 5), # set the axis ticks at these values
    xLabels = waiver(), # label the axis with the actual time values
    lineTypeGuide = "",
    positionDodge = 0.2, #this controls the spread of the data visually
    zoom_y = TRUE,
    ymax = 1000,
    ymin = 0
  ) +
  # facet_wrap(
  #   ~ateAllNutella # this splits the graph by those that did or did not each Nutella
  # ) +
  labs(
    x = "time since 1st administration (h)" # add a title to the x axis
  ) + 
  theme(
    legend.position = "top"
  )  +
  scale_color_manual(
    "treatment",
    labels = c(
      "ALPS" = "ALPS",
      "0" = "0mg/kg",
      "2" = "2mg/kg"
    ),
    values = c(
      "ALPS"="black",
      "0" = "black",
      "2" = "black"
      )
  )+
  scale_fill_manual(
    "treatment",
    labels = c(
      "ALPS" = "ALPS",
      "0" = "0mg/kg",
      "2" = "2mg/kg"
    ),
    values = c(
      "ALPS"="grey80",
      "0" = "white",
      "2" = "black"
      )
  )+
  scale_shape_manual(
    "treatment",
    labels = c(
      "ALPS" = "ALPS",
      "0" = "0mg/kg",
      "2" = "2mg/kg"
    ),
    values = c(
      "ALPS"=23,
      "0" = 21,
      "2" = 21
      )
  ) + scale_linetype_manual(
    "treatment",
    labels = c(
      "ALPS" = "ALPS",
      "0" = "0mg/kg",
      "2" = "2mg/kg"
    ),
    values = c(
      "ALPS"="dotted",
      "0" = "solid",
      "2" = "solid"
    )
  )
```

```{r}
nutellaALPS_cortPlot
fileBaseName <- "pilotNutellaALPS_cortPlot"
slideTitle <- "Oral corticosterone administration recapitulates ALPS serum corticsterone levels"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
BD_comboNutALPS_meanSum <- BD_comboNutALPS %>%
  group_by(
    cortNutTrt
    , time
  ) %>%
  meanSummary(
    cort
  )

BD_comboNutALPS_meanSum
```


# Corticosterone response

```{r}
figureNum <- figureNum + 1
```


```{r}

cortAdminCortDF <- BD_cort %>%
  filter(
    time %in% c(0, 5)
    , is.na(exclude) | exclude == FALSE
    , trust == TRUE
  )

cortAdmin_cort <- cortAdminCortDF %>%
  cortPlot(
    pointSize = 3,
    fontSize = 16,
    groupVar = dosage, # group by the dosage; this is why it needs to be a factor
    lineTypeGuide = c("solid", "dotted"),
    positionDodge = 0.2, #this controls the spread of the data visually
    zoom_y = TRUE,
    ymax = 500,
    ymin = 0
  ) +
  facet_wrap(
    ~ dosage,
    labeller = labeller(dosage = c("0" = "0mg/kg", "2" = "2mg/kg"))
  ) +
  # labs(
  #   x = "time since 1st administration (h)" # add a title to the x axis
  # ) + 
  theme(
    legend.position = "none"
  )  + 
  dosageFillShape()
```


```{r}
cortAdmin_cort
fileBaseName <- "cortAdmin_cort"
slideTitle <- "Oral corticosterone administration increases afternoon corticsterone"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
cortAdminCortDF_meanSum <- cortAdminCortDF %>%
  group_by(
    dosage
    , time
  ) %>%
  meanSummary(cort)

cortAdminCortDF_meanSum
```


```{r}
cortAdminCortAnova <- cortAdminCortDF %>%
  anova_test(
    dv = cort,
    between = dosage,
    within = time,
    wid = mouseID
    , type = 3
  ) %>%
  get_anova_table() %>%
  as_tibble()

cortAdminCortAnova_flx <- cortAdminCortAnova %>%
  formatAnova(16)

cortAdminCortAnovas_postHoc <- cortAdminCortDF %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = cort
    , wid = mouseID
    , between = dosage
    , type = 3
  ) %>%
  adjust_pvalue(
    method = "bonferroni"
  ) %>%
  get_anova_table() %>%
  as_tibble()

cortAdminCortAnovas_postHoc_flx <- cortAdminCortAnovas_postHoc %>%
  formatAdjAnova(16)

cortAdminCortAnova
cortAdminCortAnovas_postHoc

getFText(cortAdminCortAnova, "dosage:time")
```

```{r}
ppt <- pptAddOneTable(
  cortAdminCortDF_meanSum,
  title = slideTitle,
  dontFormat = FALSE
)
ppt <- pptAddTwoTables(
  cortAdminCortAnova_flx,
  cortAdminCortAnovas_postHoc_flx,
  title = slideTitle
)
```

# LH Surge

```{r}
figureNum <- figureNum + 1
```

```{r}
cortAdmin_LH_trust <- BD_LH %>%
  filter(
    trust == TRUE
    , !is.na(LH)
  )
cortAdmin_LHplot <- cortAdmin_LH_trust %>%
  LHPlot_adultTrt(
    trtVar = dosage
    , trtName = "dosage (mg/kg)"
    , trtLineGuide = c("0" = "dotted", "2" = "solid")
    , trtFill = dosageFill()
    , trtColor = dosageColor()
    , fontSize = 16
    , dotSize = 2.5
    , zoom_y = TRUE
    , ymin = 0
    , ymax = 45
  ) + facet_wrap(
    ~ dosage
    , ncol = 2
    , labeller = labeller(
      dosage = c("0" = "0 mg/kg", "2" = "2 mg/kg")
    )
  ) + 
  rremove("legend")
```


```{r}
cortAdmin_LHplot
fileBaseName <- "cortAdmin_LH"
slideTitle <- "Oral corticosterone administration does not alter pattern or amplitude of LH surge"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
cortAdmin_LH_meanSum <- cortAdmin_LH_trust %>%
  mutate(
    relTime = time - 7.5
  ) %>%
  group_by(
    dosage
    , relTime
  ) %>%
  meanSummary(
    LH
  )

cortAdmin_LH_meanSum
```


Note - time and dosage/time are significant on Mauchly's Test for Sphericity.
There is a sphericity corrected version of the ANOVA, still not significant

```{r}
cortAdmin_LH_anova <- cortAdmin_LH_trust %>%
  anova_test(
    dv = LH
    , wid = mouseID
    , between = dosage
    , within = time
    , type = 3
  ) %>%
  get_anova_table() %>%
  as_tibble()

cortAdmin_LH_anova_flx <- cortAdmin_LH_anova %>%
  formatAnova(16)

cortAdmin_LH_anova_flx
```

```{r}
ppt <- pptAddOneTable(
  cortAdmin_LH_meanSum
  , title = slideTitle
  , dontFormat = FALSE
)
ppt <- pptAddOneTable(
  cortAdmin_LH_anova_flx
  , title = slideTitle
)
```

## Max LH

```{r}
cortAdmin_sampling_trust <- BD_sampling %>%
  filter(
    trust == TRUE
    , !is.na(maxLH)
  )

cortAdmin_LHamp <- cortAdmin_sampling_trust %>%
  plotLHAmp_dosage(
    surgeMin = 3
    , textSize = 16
    , dotSize = 3
  )
```

```{r}
cortAdmin_LHamp
fileBaseName <- "cortAdmin_LHamp"
slideTitle <- "Oral corticosterone administration does not alter pattern or amplitude of LH surge"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
cortAdmin_LHamp_meanSum <- cortAdmin_sampling_trust %>%
  group_by(
    dosage
  ) %>%
  meanSummary(maxLH)

cortAdmin_LHamp_bySurged_meanSum <- cortAdmin_sampling_trust %>%
  group_by(
    dosage,
    surged
  ) %>%
  meanSummary(maxLH)

cortAdmin_LHamp_meanSum
cortAdmin_LHamp_bySurged_meanSum
```

```{r}
ppt <- pptAddTwoTables(
  cortAdmin_LHamp_meanSum
  , cortAdmin_LHamp_bySurged_meanSum
  , title = slideTitle
  , dontFormat = FALSE
)
```

```{r}
cortAdmin_LHamp_anova <- cortAdmin_sampling_trust %>%
  anova_test(
    dv = maxLH
    , between = dosage
    , type = 3
  ) %>%
  get_anova_table() %>%
  as_tibble()

cortAdmin_LHamp_anova_flx <- cortAdmin_LHamp_anova %>%
  formatAnova(16)

cortAdmin_LHamp_anova
```

```{r}
ppt <- pptAddOneTable(
  cortAdmin_LHamp_anova_flx
)
```

## Time at peak LH

```{r}
cortAdmin_LHtime <- cortAdmin_sampling_trust %>%
  plotLHTime_dosage(
    surgeMin = 3
    , textSize = 16
    , dotSize = 3
  )
```

```{r}
cortAdmin_LHtime
fileBaseName <- "cortAdmin_LHtime"
slideTitle <- "Oral corticosterone administration does not alter pattern or amplitude of LH surge"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
cortAdmin_LHtime_meanSum <- cortAdmin_sampling_trust %>%
  group_by(
    dosage
  ) %>%
  mutate(
    relTimeMax = timeAtMax - 7.5
  ) %>%
  meanSummary(relTimeMax)

cortAdmin_LHtime_bySurged_meanSum <- cortAdmin_sampling_trust %>%
  group_by(
    dosage,
    surged
  ) %>%
  mutate(
    relTimeMax = timeAtMax - 7.5
  ) %>%
  meanSummary(relTimeMax)

cortAdmin_LHtime_meanSum
cortAdmin_LHtime_bySurged_meanSum
```

```{r}
ppt <- pptAddTwoTables(
  cortAdmin_LHtime_meanSum
  , cortAdmin_LHtime_bySurged_meanSum
  , title = slideTitle
  , dontFormat = FALSE
)
```

```{r}
cortAdmin_LHtime_anova <- cortAdmin_sampling_trust %>%
  anova_test(
    dv = timeAtMax
    , between = dosage
    , type = 3
  ) %>%
  get_anova_table() %>%
  as_tibble()

cortAdmin_LHtime_anova_flx <- cortAdmin_LHtime_anova %>%
  formatAnova(16)

cortAdmin_LHtime_anova
```

```{r}
ppt <- pptAddOneTable(
  cortAdmin_LHtime_anova_flx
)
```

# Chi-squared for prop surged

```{r}
contTable <- table(
  cortAdmin_sampling_trust$dosage
  , cortAdmin_sampling_trust$surged
)

contTable

propSurged.Chi.Sq.res <- chisq_test(contTable) 

propSurged.Chi.Sq.descriptives <-  chisq_descriptives(propSurged.Chi.Sq.res)

ppt <- pptAddTwoTables(
  propSurged.Chi.Sq.res
  , propSurged.Chi.Sq.descriptives
  , title = slideTitle
  , dontFormat = FALSE
)
```
# Ovulation 

```{r}
figureNum <- figureNum + 1
```


```{r}
BD_ovulation_plot <- BD_sampling %>%
  filter(
    trust == TRUE
  ) %>%
  propOvulatedPlot(
    xVar = dosage,
    fontSize = 16
  )
```

```{r}
fileBaseName <- "cortAdmin_propOvulated"
slideTitle <- "Oral corticosterone administration does not alter proportion of animals that ovulated"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
BD_ovulation_plot
```



```{r}
saveDFsToExcel(
  "nutellaCortAdmin"
  , prefix = ""
  , saveFolder = plotFolder
  , "cortAdminSampling" = BD_samplingSave
  , "cortAdminPilot" = cortAdminPilot
  , "LH" = BD_LH_save
  , "cort" = BD_cort_save
  , "mean_cortAdminPilot" = BD_comboNutALPS_meanSum
  , "mean_cort" = cortAdminCortDF_meanSum
  , "anova_cort" = cortAdminCortAnova
  , "mean_LH" = cortAdmin_LH_meanSum
  , "anova_LH" = cortAdmin_LH_anova
  , "mean_maxLH" = cortAdmin_LHamp_meanSum
  , "anova_maxLH" = cortAdmin_LHamp_anova
  , "mean_maxLH_bySurged" = cortAdmin_LHamp_bySurged_meanSum
  , "mean_peakTime" = cortAdmin_LHtime_meanSum
  , "anova_peakTime" = cortAdmin_LHtime_anova
  , "mean_peakTime_bySurged" = cortAdmin_LHtime_bySurged_meanSum
  , "propSurged_chi" = propSurged.Chi.Sq.res
  , "propSurged_chi_descriptives" = propSurged.Chi.Sq.descriptives
)
```

```{r}
BD_sampling %>%
  filter(
    trust == TRUE
  ) %>%
scatterPlot_general(
  xVar = cort_hr5,
  xLab = "corticosterone (ng/mL)",
  yVar = maxLH,
  yLab = "LH (ng/mL)",
  fillVar = dosage,
  fillLimits = c(0, 2),
  fillValues = c("white", "black")
)

BD_sampling %>%
  filter(
    cort_hr5 > 400
  )
```

