---
title: "NGP Seminar Data"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
```

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

```{r}
litterNum_label <- c(
  "1" = "first litter",
  "2" = "second litter"
)

facetForLitterNum <- facet_grid(
    cols = vars(litterNum),
    labeller = labeller(
      litterNum = litterNum_label
    )
  )

figureNum <- 1

pptBaseName <- function(figNum) {
  baseName = paste0("ICN_fig", figNum, "_")
  return(baseName)
}

subFolder <- "ICN"

imgType <- "pdf"
```

# Dam Behavior
```{r}
behaviorTimeHours = c(12, 14, 16, 18, 20, 22, 0, 2, 4)
dam_behavior_filtered <- dam_behavior %>%
  filter(
    Litter_size_startPara >= 5,
    time %in% behaviorTimeHours
  ) %>%
  mutate(
    firstDay = ifelse(
      damID == "D015", 
      FALSE, 
      ifelse(
        (cohort == 2 | cohort == 4 | cohort == 6), 
        TRUE, 
        ifelse(
          damID == "D051-01",
          TRUE,
          FALSE
        )
      )
    )
  )
```

```{r}
# install.packages("lemon")
library(lemon)
```


```{r}
behaviorOverTime <- dam_behavior_filtered %>%
  behavior_overTime(
    yVar = Num_exits,
    yLab = "# of exits",
    fontSize = 28,
    dotSize = 5,
    dotSize_byFirstDay = FALSE,
    timeBreaks = behaviorTimeHours,
    timeLabels = behaviorTimeHours,
    lineSize = 0.75
  )
plot <- behaviorOverTime +
  facet_wrap(
    ~litterNum + earlyLifeTrt,
    ncol = 2,
    labeller = labeller(
      litterNum = litterNum_label
    ),
    scales = "free"
  )+
  theme(
    legend.position = "bottom"
    # , axis.title.x = element_blank()
  ) +
  guides(
    fill = "none"
    , linetype = "none"
  )+
  labs(
    x = "ZT hour"
    # ,shape = "start on P5"
  ) +
  scale_x_discrete(
    labels = c(
      "12" = "12", 
      "14" = "14\nlights off", 
      "16" = "16", 
      "18" = "18", 
      "20" = "20", 
      "22" = "22", 
      "0" = "0\nlights on", 
      "2" = "2", 
      "4" = "4"
    )
  ) +
  expand_limits(y = 70)

plot

fileBaseName <- "damBehavior"
thisWidth = 10.66
thisHeight = 10.8
thisUnits = "in"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
)
```

## ANOVA
```{r}

damBehaviorAnova <- dam_behavior_filtered %>%
  anova_test(
    dv = Num_exits,
    wid = damID,
    between = c(earlyLifeTrt, litterNum),
    within = time
  ) 

damBehaviorAnova$ANOVA%>%
  myDisplay()

dam_behavior_filtered %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = Num_exits,
    between = c(earlyLifeTrt)
  ) %>%
  adjust_pvalue(method = "bonferroni")
```

```{r}
# 1 -> 2
figureNum <- figureNum + 1
```

# Body mass, >= 5 pups/litter, by sex, litter number
```{r}
thisGroupByDam = TRUE
facetBySex = FALSE
useLineType = FALSE
individualLines = TRUE
meanLines = TRUE
zoom_x = FALSE
zoom_x_min = 0
zoom_x_max = 72
zoom_y = FALSE
zoom_y_min = 0
zoom_y_max = 15
indivAlpha = 0.1
meanAlpha = 1
errorBarAlpha = 1
fontSize = 28
STDColor = "#4D4D4D"
LBNColor = "#008B8B"

fileBaseName = "mass_LBN_litterNum"
thisWidth = 10.66
thisHeight = 6.25
thisUnits = "in"

df <- Mass_off %>%
  filter(
    damStrain == "CBA",
    cohort == 2 | cohort == 4 | cohort == 6 | cohort == 7 | cohort == 8,
    Litter_size >= 5,
    sex == "F"
  )
df

groupVar <- ifelse(thisGroupByDam, expr(damID), expr(mouseID))

plot <- df %>%
  plot_mass_lines(
    groupByDam = thisGroupByDam,
    facetBySex = facetBySex,
    useLineType = useLineType, # TRUE/FALSE
    lineTypeVar = earlyLifeTrt,
    lineGroupVar = {{ groupVar }},
    xtitle = "postnatal day", #x axis label
    ytitle = "mass (g)", #y axis label
    title = NULL, # plot title
    individualLines = individualLines, # plot individual lines
    meanLines = meanLines, # plot mean lines with SE
    zoom_x = zoom_x, # Zoom to part of x axis
    xmin = zoom_x_min,
    xmax = zoom_x_max,
    zoom_y = zoom_y, # Zoom to part of y axis
    ymin = zoom_y_min,
    ymax = zoom_y_max,
    indivLineAlpha = indivAlpha,
    indivLineSize = 0.8,
    errorBarWidth = 0,
    meanLineSize = 1.4,
    meanAlpha = meanAlpha,
    errorBarSize = 1,
    # errorBarColor = "grey10",
    errorBarAlpha = errorBarAlpha,
    textSize = fontSize,
    axisSize = 0.5,
    legendPosition = c(0.85, 0.2),
    STDColor = STDColor,
    LBNColor = LBNColor
  ) +
  facet_grid(
    cols = vars(litterNum),
    labeller = labeller(
      litterNum = litterNum_label
    )
  ) +
  theme(
    legend.key = element_rect(fill = NA)
  )

plot 

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```
## Body Mass ANOVA
Group by dam and sex
Look at start of paradigm, end of paradigm, weaning, day 35, and day 70
```{r}
massLong <- Mass_off %>%
  filter(
    Litter_size >= 5
    , cohort == 2 | cohort == 4 | cohort == 6 | cohort == 7 | cohort == 8
    , sex == "F"
  )  %>%
  getAvgByDam(bySex = FALSE) %>%
  makeOffMassLong()

massLong_filtered <- massLong %>%
  filter(
    day == 4 | day == 11 | day == 21 | day == 35 | day == 70
  )

massANOVA_byDam <- massLong_filtered %>%
  anova_test(
    dv = mass,
    wid = damID,
    between = c(earlyLifeTrt, litterNum),
    # within = c(sex, day)
    within = c(day)
  )

massANOVA_byDam$ANOVA %>%
  formatAnova()

# bySexAnova <- massLong_filtered %>%
#   group_by(
#     sex
#   ) %>%
#   anova_test(
#     dv = mass,
#     wid = damID,
#     between = c(earlyLifeTrt),
#     within = day
#   ) %>%
#   get_anova_table() %>%
#   adjust_pvalue(method = "bonferroni") %>%
#   formatAdjAnova()
# 
# bySexAnova
# 
# bySexAnova %>%
#   get_anova_table()
#   # %>%
#   # formatAnova() 
```


# Dam Corticosterone
```{r}
P21_cortDams <- Demo_dam %>%
  filter(
    Litter_size >= 5,
    ParaType == 4,
    !is.na(Cort_dam_P21)
  )

plot <- P21_cortDams %>%
  scatterPlotLBN(
    Cort_dam_P21,
    yLab = "corticosterone (ng/mL)",
    dotSize = 3,
    textSize = 28
  )

plot

fileBaseName = "DamCort_P21firstLitters"
thisWidth = 4
thisHeight = 5.5

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)



plot <- P21_cortDams %>%
  scatterPlotLBN(
    yVar = Cort_dam_P21,
    yLab = "corticosterone (ng/mL)",
    textSize = 28,
    dotSize = 3,
    zoom_y = TRUE,
    ymin = 0,
    ymax = 120
  ) +
  facet_wrap(
    ~litterNum,
    labeller = labeller(
      litterNum = litterNum_label
    )
  )

plot

fileBaseName = "DamCort_P21_match11Zoom"

# flexSave(
#   baseName = fileBaseName,
#   thisFilePrefix = pptBaseName(figureNum),
#   plot = plot,
#   fileType = imgType,
#   filePath = file.path(plotOutputFolder, subFolder),
#   width = thisWidth,
#   height = thisHeight,
#   units = thisUnits,
#   compType = currentCompType,
#   shinySettings = FALSE
# )
```
```{r}
P11_cortDams <- Demo_dam %>%
  filter(
    Litter_size >= 5,
    ParaType == 4,
    !is.na(Cort_dam_P11)
  )

plot <- P11_cortDams %>%
  scatterPlotLBN(
    yVar = Cort_dam_P11,
    yLab = "corticosterone (ng/mL)",
    textSize = 28,
    dotSize = 5,
    zoom_y = TRUE,
    ymin = 0,
    ymax = 120
  ) + 
  facetForLitterNum

plot

thisWidth = 5.5
thisHeight = 6
thisUnits = "in"

fileBaseName = "DamCort_P11"

# flexSave(
#   baseName = fileBaseName,
#   thisFilePrefix = pptBaseName(figureNum),
#   plot = plot,
#   fileType = imgType,
#   filePath = file.path(plotOutputFolder, subFolder),
#   width = thisWidth,
#   height = thisHeight,
#   units = thisUnits,
#   compType = currentCompType,
#   shinySettings = FALSE
# )

P11_cortDams %>%
  anova_test(
    dv = Cort_dam_P11,
    between = c(litterNum, earlyLifeTrt)
  )

P11_cortDams %>%
  scatterPlotTwoVars_byLBN(
    yVar = Cort_dam_P11,
    yLab = "corticosterone (ng/mL)",
    xVar = Litter_size,
    xLab = "# pups in litter",
    textSize = 28,
    dotSize = 3
  )
```


```{r}
# 2 -> 3
figureNum <- figureNum + 1
```

# Maturation
The paradigm was run with dams' first or second litters

```{r}
filteredDF <- Maturation_off %>%
  filter(
    damStrain == "CBA",
    cohort == 2 | cohort == 4 | cohort == 6 | cohort == 7 | cohort == 8,
    Litter_size >= 5
  )
Maturation_byDam_5plusPups_females <- filteredDF %>%
  filter(
    sex == "F"
  ) %>%
  getAvgByDam()
Maturation_byDam_5plusPups_males <- filteredDF %>%
  filter(
    sex == "M"
  ) %>%
  getAvgByDam()

df_females <- Maturation_byDam_5plusPups_females
df_males <- Maturation_byDam_5plusPups_males
```

## Vaginal Opening
### Age
```{r}
VO_age_plot <- df_females %>%
  scatterPlotLBN(
    yVar = VO_age, 
    "age (days)\nvaginal opening",
    # "age (days)",
    textSize = 28, 
    dotSize = 5
  # ) +
  )
  # labs(title = "vaginal opening")
max_VO_age <- df_females$VO_age %>% max(na.rm = TRUE)
```
### Mass
```{r}
VO_mass_plot <- df_females %>%
  scatterPlotLBN(
    yVar = VO_mass, 
    "mass at vaginal opening (g)", 
    textSize = 28, 
    dotSize = 5)
max_VO_mass <- df_females$VO_mass %>% max(na.rm = TRUE)
```

## First Estrus
### Age
```{r}
Estrus_age_plot <- df_females %>%
  scatterPlotLBN(
    yVar = Estrus_age, 
    "age (days)\nfirst estrus",
    # NULL,
    textSize = 28, 
    dotSize = 5
  # )+
  )
  # labs(title = "first estrus")
max_estrus_age <- df_females$Estrus_age %>% max(na.rm = TRUE)
```
### Mass
```{r}
Estrus_mass_plot <- df_females %>%
  scatterPlotLBN(yVar = Estrus_mass, "mass at first estrus (g)", textSize = 28, dotSize = 5)
max_estrus_mass <- df_females$Estrus_mass %>% max(na.rm = TRUE)
```
## Preputial Separation
### Age
```{r}
PreputialSep_age_plot <- df_males %>%
  scatterPlotLBN(
    yVar = PreputialSep_age, 
    "age at preputial sep. (days)",
    # NULL,
    textSize = 28, 
    dotSize = 5
  # ) +
  )
  # labs(title = "preputial sep.")
max_PPS_age <- df_males$PreputialSep_age %>% max(na.rm = TRUE)
```
### Mass
```{r}
PreputialSep_mass_plot <- df_males %>%
  scatterPlotLBN(yVar = PreputialSep_mass, "mass at preputial sep. (g)", textSize = 28, dotSize = 5)
max_PPS_mass <- df_males$PreputialSep_mass %>% max(na.rm = TRUE)
```

```{r}
thisWidth = 5.3
thisHeight = 6.25
thisUnits = "in"

litterNum_label <- c(
  "1" = "first\nlitter",
  "2" = "second\nlitter"
)

facetForLitterNum <- facet_grid(
    cols = vars(litterNum),
    labeller = labeller(
      litterNum = litterNum_label
    )
  )
```


## Age Plots
### VO
```{r}
max_age <- max(max_VO_age, max_estrus_age, max_PPS_age, na.rm = TRUE) + 3

fileBaseName = "VO_age_litterNum"
plot = VO_age_plot + expand_limits(y = max_age) + facetForLitterNum +
  theme(
    axis.text.x = element_text(size = 24)
  )
flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

### First Estrus
```{r}
# thisWidth = 3.8
fileBaseName = "estrus_age_litterNum"
plot = Estrus_age_plot + expand_limits(y = max_age) + facetForLitterNum +
  theme(
    axis.text.x = element_text(size = 24)
  )
flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

### Preputial Separation
```{r}

fileBaseName = "pps_age_litterNum"
plot = PreputialSep_age_plot + expand_limits(y = max_age) + facetForLitterNum +
  theme(
    axis.text.x = element_text(size = 24)
  )
# flexSave(
#   baseName = fileBaseName,
#   thisFilePrefix = pptBaseName(figureNum),
#   plot = plot,
#   fileType = imgType,
#   filePath = file.path(plotOutputFolder, subFolder),
#   width = thisWidth,
#   height = thisHeight,
#   units = thisUnits,
#   compType = currentCompType,
#   shinySettings = FALSE
# )
```

```{r eval=FALSE, include=FALSE}
plot <- plot_grid(
  VO_age_plot + expand_limits(y = max_age) + facetForLitterNum +
    theme(
      # plot.margin = margin(r = 1)
    )
  , Estrus_age_plot + expand_limits(y = max_age) + facetForLitterNum +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank(),
      plot.margin = margin(r = 1, l = 1)
    )
  , PreputialSep_age_plot + expand_limits(y = max_age) + facetForLitterNum +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank(),
      plot.margin = margin(r = 1, l = 1)
    )
  , nrow = 1
  , align = "v"
)
plot
fileBaseName <- "allMaturationAge"
figureNum <- 3
flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = 11.5,
  height = 6.5,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)

```


### Linear mixed effects model
```{r}
library("lmerTest")
library("lme4")
```

```{r}

VO_age_mod <- lmer(
  VO_age ~ earlyLifeTrt + Litter_size + litterNum + (1 | damID),
  data = filteredDF %>% mutate(Litter_size = as.integer(Litter_size)),
  subset = !is.na(VO_age)
)
summary(VO_age_mod)
anova(VO_age_mod)
```

```{r}
Estrus_age_mod <- lmer(
  Estrus_age ~ earlyLifeTrt + Litter_size + litterNum + (1 | damID),
  data = filteredDF %>% mutate(Litter_size = as.integer(Litter_size)),
  subset = !is.na(Estrus_age)
)
summary(Estrus_age_mod)
```

```{r}
PreputialSep_age_mod <- lmer(
  PreputialSep_age ~ earlyLifeTrt + Litter_size + litterNum + (1 | damID),
  data = filteredDF %>% mutate(Litter_size = as.integer(Litter_size)),
  subset = !is.na(PreputialSep_age)
)
summary(PreputialSep_age_mod)
```


## Mass Plots
### Vaginal opening
```{r eval=FALSE, include=FALSE}
max_mass <- max(max_VO_mass, max_estrus_mass, max_PPS_mass, na.rm = TRUE) + 3

fileBaseName = "VO_mass_litterNum"
plot = VO_mass_plot + expand_limits(y = max_mass) + facetForLitterNum
flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

### First Estrus
```{r eval=FALSE, include=FALSE}
fileBaseName = "estrus_mass_litterNum"
plot = Estrus_mass_plot + expand_limits(y = max_mass) + facetForLitterNum
flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

### Preputial Separation
```{r eval=FALSE, include=FALSE}
fileBaseName = "pps_mass_litterNum"
plot = PreputialSep_mass_plot + expand_limits(y = max_mass) + facetForLitterNum
flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
df_females %>%
  anova_test(
    dv = VO_age,
    between = c(litterNum, earlyLifeTrt)
  )
df_females %>%
  anova_test(
    dv = Estrus_age,
    between = c(litterNum, earlyLifeTrt)
  )
df_males %>%
  anova_test(
    dv = PreputialSep_age,
    between = c(litterNum, earlyLifeTrt)
  )
# df_females %>%
#   anova_test(
#     dv = VO_mass,
#     between = c(litterNum, earlyLifeTrt)
#   )
# df_females %>%
#   anova_test(
#     dv = Estrus_mass,
#     between = c(litterNum, earlyLifeTrt)
#   )
# df_males %>%
#   anova_test(
#     dv = PreputialSep_mass,
#     between = c(litterNum, earlyLifeTrt)
#   )
```


```{r}
litterNum_label <- c(
  "1" = "first litter",
  "2" = "second litter"
)

facetForLitterNum <- facet_grid(
    cols = vars(litterNum),
    labeller = labeller(
      litterNum = litterNum_label
    )
  )
```


```{r}
# 3 -> 4
figureNum <- figureNum + 1
```

# ALPS response
## First and Second litters


```{r}
Cort_off_filtered <- Cort_off %>%
  filter(
    cohort == 2 | cohort == 4 | cohort == 6 | cohort == 7 | cohort == 8,
    Litter_size >= 5,
    !is.na(cort),
    !exclude
  ) %>%
  mutate(
    adjMax = ifelse(cort >= 500, TRUE, FALSE),
    adjMin = ifelse(cort <= 1.95, TRUE, FALSE),
    cort = ifelse(cort >= 500, 500, ifelse(cort <= 1.95, 1.95, cort))
  )
thisSex <- "F"

cortByCycle <- Cort_off_filtered %>%
  filter(
    sex == thisSex,
    (Sac_cycle == "proestrus" & ReproTract_mass >= 125) | (Sac_cycle == "diestrus" & ReproTract_mass <= 100),
    mouseID != 653
  )

```


4-way ANOVA - LBN x ALPS x Cycle Stage x Time

```{r}

cortByCycle %>%
  cortAnova(
    byCycle = TRUE
  )

```


There is a significant 4-way interaction, so do the 3-way interaction of 
LBN x ALPS x Time for each cycle stage. Correct for two comparisons

```{r}

cortByCycle %>%
  group_by(
    Sac_cycle
  ) %>%
  anova_test(
    dv = cort,
    wid = mouseID,
    between = c(earlyLifeTrt, adultTrt),
    within = time
  ) %>%
  # adjust_pvalue() %>%
  get_anova_table() %>%
  as_tibble() %>%
  mutate(
    p.adj = p * 2 # doing two cycle stage comparisons
  ) %>%
  # adjust_pvalue(method = "bonferroni") %>%
  formatAdjAnova()
  
```

For diestrous mice, there is a 3-way interaction of LBN x ALPS x time

For proestrous mice, there is a 2-way interaction of ALPS x time


Follow-up the diestrous mice with a 2-way interaction between 
LBN x ALPS at each time. Adjust the p-values for two levels of time

```{r}
cortByCycle %>%
  filter(
    Sac_cycle == "diestrus"
  ) %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = cort,
    wid = mouseID,
    between = c(earlyLifeTrt, adultTrt)
  ) %>%
  # adjust_pvalue() %>%
  # adjust_pvalue(method = "bonferroni") %>%
  get_anova_table() %>%
  as_tibble() %>%
  mutate(
    p.adj = p * 2 # doing two time comparisons
  ) %>%
  formatAdjAnova()
```


At the end of the paradigm, there is an interaction between LBN and ALPS for
the diestrous mice. This means that LBN changes the way that the mice
respond to the ALPS paradigm in diestrous mice.



For the diestrous mice at the end of the paradigm, group by adult treatment
and see if the early-life mice are significantly different.
Adjust for making two treatment comparisons

```{r}

cortByCycle %>%
  filter(
    Sac_cycle == "diestrus",
    time == 5
  ) %>%
  group_by(
    adultTrt
  ) %>%
  anova_test(
    dv = cort,
    wid = mouseID,
    between = c(earlyLifeTrt)
  ) %>%
  # adjust_pvalue() %>%
  adjust_pvalue(method = "bonferroni") %>%
  formatAdjAnova()
```

For the proestrous mice, follow up the ALPS x time interaction.

Group by time, see if there is an effect of ALPS

```{r}
cortByCycle %>%
  filter(
    Sac_cycle == "proestrus"
  ) %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = cort,
    wid = mouseID,
    between = c(adultTrt)
  ) %>%
  # adjust_pvalue() %>%
  adjust_pvalue(method = "bonferroni") %>%
  formatAdjAnova()
```

### proestrus 

```{r}
Cort_off_bySex <- Cort_off_filtered %>%
  filter(
    sex == thisSex,
    Sac_cycle == "proestrus" & ReproTract_mass >= 125,
    mouseID != 653
  )

basePlot <- Cort_off_bySex %>%
  baseCortPlot(
    dotSize = 5
  )

plot <- basePlot %>%
  longCortPlot(
    fontSize = 28
    , zoom_y = TRUE
    , ymin = 0
    , ymax = 550
    , zoom_x = TRUE
    , xmin = -2
    , xmax = 7
  ) +
  ylab("corticosterone\n(ng/mL)") + 
  scale_y_continuous(
    breaks = c(0, 100, 200, 300, 400, 500)
  )
  
plot

fileBaseName = "femalesCort_pro"
thisWidth = 10.66
thisHeight = 6.5
thisUnits = "in"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

### Diestrus 

```{r}
Cort_off_bySex <- Cort_off_filtered %>%
  filter(
    sex == thisSex,
    Sac_cycle == "diestrus" & ReproTract_mass <= 100,
    mouseID != 653
  )

Cort_off_bySex

basePlot <- Cort_off_bySex %>%
  baseCortPlot(
    dotSize = 5
  )

plot <- basePlot %>%
  longCortPlot(
    fontSize = 28
    , zoom_y = TRUE
    , ymin = 0
    , ymax = 550
    , zoom_x = TRUE
    , xmin = -2
    , xmax = 7
  )+
  ylab("corticosterone\n(ng/mL)")+ 
  scale_y_continuous(
    breaks = c(0, 100, 200, 300, 400, 500)
  )
plot

fileBaseName = "femalesCort_di"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```


```{r}
# 4 -> 5
figureNum <- figureNum + 1
```

# LH

## First litter

```{r}
LH_filtered <- LH_off %>%
  filter(
    Litter_size >= 5,
    litterNum == 1,
    Sac_cycle == "proestrus" & ReproTract_mass >= 125
  )

tempLHPlot <- function(
  df,
  ymax = 40
){
  df %>%
    LHPlot(
    fontSize = 28,
    dotSize = 5,
    zoom_y = TRUE,
    ymin = 0,
    ymax = ymax
  ) +
  theme(
    legend.position = "none"
  ) +
  facet_wrap(~comboTrt, scales = "free")
}

plot <- LH_filtered %>%
  tempLHPlot()

plot 

thisWidth = 10.66
thisHeight = 11

fileBaseName = "LH_combined_first"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
plot <- surgedDF %>%
  plotLHAmp_comboTrt(
    3,
    textSize = 28,
    dotSize = 5,
    angleX = FALSE
  )

plot 
thisHeight = 5.5
thisWidth = 10.66

fileBaseName = "LH_amplitude_first"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```
## Second litter

```{r}
LH_filtered <- LH_off %>%
  filter(
    Litter_size >= 5,
    litterNum == 2,
    Sac_cycle == "proestrus" & ReproTract_mass >= 125
  )

tempLHPlot <- function(
  df,
  ymax = 40
){
  df %>%
    LHPlot(
    fontSize = 28,
    dotSize = 5,
    zoom_y = TRUE,
    ymin = 0,
    ymax = ymax
  ) +
  theme(
    legend.position = "none"
  ) +
  facet_wrap(~comboTrt, scales = "free")
}

plot <- LH_filtered %>%
  mutate(
    comboTrt = factor(comboTrt, levels = c("STD-CON", "LBN-CON", "STD-ALPS", "LBN-ALPS"))
  ) %>%
  tempLHPlot()

plot 

thisWidth = 10.66
thisHeight = 11

fileBaseName = "LH_combined_second"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
plot <- surgedDF %>%
  plotLHAmp_comboTrt(
    3,
    textSize = 28,
    dotSize = 5,
    angleX = FALSE
  )

plot 
thisHeight = 5.5
thisWidth = 10.66

fileBaseName = "LH_amplitude_second"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```


```{r}
# 5 -> 6
figureNum <- figureNum + 1
```


```{r}
# 6 -> 7
figureNum <- figureNum + 1
```

# Cycles
## Second litters
```{r}
cycles_2ndLitter <- Cycles_off %>%
  filter(
    litterNum == 2,
    Litter_size >= 5,
    cohort == 4 | cohort == 6
  )

cyclesLong_2ndLitter <- makeCyclesLong(cycles_2ndLitter)
cyclesPerc_long_2ndLitter <- makeCyclesPercLong(cycles_2ndLitter)
```


### Representative
```{r}
STDMice <- cycles_2ndLitter %>%
  filter(
    earlyLifeTrt == "STD"
  )
STDtoUse <- STDMice[sample(nrow(STDMice))[1:6], ] %>% makeCyclesLong()

LBNMice <- cycles_2ndLitter %>%
  filter(
    earlyLifeTrt == "LBN"
  )
LBNtoUse <- LBNMice[sample(nrow(LBNMice))[1:6], ] %>% makeCyclesLong()

cycles_2ndLitter_STD_plot <- plotCycleTraces(
  STDtoUse, 
  colorValues = c("grey30", "cyan4"),
  fontSize = 28,
  removeFacets = TRUE,
  ncol = 2,
  nrow = 3
  ) + theme(
    # axis.text.x = element_text(size = 16)
    panel.border = element_rect(color = "lightgrey", fill = NA)
  )
cycles_2ndLitter_LBN_plot <- plotCycleTraces(
  LBNtoUse,
  colorValues = c("grey30", "cyan4"),
  fontSize = 28,
  removeFacets = TRUE,
  ncol = 2,
  nrow = 3
  )+ theme(
    # axis.text.x = element_text(size = 16)
    panel.border = element_rect(color = "lightgrey", fill = NA)
  )

cycles_2ndLitter_STD_plot
cycles_2ndLitter_LBN_plot

STD_BaseName = "cycles_2ndLitter_STD"
LBN_BaseName = "cycles_2ndLitter_LBN"

thisWidth = 5.3
thisHeight = 5.25

flexSave(
  baseName = STD_BaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = cycles_2ndLitter_STD_plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
flexSave(
  baseName = LBN_BaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = cycles_2ndLitter_LBN_plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

### Percent days in stage
```{r}
plot <- plotCyclesPercent(cyclesPerc_long_2ndLitter, fontSize = 28, dotSize = 5)+
  expand_limits(y = 100)
plot

fileBaseName <- "cycles_2ndLitter_percDaysStage"

thisWidth = 11.2
thisHeight = 4.5

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```


<!-- # First and Second Litter Sizes >= 5 pups -->
```{r eval=FALSE, include=FALSE}
fileBaseName = "litterSize_LBN_firstVsecond"
thisWidth = 11.5
thisHeight = 5
thisUnits = "in"

df <- Demo_dam %>%
  filter(
    !is.na(Litter_size_endPara),
    cohort == "2" | cohort == "4" | cohort == "6" | cohort == "7" | cohort == "8",
    Litter_size_endPara >= 5, # Because in the middle of some
    !is.na(earlyLifeTrt)
  )

df %>%
  filter(
    is.na(Duration_ZT19)
  ) %>%
  select(
    damID,
    earlyLifeTrt,
    Litter_size_endPara
  )


plot <- df %>%
  ggplot(
    aes(
      x = Litter_size_endPara,
      fill = earlyLifeTrt
    )
  )+
  geom_bar(
    position = position_dodge2(preserve = "single"),
    width = 0.9,
    color = "white"
  ) +
  boxTheme()+
  textTheme(
    size = 16
  )+
  earlyLifeFill(STDColor = "#4D4D4D") +
  scale_x_continuous(
    breaks = seq(1, 8, by = 1)
  ) +
  scale_y_continuous(
    breaks = seq(1, 6, by = 1)
  ) +
  theme(
      legend.position = c(0.15, 0.8)
    )+
  labs(x = "litter size", y = "# of litters") +
  expand_limits(x = 0)+
  facetForLitterNum

plot

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
# 6 -> 7
figureNum <- figureNum + 1
# figureNum <- 7
```



```{r}
# 7 -> 8
figureNum <- figureNum + 1
# figureNum <- 8
```


```{r}
# 8 -> 9
figureNum <- figureNum + 1
# figureNum <- 9
```



```{r}
# 9 -> 10
figureNum <- figureNum + 1
# figureNum <- 10
```



# Cycles

## Example
Cohort 4, mouse 22
```{r}
cycles_demo <- Cycles_off %>%
  filter(
    mouseID == 422
  )
cyclesLong_demo <- makeCyclesLong(cycles_demo) %>% filter(
  day < 22
)

plot <- plotCycleTraces(cyclesLong_demo, removeFacets = TRUE, fontSize = 28)

plot

thisWidth = 11
thisHeight = 5.5
thisUnits = "in"

fileBaseName = "Demo_cyclesPlot"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
# 16 -> 17
figureNum <- figureNum + 1
# figureNum <- 17
```

## First litters
```{r}
cycles_1stLitter <- Cycles_off %>%
  filter(
    litterNum == 1,
    Litter_size >= 5,
    cohort == 2 | cohort == 7
  )

cyclesLong_1stLitter <- makeCyclesLong(cycles_1stLitter)
cyclesPerc_long_1stLitter <- makeCyclesPercLong(cycles_1stLitter)
```

### Representative
```{r}
STDMice <- cycles_1stLitter %>%
  filter(
    earlyLifeTrt == "STD"
  )
STDtoUse <- STDMice[sample(nrow(STDMice))[1:6], ] %>% makeCyclesLong()

LBNMice <- cycles_1stLitter %>%
  filter(
    earlyLifeTrt == "LBN"
  )
LBNtoUse <- LBNMice[sample(nrow(LBNMice))[1:6], ] %>% makeCyclesLong()

cycles_1stLitter_STD_plot <- plotCycleTraces(
  STDtoUse, 
  colorValues = c("grey30", "cyan4"),
  fontSize = 28,
  removeFacets = TRUE,
  ncol = 2,
  nrow = 3
  ) + theme(
    # axis.text.x = element_text(size = 16)
    panel.border = element_rect(color = "lightgrey", fill = NA)
  )
cycles_1stLitter_LBN_plot <- plotCycleTraces(
  LBNtoUse,
  colorValues = c("grey30", "cyan4"),
  fontSize = 28,
  removeFacets = TRUE,
  ncol = 2,
  nrow = 3
  )+ theme(
    # axis.text.x = element_text(size = 16)
    panel.border = element_rect(color = "lightgrey", fill = NA)
  )

cycles_1stLitter_STD_plot
cycles_1stLitter_LBN_plot

STD_BaseName = "cycles_1stLitter_STD"
LBN_BaseName = "cycles_1stLitter_LBN"

thisWidth = 4
thisHeight = 5.5

flexSave(
  baseName = STD_BaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = cycles_1stLitter_STD_plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
flexSave(
  baseName = LBN_BaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = cycles_1stLitter_LBN_plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
# 17 -> 18
figureNum <- figureNum + 1
# figureNum <- 18
```


### Percent days in stage
```{r}
plot <- plotCyclesPercent(cyclesPerc_long_1stLitter, fontSize = 28, dotSize = 2.5)
plot

fileBaseName <- "cycles_1stLitter_percDaysStage"

thisWidth = 4.65
thisHeight = 4.62

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```


```{r}
# 18 -> 19
figureNum <- figureNum + 1
# figureNum <- 19
```

## Second litters
```{r}
cycles_2ndLitter <- Cycles_off %>%
  filter(
    litterNum == 2,
    Litter_size >= 5,
    cohort == 4 | cohort == 6
  )

cyclesLong_2ndLitter <- makeCyclesLong(cycles_2ndLitter)
cyclesPerc_long_2ndLitter <- makeCyclesPercLong(cycles_2ndLitter)
```

### Representative
```{r}
STDMice <- cycles_2ndLitter %>%
  filter(
    earlyLifeTrt == "STD"
  )
STDtoUse <- STDMice[sample(nrow(STDMice))[1:6], ] %>% makeCyclesLong()

LBNMice <- cycles_2ndLitter %>%
  filter(
    earlyLifeTrt == "LBN"
  )
LBNtoUse <- LBNMice[sample(nrow(LBNMice))[1:6], ] %>% makeCyclesLong()

cycles_2ndLitter_STD_plot <- plotCycleTraces(
  STDtoUse, 
  colorValues = c("grey30", "cyan4"),
  fontSize = 28,
  removeFacets = TRUE,
  ncol = 2,
  nrow = 3
  ) + theme(
    # axis.text.x = element_text(size = 16)
    panel.border = element_rect(color = "lightgrey", fill = NA)
  )
cycles_2ndLitter_LBN_plot <- plotCycleTraces(
  LBNtoUse,
  colorValues = c("grey30", "cyan4"),
  fontSize = 28,
  removeFacets = TRUE,
  ncol = 2,
  nrow = 3
  )+ theme(
    # axis.text.x = element_text(size = 16)
    panel.border = element_rect(color = "lightgrey", fill = NA)
  )

cycles_2ndLitter_STD_plot
cycles_2ndLitter_LBN_plot

STD_BaseName = "cycles_2ndLitter_STD"
LBN_BaseName = "cycles_2ndLitter_LBN"

thisWidth = 4
thisHeight = 5.5

flexSave(
  baseName = STD_BaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = cycles_2ndLitter_STD_plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
flexSave(
  baseName = LBN_BaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = cycles_2ndLitter_LBN_plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
# 19 -> 20
figureNum <- figureNum + 1
# figureNum <- 20
```


### Percent days in stage
```{r}
plot <- plotCyclesPercent(cyclesPerc_long_2ndLitter, fontSize = 28, dotSize = 2.5)
plot

fileBaseName <- "cycles_2ndLitter_percDaysStage"

thisWidth = 4.65
thisHeight = 4.62

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```


```{r}
# 20 -> 21
figureNum <- figureNum + 1
# figureNum <- 21
```


# CBA x B6 cross response to ALPS

```{r}
# Load Beth's data
source(file.path(scriptsFolder, "03-load-bw-lh-data.R"))
```

```{r eval=FALSE, include=FALSE}
plot <- BW_data_wide %>%
  plotLHAmp(surgeMin = surgeMin, textSize = 28, dotSize = 2.2)

plot

fileBaseName = "CBA_B6 Surge Plot"

thisWidth = 3.33
thisHeight = 3.77
thisUnits = "in"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
# 21 -> 22
figureNum <- figureNum + 1
# figureNum <- 22
```


