---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```
# Set up
Set-up the notebook. This script loads the environment, and contains the names for the data file, and sources the additional scripts that will be used for the analysis.
```{r GetReady}
source("./Scripts/LBN_0002_AGG_setUp.R")
dateToday = Sys.Date()
filterDateForTaskDFs = as.Date("2020-12-01") #Look for breed dates/DOBs after this date
```

# Load Data
The "load_LBN_data" function takes the data folder and excel file name and outputs a list with the processed dataframes. These have the demographic data and any "mutations" (calculated columns) added already.
The output of this chunk is each of these dataframes.
```{r LoadData, include=FALSE}
DFs <- load_LBN_data(
  dataFolder = DataFolder,
  excelName = LBN_DataName
)

Demo_dam <- DFs$Demo_dam
Demo_off <- DFs$Demo_off
Mass_off <- DFs$Mass_off
Maturation_off <- DFs$Maturation_off
EndPara_off <- DFs$EndPara_off
Cycles_off <- DFs$Cycles_off
AcuteStress_off <- DFs$AcuteStress_off
ChronicStress_off <- DFs$ChronicStress_off
LBN_all <- DFs$LBN_all
LBN_data <- DFs$LBN_data
CRH_dam <- DFs$CRH_dam
```

```{r}
# see testing output from 2021-06-08 for outline of how to approach this
```

