---
title: "R Notebook"
output: html_notebook
---

```{r}
summarizePTB <- function(
    ptbData
    , end_time = 120
    , duration = 15
){
  # Generate a sequence of start times for each second
  start_times <- seq(0, end_time, by = 1)
  
  
  # Initialize a data frame to store the results
  results <- data.frame(
    start_time = double(),
    freq = double(),
    mean_relPeak = double()
  )
  
  # Loop through each start time and calculate the mean relPeak for the corresponding 15s window
  for (start in start_times) {
    # Define the end of the current bin
    end_bin <- start + duration
    if(end_bin<=end_time){
      # Subset ptbData for events within the current bin
      bin_data <- ptbData %>% filter(ptb >= start, ptb < end_bin)
      # num events in bin
      countEvents <- length(bin_data$ptb)
      # Calculate the mean of relPeak for the bin
      mean_relPeak <- mean(bin_data$relPeak, na.rm = TRUE)
      # Store the results (note that if there are no events in the bin, mean_relPeak will be NA)
      results <- rbind(results, data.frame(start_time = start, freq = countEvents/duration, mean_relPeak = mean_relPeak))
      
    }
  }
  
  # Remove rows with NA in `mean_relPeak`
  results <- results %>% na.omit()
  
  return(results)
}

selectMatchingBins <- function(
    sumPTB
    , desiredFreq
    , desiredPeak
    , filterByFreq = TRUE
    , filterByPeak = TRUE
    , freqTol = 0.05
    , peakTol = 2
){
  matching <- sumPTB
  
  if(filterByFreq){
    matching <- matching %>%
      filter(
        freq >= desiredFreq - freqTol & freq <= desiredFreq + freqTol
      )
  }
  
  if(filterByPeak){
    matching <- matching %>%
      filter(
        mean_relPeak >= desiredPeak - peakTol & mean_relPeak <= desiredPeak + peakTol
      )
  }
  return(matching)
}

returnPSCMedian <- function(sumDF, find_earlyLifeTrt, find_adultTrt, find_variable){
  subDF <- sumDF %>%
    filter(
      earlyLifeTrt == find_earlyLifeTrt
      , adultTrt == find_adultTrt
      , variable == find_variable
    )
  return(subDF$median)
}
```

```{r}
pscSum <- GABApscs_240Filtered %>%
  group_by(
    earlyLifeTrt
    , adultTrt
  ) %>%
  quartilesSummary(c(frequency, relPeak))

pscSum

STD_CON_freq_median <- returnPSCMedian(pscSum, "STD", "CON", "frequency")
STD_CON_amp_median <- returnPSCMedian(pscSum, "STD", "CON", "relPeak")
STD_ALPS_freq_median <- returnPSCMedian(pscSum, "STD", "ALPS", "frequency")
STD_ALPS_amp_median <- returnPSCMedian(pscSum, "STD", "ALPS", "relPeak")

LBN_CON_freq_median <- returnPSCMedian(pscSum, "LBN", "CON", "frequency")
LBN_CON_amp_median <- returnPSCMedian(pscSum, "LBN", "CON", "relPeak")
LBN_ALPS_freq_median <- returnPSCMedian(pscSum, "LBN", "ALPS", "frequency")
LBN_ALPS_amp_median <- returnPSCMedian(pscSum, "LBN", "ALPS", "relPeak")
```

# STD-CON
Freq median: 0.429
Amp median: 34.7

Selecting between 20230210c and 20230210a
They're on either side of amplitude, too

20230210a series 19, at 22s is good
Current range: -90, 80

```{r}
GABApscs_240Filtered %>%
  filter(
    earlyLifeTrt == "STD"
    , adultTrt == "CON"
  ) %>%
  arrange(
    frequency
  )
```
```{r}
seriesName <- "20230210aS19"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)

STD_CON_freq_median
STD_CON_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = STD_CON_freq_median
    , desiredPeak = STD_CON_amp_median
    , peakTol = 1
  )
```
```{r}
seriesName <- "20230210aS21"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


STD_CON_freq_median
STD_CON_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = STD_CON_freq_median
    , desiredPeak = STD_CON_amp_median
  )
```

# STD-ALPS

STD-ALPS
STD-ALPS: 
Freq median: 0.546
Amp median: 32.0

20220516a is freq median (high amp)
20220516d is amp median (high freq)
20220115e is just below freq median, a little low on amp

20220516d series 12, at 21 sec is a good trace
20220115e series 20, at 100 sec is a good trace

20220516d series 12, at 21 sec is a good trace
Current range -85, 70

```{r}
GABApscs_240Filtered %>%
  filter(
    earlyLifeTrt == "STD"
    , adultTrt == "ALPS"
  ) %>%
  arrange(
    frequency
  )
```

```{r}
seriesName <- "20220516aS17"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


STD_ALPS_freq_median
STD_ALPS_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = STD_ALPS_freq_median
    , desiredPeak = STD_ALPS_amp_median
    # , filterByPeak = FALSE
  )
```

```{r}
seriesName <- "20220516aS19"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


STD_ALPS_freq_median
STD_ALPS_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = STD_ALPS_freq_median
    , desiredPeak = STD_ALPS_amp_median
    # , filterByPeak = FALSE
  )
```


```{r}
seriesName <- "20220516dS12"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


STD_ALPS_freq_median
STD_ALPS_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = STD_ALPS_freq_median
    , desiredPeak = STD_ALPS_amp_median
    # , filterByPeak = FALSE
  )
```

```{r}
seriesName <- "20220516dS14"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


STD_ALPS_freq_median
STD_ALPS_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = STD_ALPS_freq_median
    , desiredPeak = STD_ALPS_amp_median
    # , filterByPeak = FALSE
  )
```

```{r}
seriesName <- "20220115eS20"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


STD_ALPS_freq_median
STD_ALPS_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = STD_ALPS_freq_median
    , desiredPeak = STD_ALPS_amp_median
    # , filterByPeak = FALSE
  )
```
```{r}
seriesName <- "20220115eS22"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


STD_ALPS_freq_median
STD_ALPS_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = STD_ALPS_freq_median
    , desiredPeak = STD_ALPS_amp_median
    # , filterByPeak = FALSE
  )
```

# LBN-CON

Freq median: 0.650
Amp median: 34.7

20220513j is freq median, also close on amp
20220513j series 12, at 45s is good
Current range -62, 70

```{r}
GABApscs_240Filtered %>%
  filter(
    earlyLifeTrt == "LBN"
    , adultTrt == "CON"
  ) %>%
  arrange(
    frequency
  )
```


```{r}
seriesName <- "20220513jS12"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


LBN_CON_freq_median
LBN_CON_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = LBN_CON_freq_median
    , desiredPeak = LBN_CON_amp_median
    # , filterByPeak = FALSE
  )
```
```{r}
seriesName <- "20220513jS15"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


LBN_CON_freq_median
LBN_CON_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = LBN_CON_freq_median
    , desiredPeak = LBN_CON_amp_median
    # , filterByPeak = FALSE
  )
```



# LBN-ALPS 
Freq median: 0.429
Amp median: 44.17

20220305b and 20221209a are either side of freq median
20220305b is amp median

20220305b, series 22, at 10.9s is good
Current range, -50, 70

```{r}
GABApscs_240Filtered %>%
  filter(
    earlyLifeTrt == "LBN"
    , adultTrt == "ALPS"
  ) %>%
  arrange(
    frequency
  )
```

```{r}
seriesName <- "20220305bS18"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


LBN_ALPS_freq_median
LBN_ALPS_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = LBN_ALPS_freq_median
    , desiredPeak = LBN_ALPS_amp_median
    # , filterByPeak = FALSE
    , peakTol = 1
  )
```

```{r}
seriesName <- "20220305bS22"
ptbData <- loadExcelSheet_fromFile(path(dataFolder, "AGG_LBN_GABA_PTBs_forRep.xlsx"), seriesName)


LBN_ALPS_freq_median
LBN_ALPS_amp_median

ptbData %>%
  summarizePTB() %>%
  selectMatchingBins(
    desiredFreq = LBN_ALPS_freq_median
    , desiredPeak = LBN_ALPS_amp_median
    # , filterByPeak = FALSE
    , peakTol = 1
  )
```

