---
title: "R Notebook"
output: html_notebook
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
source("./01-scripts/04-filter-datasets.R")
```


```{r}
ZTs = c(0:23)
mins = c(0, 15, 30, 45)

damsDOB <- damFiltered %>%
  select(
    damID,
    DOB,
    Camera_number,
    earlyLifeTrt,
    cohort,
    litterNum,
    Litter_size
  ) %>%
  rename(
    Camera = Camera_number
  ) %>%
  mutate(
    Camera_number = case_when(
      Camera == "Right" ~ 5,
      Camera == "Right - Mac Air" ~ 5,
      Camera == "Left - MacBook Pro" ~ 6,
      Camera == "Mac Book Pro (right)" ~ 2,
      Camera == "Mac Book Air - (now left)" ~ 1,
      Camera == "1 - MacBook Air " ~ 1,
      Camera == "1 - MacBook Air" ~ 1,
      Camera == "2 - MacBook Pro" ~ 2,
      Camera == "3 - Dispo Mac" ~ 3,
      Camera == "4 - Beth Pro" ~ 4,
      TRUE ~ NaN
    )
  ) %>%
  select (
    -Camera
  ) %>%
  rename(
    camera = Camera_number,
    litterSize = Litter_size
  ) %>%
  relocate(
    camera,
    .before = litterSize
  )

damsDOB

saveDFsToExcel(
  "damsInfo",
  "damsInfo" = damsDOB
)
```


```{r}
getImgsDF <- function(
    damsDOB,
    PNDs,
    ZTs = c(0:23),
    mins = c(0, 15, 30, 45),
    imgsFolder = damImgsFolder
){
  damsImgs <- damsDOB

  for(PND in PNDs){
    for(ZT in ZTs){
      for(min in mins){
        colName = paste0(
          "PND",
          sprintf("%02d", as.integer(PND)),
          "_ZT",
          sprintf("%02d", as.integer(ZT)),
          "_min",
          sprintf("%02d", as.integer(min))
        )
        damsImgs <- damsImgs %>%
          mutate(
            "{colName}":=NA
          )
      }
    }
  }
  
  damsImgs_long <- damsImgs %>%
    pivot_longer(
      cols = starts_with("PND"),
      names_to = c("PND", "ZT", "minute"),
      names_pattern = "PND(.*)_ZT(.*)_min(.*)"
    ) %>%
    mutate(
      PND = as.numeric(PND),
      ZT = as.numeric(ZT),
      minute = as.numeric(minute)
    ) %>%
    select(
      -value
    )
  
  damsImgs_long
  
  imgsDF <- damsImgs_long %>%
    rowwise() %>%
    mutate(
      imgDate = getZTDate(getZT_DateTime(DOB, PND, ZT)),
      imgTime = getZTHour(getZT_DateTime(DOB, PND, ZT)),
      imgMatchString = paste0(
        damID,
        "_",
        imgDate,
        "_",
        sprintf("%02d", as.integer(imgTime)),
        "*",
        sprintf("%02d", as.integer(minute)),
        "min.png"
      ),
      imgRegEx = getStillRegEx(damID, DOB, PND, ZT, minute),
      imgPath = findMatchingFile(
        imgsFolder,
        imgRegEx,
        damID,
        date = paste(PND, ZT, minute)
      ),
      imgName = ifelse(!is.na(imgPath), basename(imgPath), NA)
    ) %>%
    filter(
      !is.na(imgName)
    )
  
  return(imgsDF)
}
```


# PND 4

```{r}
ptm <- proc.time()
PNDs = c(4)

P4_imgs <- getImgsDF(damsDOB, PNDs)

P4_imgs
saveDFsToExcel(
  "P4_imgs",
  "P4" = P4_imgs
)
remove(P4_imgs)
proc.time() - ptm
```

# PND 5

```{r}
PNDs = c(5)

P5_imgs <- getImgsDF(damsDOB, PNDs)

P5_imgs
saveDFsToExcel(
  "P5_imgs",
  "P5" = P5_imgs
)
remove(P5_imgs)
```

# PND 6

```{r}
PNDs = c(6)

P6_imgs <- getImgsDF(damsDOB, PNDs)

P6_imgs
saveDFsToExcel(
  "P6_imgs",
  "P6" = P6_imgs
)
remove(P6_imgs)
```

# PND 7

```{r}
PNDs = c(7)

P7_imgs <- getImgsDF(damsDOB %>% filter(cohort == 9), PNDs)

P7_imgs
saveDFsToExcel(
  "P7_imgs",
  "P7" = P7_imgs
)
remove(P7_imgs)
```

# PND 8

```{r}
PNDs = c(8)

P8_imgs <- getImgsDF(damsDOB %>% filter(cohort == 9), PNDs)

P8_imgs
saveDFsToExcel(
  "P8_imgs",
  "P8" = P8_imgs
)
remove(P8_imgs)
```

# PND 9

```{r}
PNDs = c(9)

P9_imgs <- getImgsDF(damsDOB %>% filter(cohort == 9), PNDs)

P9_imgs
saveDFsToExcel(
  "P9_imgs",
  "P9" = P9_imgs
)
remove(P9_imgs)
```

# PND 10

```{r}
PNDs = c(10)

P10_imgs <- getImgsDF(damsDOB %>% filter(cohort == 9), PNDs)

P10_imgs
saveDFsToExcel(
  "P10_imgs",
  "P10" = P10_imgs
)
remove(P10_imgs)
```

# PND 11

```{r}
PNDs = c(11)

P11_imgs <- getImgsDF(damsDOB %>% filter(cohort == 9), PNDs)

P11_imgs
saveDFsToExcel(
  "P11_imgs",
  "P11" = P11_imgs
)
remove(P11_imgs)
```

# D062 - Images were initially labeled as test, get the files for the relabeled ones

```{r}
PNDs = c(4)

D062_imgs <- getImgsDF(damsDOB %>% filter(damID == "D062-01"), PNDs, ZTs = c(4:13))

D062_imgs
saveDFsToExcel(
  "D062_imgs",
  "D062" = D062_imgs
)
remove(D062_imgs)
```
# D029 - P5, ZT14, only have first two images exported initially

```{r}
PNDs = c(5)

D029_imgs <- getImgsDF(damsDOB %>% filter(damID == "D029-02"), PNDs, ZTs = c(14))

D029_imgs
saveDFsToExcel(
  "D029_imgs",
  "D029" = D029_imgs
)
remove(D029_imgs)
```

# D035 - P5, ZT21, need to add min 45

```{r}
PNDs = c(5)

D035_imgs <- getImgsDF(damsDOB %>% filter(damID == "D035-02"), PNDs, ZTs = c(21), mins = c(45))

D035_imgs
saveDFsToExcel(
  "D035_imgs",
  "D035" = D035_imgs
)
remove(D035_imgs)
```

# D051 - P5, ZT7, need to add min 30, 45
File was split, had to modify the times to get the appropriate output

```{r}
PNDs = c(5)

D051_imgs <- getImgsDF(damsDOB %>% filter(damID == "D051-01"), PNDs, ZTs = c(7), mins = c(30, 45))

D051_imgs
saveDFsToExcel(
  "D051_imgs",
  "D051" = D051_imgs
)
remove(D051_imgs)
```

# D069 - P10, ZT23, need to add min 30, 45
File was split, had to modify the times to get the appropriate output

```{r}
PNDs = c(10)

D069_imgs <- getImgsDF(damsDOB %>% filter(damID == "D069-01"), PNDs, ZTs = c(23), mins = c(30, 45))

D069_imgs
saveDFsToExcel(
  "D069_imgs",
  "D069" = D069_imgs
)
remove(D069_imgs)
```

# D087

```{r}
PNDs = c(4:11)

D087_imgs <- getImgsDF(damsDOB %>% filter(damID == "D087-01"), PNDs)

D087_imgs
saveDFsToExcel(
  "D087_imgs",
  "D087" = D087_imgs
)
remove(D087_imgs)
```

# Move incorrect Dam Images
```{r}
LBN_imgDelete <- loadExcelSheet_fromFile(file.path(dataFolder, "AGG_LBN_deleteDamImgs_2023-01-12.xlsx"), "Sheet1")
LBN_imgDelete

damImgsFolder

moveDamImgFile <- function(thisDamID, fileName, imgsFolder = damImgsFolder){
  currentLoc = file.path(imgsFolder, thisDamID)
  newLoc = file.path(imgsFolder, "movedImgs", thisDamID)
  newLocExists = dir_exists(newLoc)
  if(!newLocExists){
    dir_create(newLoc) # dir_create should ignore already existing directories, but just to be safe, check myself
  }
  file_move(
    file.path(currentLoc, fileName),
    newLoc
  )
}

mapply(moveDamImgFile, thisDam = LBN_imgDelete$damID, fileName = LBN_imgDelete$imgName)
```

Find other matching files at these times
Ran this until there weren't any more matching files
```{r}
moveImgsDF <- LBN_imgDelete %>%
    rowwise() %>%
    mutate(
      imgRegEx = getStillRegEx(damID, DOB, PND, ZT, minute),
      imgPath = findMatchingFile(
        file.path(damImgsFolder, damID),
        imgRegEx,
        damID,
        date = paste(PND, ZT, minute)
      ),
      imgName = ifelse(!is.na(imgPath), basename(imgPath), NA)
    ) %>%
    filter(
      !is.na(imgName)
    )

moveImgsDF

mapply(moveDamImgFile, thisDam = moveImgsDF$damID, fileName = basename(moveImgsDF$imgName))
```

# Move images that will be regenerated
```{r}
LBN_imgUpdate <- loadExcelSheet_fromFile(file.path(dataFolder, "AGG_LBN_updateImgs_2023-01-12.xlsx"), "Sheet1")
LBN_imgUpdate
```

Find other matching files at these times
Ran this until there weren't any more matching files
```{r}
moveImgsDF <- LBN_imgUpdate %>%
    rowwise() %>%
    mutate(
      imgRegEx = getStillRegEx(damID, DOB, PND, ZT, minute),
      imgPath = findMatchingFile(
        file.path(damImgsFolder, damID),
        imgRegEx,
        damID,
        date = paste(PND, ZT, minute)
      ),
      imgName = ifelse(!is.na(imgPath), basename(imgPath), NA)
    ) %>%
    filter(
      !is.na(imgName)
    )

moveImgsDF

mapply(moveDamImgFile, thisDam = moveImgsDF$damID, fileName = basename(moveImgsDF$imgName))
```


```{r}
LBN_imgUpdate
```


```{r}
imgsDF <- LBN_imgUpdate %>%
  rowwise() %>%
  mutate(
    imgDate = getZTDate(getZT_DateTime(DOB, PND, ZT)),
    imgTime = getZTHour(getZT_DateTime(DOB, PND, ZT)),
    imgMatchString = paste0(
      damID,
      "_",
      imgDate,
      "_",
      sprintf("%02d", as.integer(imgTime)),
      "*",
      sprintf("%02d", as.integer(minute)),
      "min.png"
    ),
    imgRegEx = getStillRegEx(damID, DOB, PND, ZT, minute),
    imgPath = file.path(damImgsFolder, damID, imgName)
  ) %>%
  mutate(
    cohort = as_factor(cohort)
  ) %>%
  left_join(
    damsDOB
    , by = c("damID", "DOB", "cohort")
  ) %>%
  select(
    damID,
    DOB,
    earlyLifeTrt,
    cohort,
    litterNum,
    camera,
    litterSize,
    PND,
    ZT,
    minute,
    imgDate,
    imgTime,
    imgRegEx,
    imgPath,
    imgName
  )
imgsDF

saveDFsToExcel(
  "updatedImgsPath",
  "updatedImgs" = imgsDF
)
```


# 2023-01-12
Added scored dam frame information to R

```{r}
damFrames

damFrames_byLightDark <- damFrames %>%
  makeFactors(
    c("PND", "lightDark") 
  )%>%
  group_by(
    damID,
    PND,
    lightDark
  ) %>%
  summarize(
    numForMouse = n(),
    percTogether = sum(pupsTogether) / numForMouse * 100
  ) %>%
  left_join(
    Demo_dam %>%
      select(
        damID,
        earlyLifeTrt,
        cohort,
        Litter_size,
        Camera_number
      ), by = "damID"
  )

damFrames_byPND <- damFrames %>%
  makeFactors(
    c("PND", "lightDark") 
  )%>%
  group_by(
    damID,
    PND
  ) %>%
  summarize(
    numForMouse = n(),
    percTogether = sum(pupsTogether) / numForMouse * 100
    , .groups = "drop"
  ) %>%
  left_join(
    Demo_dam %>%
      select(
        damID,
        earlyLifeTrt,
        cohort,
        Litter_size,
        Camera_number
        , litterNum
      ), by = "damID"
  )


plotPercTogetherP4_P11 <- damFrames_byPND %>%
  plotDamFrame_days(
    percTogether,
    "% frames pups together",
    addTriangleForMean = TRUE,
    redMean = TRUE,
    showDots = FALSE,
    colorByDam = TRUE,
    dotSize = 5
  ) +
  facet_wrap(
    ~ earlyLifeTrt
  ) +
  ylim(c(0, 100))


plotPercTogetherP4_P6 <- damFrames_byPND %>%
  filter(
    PND %in% c(4:6)
  ) %>%
  plotDamFrame_days(
    percTogether,
    "% frames pups together",
    addTriangleForMean = TRUE,
    redMean = TRUE,
    showDots = FALSE,
    colorByDam = TRUE,
    dotSize = 5
  ) +
  facet_wrap(
    ~ earlyLifeTrt
  ) +
  ylim(c(0, 100))

plotPercTogetherP4_P6
plotPercTogetherP4_P11

flexSave(
  baseName = "plotPercTogetherP4_P6",
  plot = plotPercTogetherP4_P6,
  fileType = "png",
  units = "in",
  width = 11.5,
  height = 5
)
flexSave(
  baseName = "plotPercTogetherP4_P11",
  plot = plotPercTogetherP4_P11,
  fileType = "png",
  units = "in",
  width = 11.5,
  height = 5
)


```

```{r}
library('lmerTest')
library('lme4')
mod <- lmer(percTogether ~ earlyLifeTrt*PND + (1 | damID), data = damFrames_byPND)
summary(mod)
anova(mod)
```

