---
title: "LBN_0004 Male Stress"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```
# Set up
Set-up the notebook. This script loads the environment, and contains the names for the data file, and sources the additional scripts that will be used for the analysis.
```{r GetReady}
source("./Scripts/LBN_0002_AGG_setUp.R")
dateToday = Sys.Date()
filterDateForTaskDFs = as.Date("2020-12-01") #Look for breed dates/DOBs after this date
```

# Load Data
The "load_LBN_data" function takes the data folder and excel file name and outputs a list with the processed dataframes. These have the demographic data and any "mutations" (calculated columns) added already.
The output of this chunk is each of these dataframes.
```{r LoadData, include=FALSE}
DFs <- load_LBN_data(
  dataFolder = DataFolder,
  excelName = LBN_DataName
)

Demo_dam <- DFs$Demo_dam
Demo_off <- DFs$Demo_off
Mass_off <- DFs$Mass_off
Maturation_off <- DFs$Maturation_off
EndPara_off <- DFs$EndPara_off
Cycles_off <- DFs$Cycles_off
AcuteStress_off <- DFs$AcuteStress_off
ChronicStress_off <- DFs$ChronicStress_off
LBN_all <- DFs$LBN_all
LBN_data <- DFs$LBN_data
CRH_dam <- DFs$CRH_dam
```

```{r}
stress_LBN_0004_males <- AcuteStress_off %>% 
  filter(
    Cohort == 4,
    Sex == "M",
    !is.na(Stress_treatment)
  )

stress_LBN_0004_males
```

# Body Mass
```{r}
bodyMass_anova <- stress_LBN_0004_males %>%
  rename(
    earlyLifeTrt = Treatment,
    adultTrt = Stress_treatment
  ) %>%
  anova_test(
  dv = "Body_mass_stress",
  between = c("earlyLifeTrt", "adultTrt"),
  type = 3
)

bodyMass_t_test <- t_test(stress_LBN_0004_males, Body_mass_stress ~ Treatment)

bodyMass_plot <- stress_LBN_0004_males %>%
  renameStressGroups() %>%
  combineStressGroups() %>%
  twoWayDotPlot(
    yVar = Body_mass_stress,
    yLab = "body mass (g)",
    fillVar = comboTrt,
    shapeVar = comboTrt
  ) + scale_shape_color()

bodyMass_anova
bodyMass_t_test
bodyMass_plot
```

# Seminal Vesicle Mass
```{r}
semVes_anova <- stress_LBN_0004_males %>%
  rename(
    earlyLifeTrt = Treatment,
    adultTrt = Stress_treatment
  ) %>%
  anova_test(
  dv = "ReproTract_mass",
  between = c("earlyLifeTrt", "adultTrt"),
  type = 3
)

semVes_t_test <- t_test(stress_LBN_0004_males %>% filter(!Mouse_ID == "D033-02_66"), ReproTract_mass ~ Treatment)

semVes_plot <- stress_LBN_0004_males %>%
  renameStressGroups() %>%
  combineStressGroups() %>%
  twoWayDotPlot(
    yVar = ReproTract_mass,
    yLab = "seminal vesicle mass (mg)",
    fillVar = comboTrt,
    shapeVar = comboTrt
  ) + scale_shape_color()

semVes_anova
semVes_t_test
semVes_plot
```

# Testicular Mass
```{r}
testes_anova <- stress_LBN_0004_males %>%
  rename(
    earlyLifeTrt = Treatment,
    adultTrt = Stress_treatment
  ) %>%
  anova_test(
  dv = "Gonad_mass",
  between = c("earlyLifeTrt", "adultTrt"),
  type = 3
)

testes_t_test <- t_test(stress_LBN_0004_males, Gonad_mass ~ Treatment)

testes_plot <- stress_LBN_0004_males %>%
  renameStressGroups() %>%
  combineStressGroups() %>%
  twoWayDotPlot(
    yVar = Gonad_mass,
    yLab = "testicular mass (mg)",
    fillVar = comboTrt,
    shapeVar = comboTrt
  ) + scale_shape_color()

testes_anova
testes_t_test
testes_plot
```
# Adrenal Mass
```{r}
adrenal_anova <- stress_LBN_0004_males %>%
  rename(
    earlyLifeTrt = Treatment,
    adultTrt = Stress_treatment
  ) %>%
  anova_test(
  dv = "Adrenal_mass",
  between = c("earlyLifeTrt", "adultTrt"),
  type = 3
)

adrenal_t_test <- t_test(stress_LBN_0004_males, Adrenal_mass ~ Treatment)

adrenal_plot <- stress_LBN_0004_males %>%
  renameStressGroups() %>%
  combineStressGroups() %>%
  twoWayDotPlot(
    yVar = Adrenal_mass,
    yLab = "adrenal mass (mg)",
    fillVar = comboTrt,
    shapeVar = comboTrt
  ) + scale_shape_color()

adrenal_anova
adrenal_t_test
adrenal_plot
```



```{r}
earlyLifeLegend <- get_legend(
  bodyMass_plot + 
    theme(
      legend.position = "top", 
      legend.text = element_text(size = 11, family = "Arial")
    ) + labs(fill = NULL)
)
maleMassPlot <- plot_grid(
  bodyMass_plot + rremove("x.text") + rremove("x.ticks") + theme(plot.margin = margin(0, 0, 6, 0)),
  adrenal_plot + rremove("x.text") + rremove("x.ticks"),
  semVes_plot + expand_limits(y = 260) + rremove("x.text") + rremove("x.ticks"),
  testes_plot + expand_limits(y = 260) + rremove("x.text") + rremove("x.ticks"),
  labels = c("A", "B", "C","D"),
  ncol = 4,
  label_fontfamily = "Arial"
)

maleMassPlotWLegend <- plot_grid(
  earlyLifeLegend,
  maleMassPlot,
  ncol = 1,
  rel_heights = c(0.1, 1)
)

maleMassPlotWLegend

ggsave(
  file.path(PlotFolder, "LBN_0004_male_masses.pdf"),
  plot = maleMassPlotWLegend,
  device = "pdf",
  width = 7.5,
  height = 2.75,
  units = c("in"),
  useDingbats = FALSE
)

```


