---
title: "Recode LH Samples"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r include=FALSE}
# If can't find it, be sure that the directory is the project directory
# Arrow between notebook and settings gear -> Knit directory
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
```

# Get Second Litter Samples

```{r}
LH_code_2ndLitters <- LH_code %>%
  filter(
    litterNum == 2#,
    # Sac_cycle == "proestrus"
    # Sac_cycle == "diestrus"
  ) %>%
  mutate(
    originalID = as.numeric(as.character(originalID)),
    sampleID = as.numeric(as.character(sampleID))
  ) %>%
  arrange(
    num_ID,
    time
  ) %>%
  relocate(
    originalID,
    sampleID,
    Sac_cycle,
    comboTrt,
    .before = sex
  )
LH_code_2ndLitters
```

# Get IDs and randomly order

```{r}
LH_code_2ndLitters_IDs <- LH_code_2ndLitters %>%
  group_by(
    mouseID
  ) %>%
  summarize(
    num_ID = mean(num_ID, na.rm = TRUE)
  )

set.seed(42)
rows <- sample(nrow(LH_code_2ndLitters_IDs))
LH_code_2ndLitters_IDs <- LH_code_2ndLitters_IDs[rows, ] %>%
  mutate(
    plateOrder = row_number()
  ) %>%
  select(
    -num_ID
  )
LH_code_2ndLitters_IDs
```

```{r eval=FALSE, include=FALSE}
# orders all
LH_code_2ndLitters_ordered <- LH_code_2ndLitters %>%
  left_join(
    LH_code_2ndLitters_IDs,
    by = "mouseID"
  ) %>%
  arrange(
    plateOrder,
    time
  ) %>%
  mutate(
    sampleID = row_number()
  )
LH_code_2ndLitters_ordered
```

# Order morning samples separately
Decide which morning samples to include

```{r}
lastSample <- 0 # starting point for my samples
LH_code_morning <- LH_code_2ndLitters %>%
  filter(
    time == 0
  ) %>%
  left_join(
    LH_code_2ndLitters_IDs,
    by = "mouseID"
  ) %>%
  arrange(
    plateOrder
  ) %>%
  mutate(
    sampleID = row_number() + lastSample
  )
lastSample <- nrow(LH_code_morning)

LH_code_morning
```

# Order all afternoon samples
Keep together by mouse
Decide which should be excluded

```{r}
LH_code_afternoon <- LH_code_2ndLitters %>%
  filter(
    time > 0
  ) %>%
  left_join(
    LH_code_2ndLitters_IDs,
    by = "mouseID"
  ) %>%
  arrange(
    plateOrder
  ) %>%
  mutate(
    sampleID = row_number() + lastSample
  )
LH_code_afternoon
```

# Join together morning and afternoon
Put the two dataframes back together

```{r}
LH_code_all <- rbind(LH_code_morning, LH_code_afternoon) %>%
  arrange(sampleID)
LH_code_all
```


I used the order generated here to identify the number ID that corresponded with the group order to each treatment/cycle group. I added this to my LH_random table that I created in Excel, using a random sequence generator to put 10 proestrus samples and 6 diestrus samples on a plate

```{r}
LH_code_2ndLitters_ordered %>%
  arrange(
    comboTrt,
    Sac_cycle,
    plateOrder
  )
```

```{r}
LH_reordered <- LH_code_2ndLitters %>%
  left_join(
    LH_random %>% select(-comboTrt, Sac_cycle),
    by = "num_ID"
  ) %>%
  relocate(
    Order_total:Order_group,
    .before = earlyLifeTrt
  ) %>%
  arrange(
    Order_total,
    time
  ) %>%
  mutate(
    sampleID = row_number()
  )
mice_originalOrder <- AcuteStress_off %>%
  filter(
    litterNum == 2,
    sex == "F"
  ) %>%
  left_join(
    LH_random %>% select(-comboTrt, Sac_cycle),
    by = "num_ID"
  ) %>%
  relocate(
    Order_total:Order_group,
    .before = earlyLifeTrt
  ) %>%
  arrange(
    Sac_date,
    num_ID
  ) %>%
  mutate(
    origMouseOrder = row_number(),
    boxNumber = floor((origMouseOrder -1) / 9) + 5,
    .after = num_ID
  ) %>%
  mutate(
    boxNumber = ifelse(boxNumber < 9, boxNumber, boxNumber + 1)
  )
mice_originalOrder
LH_reordered <- LH_reordered %>%
  left_join(
    mice_originalOrder %>% select(mouseID, origMouseOrder, boxNumber),
    by = "mouseID"
  ) %>%
  relocate(
    origMouseOrder,
    boxNumber,
    .after = sampleID
  )
saveDFsToExcel(
  fileBaseName = "LH_reordered",
  prefix = filePrefix,
  addDate = dateToday,
  saveFolder = dataOutputFolder,
  LH_IDs = LH_reordered, # use sheetName = df, sheetName2 = df2, sheetName3 = df3 for each df you want to add to a new sheet
  mice = mice_originalOrder
  )
```

