---
title: "AGG Comittee Meeting 2022-11-01"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r eval=FALSE, include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
source("./01-scripts/04-filter-datasets.R")
source("./01-scripts/06-run-LBN-stats.R")
source("./01-scripts/05-make-LBN-plots-modelError-manuscript.R")
```

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

# Set-up
```{r}
figureNum <- 1

pptBaseName <- makeBaseNameFunc("")

plotFolder <- file.path(plotOutputFolder, "2023-11-16")

imgType <-"png"

exportImg <- exportImg_forPurposeFunc(
  imgType = imgType
  , figNumFunc = pptBaseName
  , plotFolder = plotFolder
  , compType = currentCompType
)

exportFullPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
    , width = 11.5
    , height = 5
){
  exportImg(
    plot = plot
    , fileBaseName = baseName
    , figNum = figNum
    , units = "in"
    , width = width
    , height = height
  )
}

exportHalfPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  exportImg(
    plot = plot
    , fileBaseName = baseName
    , figNum = figNum
    , units = "in"
    , width = 5.67
    , height = 5
  )
}

exportThirdPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  exportImg(
    plot = plot
    , fileBaseName = baseName
    , figNum = figNum
    , units = "in"
    , width = 3.6
    , height = 5
  )
}

exportQuarterPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  exportImg(
    plot = plot
    , fileBaseName = baseName
    , figNum = figNum
    , units = "in"
    , width = 3.2
    , height = 5
  )
}

editableImgs <- TRUE
pptAddOneGraph <- function(
    title = slideTitle
    , plot = last_plot()
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_oneGraph(
    officer_ppt, 
    title, 
    plot, 
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddOneTable <- function(
    table
    , title = slideTitle
    , officer_ppt = ppt
    , dontFormat = TRUE
){
  officer_ppt <- addSlide_oneTable(
    officer_ppt, 
    title, 
    table, 
    dontFormat = dontFormat
  )
  return(officer_ppt)
}

pptUneditAddOneGraph <- function(
    title = slideTitle
    , plot = last_plot()
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_oneGraph(
    officer_ppt, 
    title, 
    plot, 
    makeEditable = FALSE
  )
  return(officer_ppt)
}

pptAddTwoGraphs <- function(
    plot1
    , plot2
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_twoGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2,
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddTwoGraphsMoreLeft <- function(
    plot1
    , plot2
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_twoGraphMoreLeft(
    officer_ppt, 
    title, 
    plot1, 
    plot2,
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddGraphTable <- function(
    plot
    , table
    , title = slideTitle
    , officer_ppt = ppt
    , dontFormat = TRUE
){
  officer_ppt <- addSlide_graphTable(
    officer_ppt, 
    title, 
    plot, 
    table,
    makeEditable = editableImgs
    , dontFormat = dontFormat
    , textSize = textSize
  )
  return(officer_ppt)
}

pptAddFourGraphs <- function(
    plot1
    , plot2
    , plot3
    , plot4
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_fourGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2, 
    plot3,
    plot4,
    makeEditable = editableImgs
    )
  return(officer_ppt)
}

pptAddThreeGraphs <- function(
    plot1
    , plot2
    , plot3
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_threeGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2, 
    plot3,
    makeEditable = editableImgs
    )
  return(officer_ppt)
}

pptAddStats <- function(
    statsText
    , officer_ppt = ppt
){
  officer_ppt <- addStatsToBottom(
    officer_ppt,
    statsText
  )
}

pptAddTwoStats <- function(
    statsText1
    , statsText2
    , officer_ppt = ppt
){
  officer_ppt <- addTwoStatsToGraphs(
    officer_ppt,
    statsText1,
    statsText2
  )
}

pptAddSectionHead <- function(
    title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_sectionHead(
    officer_ppt
    , title
  )
}



```

```{r}
# make powerpoint and title slide
ppt <- read_pptx("genericPPT.pptx")
ppt <- add_slide(ppt, layout = "Title Slide")

# layout_properties(ppt, layout="Title Slide")

subText <- "Amanda Gibson\nHope\nNov 2023"
ppt <- ph_with(
  ppt,
  value = subText,
  location = ph_location_label("Subtitle 2")
)


# Run this function to save the PPT file to the disk
# On windows, don't run if the PPT file is open
savePPT <- makeSavePPTFunc(
  presPPT = ppt
  , presFolder = plotFolder
  , presFileName = "AGG_LBN_Hope"
  , addDate = TRUE
)
```


# Dam exits - demo
```{r}
fig_demoDamBehavior_byDay <- damBehavior_byPND %>%
  plotDamBehavior(
    yVar = Num_exits
    , yLab = "mean # of exits"
    , fontSize = textSize
    , addTriangleForMean = FALSE
    , colorByDam = TRUE
    , dotSize = 1
    , zoom_y = TRUE
    , ymax = 50
    , ymin = 0
    , showMean = FALSE
    , addVertError = FALSE
    , subset = TRUE
    , numPerGroup = 4
  )

fig_demoDamBehavior_mean <- damBehavior_byDam %>%
  plotDamBehavior(
    yVar = Num_exits
    , yLab = "mean # of exits"
    , fontSize = textSize
    , addTriangleForMean = FALSE
    , colorByDam = TRUE
    , dotSize = 3
    , zoom_y = TRUE
    , ymax = 50
    , ymin = 0
    , showMean = FALSE
    , addVertError = FALSE
    , subset = TRUE
    , numPerGroup = 4
  ) +
  facet_wrap(
    ~earlyLifeTrt
    , scales = "free_x"
  ) +
  theme(
    axis.text.x = element_blank()
    , axis.ticks.x = element_blank()
  )

figDemoDamBehavior <- plot_grid(
  fig_demoDamBehavior_byDay
  , fig_demoDamBehavior_mean
  , rel_widths = c(3, 1)
  , align = c("h")
  , axis = c("tb")
)

figDemoDamBehavior

fileBaseName <- "demoDamBehavior"
slideTitle <- "LBN dams had more exits from the nest than STD dams"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

# Dam exits - mean normal color


## nparLD

```{r}
library(nparLD)
```

```{r}
numExits_nparLD <- f1.ld.f1(
  y = damBehavior_byPND$Num_exits
  , time = damBehavior_byPND$PND
  , group = damBehavior_byPND$earlyLifeTrt
  , subject = damBehavior_byPND$damID
  , time.name = "PND"
  , group.name = "early-life trt"
)

numExits_nparLD
```

```{r}
fig_damBehavior_byDay <- damBehavior_byPND %>%
  plotDamBehavior(
    yVar = Num_exits
    , yLab = "mean # of exits"
    , fontSize = textSize
    , addTriangleForMean = FALSE
    , colorByDam = TRUE
    , redMean = TRUE
    , dotSize = 1
    , zoom_y = TRUE
    , ymax = 50
    , ymin = 0
    , showMean = TRUE
    , addVertError = FALSE
    , lineAlpha = 0.2
    , dotAlpha = 0.4
  ) +
  stat_summary(
    geom = "linerange", 
    fun.data = mean_se,
    size = 0.6,
    position = "identity",
    show.legend = FALSE
    # , color = "grey80"
  ) +
  stat_summary(
    geom = "errorbar", 
    fun.min = mean, 
    fun = mean, 
    fun.max = mean, 
    width = .7,
    size = .6,
    position = "identity",
    # color = "grey80"
  )
  

fig_damBehavior_byDay
```

```{r}
fig_damBehavior_meanExits <- damBehavior_byDam %>%
  plotDamBehavior(
    yVar = Num_exits
    , yLab = "mean # of exits"
    , fontSize = textSize
    , addTriangleForMean = FALSE
    , colorByDam = TRUE
    , dotSize = 3
    , zoom_y = TRUE
    , ymax = 50
    , ymin = 0
    , showMean = TRUE
    , addVertError = TRUE
  ) +
  facet_wrap(
    ~earlyLifeTrt
    , scales = "free_x"
  ) +
  theme(
    axis.text.x = element_blank()
    , axis.ticks.x = element_blank()
  )
fig_damBehavior_meanExits
```


```{r eval=FALSE, include=FALSE}
fig_damBehavior_meanExits <- damBehavior_byDam %>%
  unite(
    fullRec,
    earlyLifeTrt,
    cohort,
    sep = "-",
    remove = FALSE
  ) %>%
  scatterPlot_general(
    xVar = earlyLifeTrt
    , xLab = NULL
    , yVar = Num_exits
    , yLab = "mean # exits"
    , fillVar = fullRec
    , fillLimits = c("STD-7", "STD-9", "LBN-7", "LBN-9")
    , fillValues = c("grey", "white", "darkcyan", "lightblue1")
    , textSize = textSize
    , dotSize = dotSize
    , addMean = FALSE
    , addSE = FALSE
    , zoom_y = TRUE
    , ymax = 50
    , ymin = 0
  ) +
  facet_wrap(
    ~earlyLifeTrt
    , scales = "free_x"
  ) +
  theme(
    axis.text.x = element_blank()
    , axis.ticks.x = element_blank()
  ) +
  stat_summary(
    geom = "linerange", 
    fun.data = mean_se,
    size = 0.6,
    position = "identity",
    show.legend = FALSE
    , data = damBehavior_byDam
    , aes(x = earlyLifeTrt, y = Num_exits)
    , inherit.aes = FALSE
  ) +
  stat_summary(
    geom = "errorbar", 
    fun.min = mean, 
    fun = mean, 
    fun.max = mean, 
    width = .7,
    size = .6,
    position = "identity"
    , data = damBehavior_byDam
    , aes(x = earlyLifeTrt, y = Num_exits)
    , inherit.aes = FALSE
  )

fig_damBehavior_meanExits
```

```{r}
figDamBehavior <- plot_grid(
  fig_damBehavior_byDay
  , fig_damBehavior_meanExits
  , rel_widths = c(3, 1)
  , align = c("h")
  , axis = c("tb")
)

figDamBehavior

fileBaseName <- "damBehavior"
slideTitle <- "LBN dams had more exits from the nest than STD dams"
ppt <- pptAddOneGraph()
```



# Cycles

## Demonstration

```{r}
fig_cyclesDemo <- cyclesLong %>% 
  filter(mouseID == 903) %>%
  addCycleStartCol() %>%
  addPNDForCyles() %>%
  plotCycleTraces_single(day = PND, fontSize =  textSize)

fig_cyclesDemo_red <- fig_cyclesDemo +
  geom_point(aes(color = isStartCycle, alpha = isStartCycle))+
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red", "STD" = "grey", "LBN" = "black"))+
  scale_alpha_manual(values = c("FALSE" = .2, "TRUE" = 1))

fig_cyclesDemo
slideTitle <- "903"
ppt <- pptAddOneGraph()
ppt <- pptAddTwoGraphsMoreLeft(fig_cyclesDemo, fig_cyclesDemo)

fig_cyclesDemo_red
ppt <- pptAddOneGraph()
ppt <- pptAddTwoGraphsMoreLeft(fig_cyclesDemo_red, fig_cyclesDemo_red)
```



## Example traces 
```{r}

STD_cycles <- cyclesFiltered %>%
  filter(
    earlyLifeTrt == "STD"
  ) %>%
  getRandomSubjects(mouseID, 6, seed = 49) %>%
  mutate(
    mouseByRow = row_number()
  ) %>%
  makeCyclesLong() %>%
  addCycleStartCol() %>%
  addPNDForCyles() %>%
  plotCycleTraces(
    colorValues = c("grey30", "cyan4")
    , fontSize = textSize
    , removeFacets = TRUE
    , ncol = 2
    , nrow = 3
    , day = PND
    , breakSeq = seq(70, 90, 5)
    , MouseID = mouseByRow
    , facetDir = "v"
  ) + theme(
    panel.border = element_rect(color = "lightgrey", fill = NA)
    , panel.spacing.x=unit(2, "lines")
    , plot.margin = margin(0, 1, 0, 1, "cm")
  )

LBN_cycles <- cyclesFiltered %>%
  filter(
    earlyLifeTrt == "LBN"
  ) %>%
  getRandomSubjects(mouseID, 6, seed = 49) %>%
  mutate(
    mouseByRow = row_number()
  ) %>%
  makeCyclesLong() %>%
  addCycleStartCol() %>%
  addPNDForCyles() %>%
  plotCycleTraces(
    colorValues = c("grey30", "cyan4")
    , fontSize = textSize
    , removeFacets = TRUE
    , ncol = 2
    , nrow = 3
    , day = PND
    , breakSeq = seq(70, 90, 5)
    , MouseID = mouseByRow
    , facetDir = "v"
  ) + theme(
    panel.border = element_rect(color = "lightgrey", fill = NA)
    , panel.spacing.x=unit(2, "lines")
    , plot.margin = margin(0, 1, 0, 1, "cm")
  )

STD_cycles
LBN_cycles

slideTitle <- "LBN did not change estrous cycles"
ppt <- pptAddTwoGraphs(
  STD_cycles
  , LBN_cycles
)
```

# Corticosterone
```{r}
cortFilteredPro %>%
  mutate(
    comboTrt = factor(comboTrt, levels = c("STD-CON", "LBN-CON", "STD-ALPS", "LBN-ALPS"))
  ) %>%
  manuscriptCortPlotFunc(
    fontSize = textSize
    , dotSize = dotSize
    # , zoom_y = FALSE
    , zoom_y = TRUE
    , ymin = 0
    , ymax = 500
    , plotMean = FALSE
    , plotSE = FALSE
    , yUnitsNewLine = FALSE
  )() +
  scale_y_continuous(
    breaks = c(0, 100, 200, 300, 400, 500)
  ) +
  plotError_LMM_aes(
    cort_lmm_error_f %>%
      filter(
        Sac_cycle == "proestrus"
      ) %>%
      mutate(
        time = ifelse(
          time == 0
          , time - 1.5
          , time + 1.5
        )
      )
    , xVar = time
    , nudgeErrorLine = 0
    , nudgeMeanLine = 0
    , meanBarWidth = 1
    , color = comboTrt
  )

slideTitle <- "pro cort"
ppt <- pptAddOneGraph()
```

# LH

## Demo

```{r}
samplingLH <- LHFilteredPro %>%
    filter(
      mouseID %in% c(960)
      , time > 0
    ) %>%
    LHPlot_noMean(
        fontSize = textSize
        , dotSize = dotSize
        , zoom_y = TRUE
        , ymin = 0
        , ymax = 40
      ) + theme(
        legend.position = "none"
      ) + 
        geom_hline(
          yintercept = 3
          , color = "red"
          , alpha = 0.3
        )

samplingLH

exportFullPPTSlide(plot = samplingLH, baseName = "LH_demo", 2, width = 7.36, height = 3.5)

samplingLH_both <- LHFilteredPro %>%
    filter(
      mouseID %in% c(960, 916)
      , time > 0
    ) %>%
    LHPlot_noMean(
        fontSize = textSize
        , dotSize = dotSize
        , zoom_y = TRUE
        , ymin = 0
        , ymax = 40
      ) + theme(
        legend.position = "none"
      ) + 
        geom_hline(
          yintercept = 3
          , color = "red"
          , alpha = 0.3
        )

samplingLH_both

exportFullPPTSlide(plot = samplingLH_both, baseName = "LH_demo_both", 2, width = 7.36, height = 3.5)
```

## Amplitude

```{r}
nonEphysMice <- surgedDF %>%
  filter(
    !is.na(LH_hr7.5) & !is.na(LH_hr5.5)
  )

sampling_percSurgedPlot <- nonEphysMice %>%
  propSurgedPlotCombo_forSBN(
    fontSize = textSize
  )

sampling_percSurgedPlot
```

```{r}
surgedPlot <- nonEphysMice %>%
  mutate(
    comboTrt = factor(comboTrt, levels = c("STD-CON", "LBN-CON", "STD-ALPS", "LBN-ALPS"))
  ) %>%
  scatterPlotComboTrt_surgeAmp(
    yVar = maxLH
    , yLab = "LH (ng/mL)"
    , dotSize = dotSize
    , fontSize = textSize
    , addMeanSE = FALSE
    , surgeMin = 3
  )
```

```{r}
plot_grid(
  surgedPlot
  , sampling_percSurgedPlot
  , nrow = 1
  , rel_widths = c(1.8, 1)
)
slideTitle <- "LH"
ppt <- pptAddOneGraph()
```



```{r}
surgeAmp <- nonEphysMice %>% plotLHAmp_comboTrt(
  surgeMin, 
  textSize = textSize, 
  dotSize = dotSize,
  angleX = FALSE,
  # angleX = TRUE,
  addSurgeMinLine = TRUE
)

surgeAmp
slideTitle <- "surge amplitude"
ppt <- pptAddOneGraph()
```

```{r}
surgeAmp_byAdultTrt <- nonEphysMice %>% plotLHAmp_comboTrt_byEarlylife(
  surgeMin, 
  textSize = textSize, 
  dotSize = dotSize,
  angleX = FALSE,
  # angleX = TRUE,
  addSurgeMinLine = TRUE
) +
  facet_wrap(
    ~ adultTrt
    , nrow = 1
    , scales = "free_x"
  )

surgeAmp_byAdultTrt
```

```{r}
plot_grid(
  surgeAmp_byAdultTrt
  , sampling_percSurgedPlot +
    facet_wrap(
      ~adultTrt + earlyLifeTrt
      , scales = "free_x"
      , nrow = 1
    ) + # emphasize the comparison between early-life trt, not adult treat
    theme(
      axis.text.x = element_blank()
      , panel.spacing.x=unit(-.2, "lines")
      , strip.text = element_blank()
    )
    # scale_x_discrete(
    #     labels = c(
    #       "STD-CON" = "STD"
    #       , "STD-ALPS" = "STD"
    #       , "LBN-CON" = "LBN"
    #       , "LBN-ALPS" = "LBN"
    #     
    #   ))
    # facet_wrap(~earlyLifeTrt, scales = "free_x") + 
    # scale_x_discrete(
    #     labels = c(
    #       "STD-CON" = "CON"
    #       , "STD-ALPS" = "ALPS"
    #       , "LBN-CON" = "CON"
    #       , "LBN-ALPS" = "ALPS"
    #     
    #   ))
  , nrow = 1
  , rel_widths = c(2, 1)
  , axis = "tb"
  , align = "h"
)
slideTitle <- "LH"
ppt <- pptAddOneGraph()
```

```{r}
surgeAmp_stacked <- nonEphysMice %>% plotLHAmp_comboTrt(
  surgeMin, 
  textSize = textSize, 
  dotSize = dotSize,
  angleX = FALSE,
  # angleX = TRUE,
  addSurgeMinLine = TRUE
) +
  facet_wrap(
      ~earlyLifeTrt
      ,ncol = 1
    )

surgeAmp_stacked
slideTitle <- "surge amplitude"
ppt <- pptAddTwoGraphsMoreLeft(surgeAmp_stacked, sampling_percSurgedPlot)
ppt <- pptAddTwoGraphs(surgeAmp_stacked, sampling_percSurgedPlot)
```
```{r}
plot_grid(
  surgeAmp_stacked
  , sampling_percSurgedPlot
  , nrow = 1
  , rel_widths = c(1.5, 1)
)
ppt <- pptAddOneGraph()
```


# Cort administration

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

```{r include=FALSE}
BD_filePath <- normalizePath("C:\\Users\\percs\\OneDrive - Umich\\Moenter lab\\Bo Dong\\BD_cort-admin_AGG.xlsx")
BD_fileInfo <- loadExcelSheet_fromFile(BD_filePath, "fileInfo")
BD_cycleDir <- BD_fileInfo$cycleImgFolder[1]

BD_damInfo <- loadExcelSheet_fromFile(BD_filePath, "DamInfo") %>%
  makeFactors("damID")

BD_offspringInfo <- loadExcelSheet_fromFile(BD_filePath, "OffspringInfo") %>% makeFactors(c("mouseID", "damID"))

BD_offspringInfo <- BD_offspringInfo %>%
  left_join(
    BD_damInfo,
    by = "damID"
  ) %>%
  mutate(
    cyclingFolderPath = BD_cycleDir,
    earlyLifeTrt = NA,
    maxLH = NA
  )

BD_cycles <- loadExcelSheet_fromFile(BD_filePath, "Cycles_off") %>%
  makeFactors(
    "mouseID"
  )%>%
  mutate(
    num_ID = cycleID
  )


# BD_allInfo <- BD_offspringInfo %>%
#   left_join(
#     BD_cycles,
#     by = "mouseID"
#   ) %>%
#   left_join(
#     BD_sacrifice,
#     by = "mouseID"
#   )

BD_cycles <- BD_cycles %>%
  left_join(
    BD_offspringInfo,
    by = "mouseID"
  )

BD_damInfo
BD_offspringInfo
BD_cycles
# BD_allInfo
```

```{r}
BD_filePrefix  <-  "BD_cortAdmin_"
BD_width <- 11.5
BD_height <- 5
```

## Data 

```{r}
source(file.path(scriptsFolder, "cortAdmin-get-datasets.R"))
BD_cort1 <- BD_cort1 %>%
  mutate(ateAllNutella = ifelse(is.na(ateNutella), "ate all Nutella", "did not eat all Nutella" ))
BD_cort2 <- BD_cort2 %>%
  mutate(ateAllNutella = ifelse(is.na(ateNutella), "ate all Nutella", "did not eat all Nutella" ))
BD_cort3 <- BD_cort3 %>%
  mutate(ateAllNutella = ifelse(is.na(ateNutella), "ate all Nutella", "did not eat all Nutella" ))
BD_cort4 <- BD_cort4 %>%
  filter(
    Sac_date == "2022-05-27"
  ) %>%
  mutate(ateAllNutella = ifelse(is.na(ateNutella), "ate all Nutella", "did not eat all Nutella" ))
```

## Pilot 1

```{r fig.width=11.5}
nutellaCortPlot1 <- BD_cort1 %>%
  cortPlot(
    pointSize = dotSize,
    fontSize = textSize,
    plotMean = FALSE, # we don't have enough data yet for mean/se to be helpful
    plotSE = FALSE,
    groupVar = dosage, # group by the dosage; this is why it needs to be a factor
    xBreaks = c(0, 0.5, 1, 3, 5), # set the axis ticks at these values
    xLabels = c("0", "0.5", "1", "3", "5"), # label the axis with the actual time values
    lineTypeGuide = "",
    positionDodge = 0.2 #this controls the spread of the data visually
  ) +
  facet_wrap(
    ~ateAllNutella # this splits the graph by those that did or did not eat Nutella
  ) +
  labs(
    x = "time since administration (h)" # add a title to the x axis
  ) +
  pilotDosageFillShape(c(0, 10, 20, 50))

nutellaCortPlot1
```

```{r fig.width=11.5}
nutellaCortPlot1_ateAll <- BD_cort1 %>%
  filter(
    ateAllNutella == "ate all Nutella"
  ) %>%
  cortPlot(
    pointSize = dotSize,
    fontSize = textSize,
    plotMean = FALSE, # we don't have enough data yet for mean/se to be helpful
    plotSE = FALSE,
    groupVar = dosage, # group by the dosage; this is why it needs to be a factor
    xBreaks = c(0, 0.5, 1, 3, 5), # set the axis ticks at these values
    xLabels = c("0", "0.5", "1", "3", "5"), # label the axis with the actual time values
    lineTypeGuide = "",
    positionDodge = 0.2 #this controls the spread of the data visually
  ) +
  facet_wrap(
    ~ateAllNutella # this splits the graph by those that did or did not eat Nutella
  ) +
  labs(
    x = "time since administration (h)" # add a title to the x axis
  ) +
  pilotDosageFillShape(c(0, 10, 20, 50))

nutellaCortPlot1_ateAll
```

## Pilot 2

```{r fig.width=11.5}
nutellaCortPlot2 <- BD_cort2 %>%
  cortPlot(
    pointSize = dotSize,
    fontSize = textSize,
    plotMean = FALSE, # we don't have enough data yet for mean/se to be helpful
    plotSE = FALSE,
    groupVar = dosage, # group by the dosage; this is why it needs to be a factor
    xBreaks = c(0, 0.5, 1, 3, 5), # set the axis ticks at these values
    xLabels = c("0", "0.5", "1", "3", "5"), # label the axis with the actual time values
    lineTypeGuide = "",
    positionDodge = 0.2 #this controls the spread of the data visually
  ) +
  facet_wrap(
    ~ateAllNutella # this splits the graph by those that did or did not eat Nutella
  ) +
  labs(
    x = "time since administration (h)" # add a title to the x axis
  ) +
  pilotDosageFillShape(c(0, 3, 10))

nutellaCortPlot2
```
## Pilot 3

```{r fig.width=11.5}
nutellaCortPlot3<- BD_cort3 %>%
  cortPlot(
    pointSize = dotSize,
    fontSize = textSize,
    plotMean = FALSE, # we don't have enough data yet for mean/se to be helpful
    plotSE = FALSE,
    groupVar = dosage, # group by the dosage; this is why it needs to be a factor
    xBreaks = c(0, 0.5, 1, 3, 5), # set the axis ticks at these values
    xLabels = c("0", "0.5", "1", "3", "5"), # label the axis with the actual time values
    lineTypeGuide = "",
    positionDodge = 0.2 #this controls the spread of the data visually
    , zoom_y = TRUE
    , ymin = 0
    , ymax = 1000
  ) +
  facet_wrap(
    ~ateAllNutella # this splits the graph by those that did or did not eat Nutella
  ) +
  labs(
    x = "time since administration (h)" # add a title to the x axis
  ) +
  pilotDosageFillShape(c(0, 0.5, 1))

nutellaCortPlot3
```

## 2 mg/kg
```{r}
nutellaALPS_cortPlot <- BD_comboNutALPS %>%
  cortPlot(
    pointSize = dotSize,
    fontSize = textSize,
    plotMean = FALSE, # we don't have enough data yet for mean/se to be helpful
    plotSE = FALSE,
    groupVar = cortNutTrt, # group by the dosage; this is why it needs to be a factor
    xBreaks = c(0, 0.5, 1, 3, 5), # set the axis ticks at these values
    xLabels = c("0", "0.5", "1", "3", "5"),
    lineTypeGuide = "",
    positionDodge = 0.2, #this controls the spread of the data visually
    zoom_y = TRUE,
    ymax = 1000,
    ymin = 0
  ) +
  # facet_wrap(
  #   ~ateAllNutella # this splits the graph by those that did or did not each Nutella
  # ) +
  labs(
    x = "time since 1st administration (h)" # add a title to the x axis
  ) + 
  theme(
    legend.position = "top"
  )  +
  scale_color_manual(
    "treatment",
    labels = c(
      "ALPS" = "ALPS",
      "0" = "0mg/kg",
      "2" = "2mg/kg"
    ),
    values = c(
      "ALPS"="black",
      "0" = "black",
      "2" = "black"
    )
  )+
  scale_fill_manual(
    "treatment",
    labels = c(
      "ALPS" = "ALPS",
      "0" = "0mg/kg",
      "2" = "2mg/kg"
    ),
    values = c(
      "ALPS"="grey80",
      "0" = "white",
      "2" = "black"
    )
  )+
  scale_shape_manual(
    "treatment",
    labels = c(
      "ALPS" = "ALPS",
      "0" = "0mg/kg",
      "2" = "2mg/kg"
    ),
    values = c(
      "ALPS"=23,
      "0" = 21,
      "2" = 21
    )
  ) + scale_linetype_manual(
    "treatment",
    labels = c(
      "ALPS" = "ALPS",
      "0" = "0mg/kg",
      "2" = "2mg/kg"
    ),
    values = c(
      "ALPS"="dotted",
      "0" = "solid",
      "2" = "solid"
    )
  )

nutellaALPS_cortPlot
```


```{r}
nutellaCortPlot1

slideTitle <- "Pilot 1"
ppt <- pptAddOneGraph()
```

```{r}
nutellaCortPlot2

slideTitle <- "Pilot 2"
ppt <- pptAddOneGraph()
```

```{r}
nutellaCortPlot3

slideTitle <- "Pilot 3"
ppt <- pptAddTwoGraphs(nutellaCortPlot3, nutellaCortPlot1_ateAll)
```

```{r}
nutellaALPS_cortPlot

slideTitle <- "2mg/kg and ALPS"
ppt <- pptAddOneGraph()

```




# Example plot for teaching sample

```{r}
# Create an empty dataframe
df <- data.frame(time = numeric(), potential = numeric())

# Adding x and y axis limits
p <- ggplot(df, aes(time, potential)) +
  theme(axis.text.x=element_blank()) +
  scale_x_continuous(limits = c(0, 100), expand = c(0,0)) +
  scale_y_continuous(limits = c(-100, 80), breaks = seq(-100, 80, by = 20)) +
  
  # Adding horizontal lines
  geom_hline(aes(yintercept = 0),     color = "grey", linetype = "dotted") +
  geom_hline(aes(yintercept = -71.7), color = "black", linetype = "dashed") +
  geom_hline(aes(yintercept = -90.1), color = "#6D6ECB", linetype = "dashed") +
  geom_hline(aes(yintercept = 61),    color = "#8B4386", linetype = "dashed") +
  geom_hline(aes(yintercept = -63.5),    color = "#44A043", linetype = "dashed") +
  
  # Add a solid line from 0 to 25
  geom_line(data = data.frame(time = c(0, 25), potential = rep(-71.7, 2)), 
            aes(time, potential), color = "red", linetype = "solid") +
   
  # Labels for the axes
  labs(x = "Time (ms)", y = "Membrane potential (mV)") +
  
  textTheme(size = textSize) +
  boxTheme()

# Create the plot
p
```

```{r}
# Create an empty dataframe
df <- data.frame(time = numeric(), potential = numeric())

# Adding x and y axis limits
p_GnRH <- ggplot(df, aes(time, potential)) +
  theme(axis.text.x=element_blank()) +
  scale_x_continuous(limits = c(0, 100), expand = c(0,0)) +
  scale_y_continuous(limits = c(-100, 80), breaks = seq(-100, 80, by = 20)) +
  
  # Adding horizontal lines
  geom_hline(aes(yintercept = 0),     color = "grey", linetype = "dotted") +
  geom_hline(aes(yintercept = -71.7), color = "black", linetype = "dashed") +
  geom_hline(aes(yintercept = -90.1), color = "#6D6ECB", linetype = "dashed") +
  geom_hline(aes(yintercept = 61),    color = "#8B4386", linetype = "dashed") +
  geom_hline(aes(yintercept = -39.2),    color = "#44A043", linetype = "dashed") +
  
  # Add a solid line from 0 to 25
  geom_line(data = data.frame(time = c(0, 25), potential = rep(-71.7, 2)), 
            aes(time, potential), color = "red", linetype = "solid") +
   
  # Labels for the axes
  labs(x = "Time (ms)", y = "Membrane potential (mV)") +
  
  textTheme(size = textSize) +
  boxTheme()

# Create the plot
p_GnRH
```

```{r}
p
slideTitle <- "Reverse potentials and membrane potentials"
ppt <- pptAddTwoGraphs(p, p_GnRH)
```







# Dams - number of exits

```{r}
plot_grid(
  figDams_exits
  , figDams_meanExits
  , rel_widths = c(3, 1)
  , align = c("hv")
)

fileBaseName <- "damBehavior"
slideTitle <- "LBN dams had more exits from the nest than STD dams"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  coef(summary(numExits_nb.GLMM)) %>%
    as.data.frame() %>%
    rownames_to_column("effect"),
  dontFormat = FALSE
)
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  numExits_nb.GLMM_jointTest,
  dontFormat = FALSE
)
```

# Dams - % off nest

```{r}
plot_grid(
  figDams_offNest
  , figDams_meanOffNest
  , rel_widths = c(3, 1)
  , align = c("hv")
)

fileBaseName <- "damBehavior_percOff"
slideTitle <- "LBN did not alter the percent of time spent off the nest"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  percOffNest_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

# Dam corticosterone

```{r}
figDamsD

fileBaseName <- "damCort"
slideTitle <- "PND11 corticosterone was not different after LBN"
exportHalfPPTSlide()
ppt <- pptAddTwoGraphs(
  figDamsD
  , figDamsD
)

ppt <- addStatsToBottom(ppt, paste0(
  "t = "
  , round(damCort_t.Test$statistic[[1]], 3)
  , ", p = "
  , round(damCort_t.Test$p.value[[1]], 3)
  )
)
```

# Dam mass

```{r}
figDams_mass

fileBaseName <- "damMass"
slideTitle <- "LBN dams have a higher body mass than STD dams"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_twoTables(
  ppt,
  slideTitle,
  damMass_lmm$anova_table %>% as.data.frame(),
  damMass_lmm_EMM.earlyLifeTrt.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

# Offspring mass 

```{r}
figOffA

fileBaseName <- "offMass"

exportFullPPTSlide()
slideTitle <- "Offspring mass"
ppt <- pptAddOneGraph()
```

# Offspring maturation

```{r}
figOffAge_model

fileBaseName <- "matAge"

exportFullPPTSlide()
slideTitle <- "LBN does not alter age for external markers of puberty"
ppt <- pptAddOneGraph()
```
```{r}
figOffMass_model

fileBaseName <- "matMass"

exportFullPPTSlide()
slideTitle <- "LBN does not alter mass at external markers of puberty"
ppt <- pptAddOneGraph()
```

```{r}
slideTitle <- "Vaginal opening"
ppt <- addSlide_twoTables(
  ppt,
  slideTitle,
  VO_age_lmm %>% formatMixedLMM_ppt(),
  VO_mass_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```
```{r}
slideTitle <- "First Estrus"
ppt <- addSlide_twoTables(
  ppt,
  slideTitle,
  Estrus_age_lmm %>% formatMixedLMM_ppt(),
  Estrus_mass_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```
```{r}
slideTitle <- "Preputial Separation"
ppt <- addSlide_twoTables(
  ppt,
  slideTitle,
  PreputialSep_age_lmm %>% formatMixedLMM_ppt(),
  PreputialSep_mass_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

# AGD

```{r}
plot_grid(
  figOff_femaleAGD
  , figOff_maleAGD
  , align = "hv"
  , axis = "tblr"
)

fileBaseName <- "matAGD"

exportFullPPTSlide()
slideTitle <- "LBN does not alter adult AGD"
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  AGD_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

# Estrous cycle

```{r}
plot_grid(
  figCycles_numCycles_model
  , figCycles_lengthLog_model
  , figCyclesD
  , ncol = 3
  , align = "h"
  , axis = "bt"
  , rel_widths = c(1, 1, 2)
)

fileBaseName <- "cyclesFeatures"

exportFullPPTSlide()
slideTitle <- "LBN does not alter estrous cyclicity"
ppt <- pptAddOneGraph()
```

```{r}
slideTitle <- "Number of cycles"
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  numCycles_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
slideTitle <- "Cycle length"
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  lengthCycles_log_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
slideTitle <- "Cycle distribution"
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  cycles_ChiSq,
  dontFormat = FALSE
)
```


# Cort

```{r}
figCortLogA

fileBaseName <- "cortMales"

exportFullPPTSlide()
slideTitle <- "LBN does not alter corticosterone response to ALPS in males"
ppt <- pptAddOneGraph()
```

```{r}
figCortLogB

fileBaseName <- "cortDi"

exportFullPPTSlide()
slideTitle <- "LBN does not alter corticosterone response to ALPS in diestrous females"
ppt <- pptAddOneGraph()
```

```{r}
figCortLogC

fileBaseName <- "cortPro"

exportFullPPTSlide()
slideTitle <- "LBN does not alter corticosterone response to ALPS in proestrous females"
ppt <- pptAddOneGraph()
```

```{r}
slideTitle <- "LBN does not alter corticosterone response to ALPS"
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  cort_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
slideTitle <- "ALPS increases afternoon serum corticosterone"
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  cort_lmm_emm_adultTrtTime.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

```{r}
slideTitle <- "Corticosterone varies with hormone status"
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  cort_lmm_emm_hormoneStatusTime.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

```{r}
cortFiltered_M_DiPro %>%
  manuscriptCortPlotFunc(
    fontSize = textSize
    , dotSize = dotSize
    , zoom_y = FALSE
    , plotMean = FALSE
    , plotSE = FALSE
    , pointAlpha = 0.1
    , lineAlpha = 0.1
  )() +
  facet_wrap(
    ~hormoneStatus
  ) +
  cortScale +
 plotError_LMM(
   cort_lmm_emm_hormoneStatusTime %>%
   as_data_frame() %>%
  rename(
    y = response
  ) %>%
  mutate(
    lower = y - SE
    , upper = y + SE
    ,time = ifelse(
      time == 0
      , time - 1.5
      , time + 1.5
    )
  )
  , xVar = time
  , nudgeErrorLine = 0
  , nudgeMeanLine = 0
  , meanBarWidth = 1
  , color = "black"
)


ppt <- pptAddOneGraph()
```



# Body mass - AM

```{r}
figMassFacetA_model

fileBaseName <- "bodyMassAM"

exportFullPPTSlide()
slideTitle <- "There were some differences in body mass between male treatment groups"
ppt <- pptAddOneGraph()
```
```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  bodyMassAM_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
slideTitle <- "Males that went on to receive ALPS were larger than those that received CON"
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  bodyMassAM_lmm_emm_adultTrt.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

```{r}
slideTitle <- "LBN males were trending towards being smaller than STD males"
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  bodyMassAM_lmm_emm_earlyLifeTrt.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

# % change body mass

```{r}
figMassFacetB_perc_model

fileBaseName <- "bodyMassPercChange"

exportFullPPTSlide()
slideTitle <- "ALPS mice lost more body mass than CON mice during the paradigm"
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  percChangeBodyMass_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  percChangeBodyMass_lmm_emm_adultTrt.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

# Adrenal mass

```{r}
figMassFacetC_model

fileBaseName <- "adrenalMass"

exportFullPPTSlide()
slideTitle <- "Females have larger adrenal glands than males"
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  adrenalMass_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  adrenalMass_lmm_emm_hormoneStatus.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

# Seminal vesicle mass

```{r}
figMassFacetD_male_model

fileBaseName <- "seminalVesicleMass"

exportFullPPTSlide()
slideTitle <- "Relative seminal vesicle mass is larger in LBN males"
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  seminalVesicle_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  seminalVesicle_lmm_emm_earlyLifeTrt.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

# Uterine mass

```{r}
figMassFacetD_female_model

fileBaseName <- "uterineMass"

exportFullPPTSlide()
slideTitle <- "Proestrus females have larger uteri than diestrus females (... by definition)"
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  uterineMass_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  uterineMass_lmm_emm_stage.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

# Testicular mass

```{r}
figMass_testicular_model

fileBaseName <- "testicularMass"

exportFullPPTSlide()
slideTitle <- "ALPS males have a smaller relative testicular mass"
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  testicularMass_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  testicularMass_lmm_emm_adultTrt.pairs %>% as.data.frame(),
  dontFormat = FALSE
)
```

# LH results

```{r}
ephys_percSurgedPlot <- surgedDF %>%
  filter(
    is.na(LH_hr7.5) & !is.na(LH_hr5.5)
  ) %>%
  propSurgedPlotCombo_forSBN(
    fontSize = textSize
  )

ephys_percSurgedPlot

fileBaseName <- "percSurgedEphys"

exportFullPPTSlide()
```

```{r}
ephysMice <- surgedDF %>%
  filter(
    is.na(LH_hr7.5) & !is.na(LH_hr5.5)
  )
ephysLH <- LHFilteredPro %>%
  filter(
    mouseID %in% ephysMice$mouseID
    , time > 0
  ) %>%
  plotLHFunc(
    c(1)
    , fontSize = 16
    , dotSize = dotSize
    , addSurgeLine = TRUE
  )()

ephysLH

fileBaseName <- "percSurgedEphys_trace"
exportFullPPTSlide()
```
```{r}
nonEphysMice <- surgedDF %>%
  filter(
    !is.na(LH_hr7.5) & !is.na(LH_hr5.5)
  )
samplingLH <- LHFilteredPro %>%
  filter(
    mouseID %in% nonEphysMice$mouseID
    , time > 0
  ) %>%
  plotLHFunc(
    c(1)
    , fontSize = 16
    , dotSize = dotSize
    , addSurgeLine = TRUE
  )()

samplingLH

```

```{r}
sampling_percSurgedPlot <- surgedDF %>%
  filter(
    !is.na(LH_hr7.5) & !is.na(LH_hr5.5)
  ) %>%
  propSurgedPlotCombo_forSBN(
    fontSize = textSize
  )

sampling_percSurgedPlot
```


```{r}
plot_grid(
  ephysLH + 
    scale_x_continuous(
      breaks = c(5, 5.5)
      , labels = c(-2.5, -2)
    )
  , ephys_percSurgedPlot
  , nrow = 1
  , rel_widths = c(1.5, 1)
)

fileBaseName <- "ephysLHPlots"

exportFullPPTSlide(
  height = 5.75
)

slideTitle <- "With limited sampling for ephys mice, did not detect surge in many LBN mice"
ppt <- pptAddOneGraph()
```
```{r}
plot_grid(
  samplingLH
  , sampling_percSurgedPlot
  , nrow = 1
  , rel_widths = c(1.5, 1)
)

fileBaseName <- "samplingLHPlots"

exportFullPPTSlide(
  height = 5.75
)

slideTitle <- "With full sampling window, 3/5 LBN-ALPS mice still surged"
ppt <- pptAddOneGraph()
```


# GABA PSC Freq

```{r}
figGABAe_model

fileBaseName <- "GABAfreq"

exportFullPPTSlide()
slideTitle <- "Neither LBN nor ALPS altered the frequency of GABA PSCs"
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
   coef(summary(numEvents_nb.GLMM)) %>%
    as.data.frame() %>%
    rownames_to_column("effect"),
  dontFormat = FALSE
)
```

# GABA PSC Amp

```{r}
figGABAf_model

fileBaseName <- "GABAamp"

exportFullPPTSlide()
slideTitle <- "Neither LBN nor ALPS altered the amplitude of GABA PSCs"
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  slideTitle,
  relAmplitude_lmm %>% formatMixedLMM_ppt(),
  dontFormat = FALSE
)
```

```{r}
GABAlegend <- get_legend(figGABAb_model + theme(legend.position = "top"))

plot_grid(
  GABAlegend
  , plot_grid(
    figGABAa_model +
      theme(
        axis.text.x = element_blank()
      )
    , figGABAb_model+
      theme(
        axis.text.x = element_blank()
      )
    , figGABAc_model+
      theme(
        axis.text.x = element_blank()
      )
    , figGABAd_model+
      theme(
        axis.text.x = element_blank()
      )
    , align = "h"
    , axis = "tb"
    , nrow = 1
  )
  , nrow = 2
  , rel_heights = c(0.1, 1)
)

fileBaseName <- "GABApassives"

exportFullPPTSlide()
slideTitle <- "Neither LBN nor ALPS altered passive properties or recording quality"
ppt <- pptAddOneGraph()
```

```{r}
maleCortAdmin_plotByConsumption

fileBaseName <- "maleCortPlotByConsumption"

slideTitle <- "Serum corticosterone is elevated by corticosterone consumption"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```
```{r}
latterCortAdmin_plotByConsumption

fileBaseName <- "maleCortPlotByConsumption"

slideTitle <- "Serum corticosterone is elevated by corticosterone consumption"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```
```{r}
maleCortAdmin_AMBodyMass

fileBaseName <- "maleCortAdmin_AMBodyMass"

slideTitle <- "AM Body mass"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
maleCortAdmin_PercChangeBodyMass

fileBaseName <- "maleCortAdmin_PercChangeBodyMass"

slideTitle <- "% Change in Body Mass"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
maleCortAdmin_TesticularMass

fileBaseName <- "maleCortAdmin_TesticularMass"

slideTitle <- "Testicular mass"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
maleCortAdmin_SeminalVesicleMass

fileBaseName <- "maleCortAdmin_SeminalVesicleMass"

slideTitle <- "Seminal vesicle mass"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
maleCortAdmin_AdrenalMass

fileBaseName <- "maleCortAdmin_AdrenalMass"

slideTitle <- "Adrenal mass"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}

```

