---
title: "ALPS"
output:
  html_document:
    df_print: kable
    toc: yes
  word_document:
    toc: yes
  html_notebook:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
```

```{r}
proUterineCutoff <- 135
```

# Uterine Mass and Evening LH - all P4-P11 controls
At the moment, this is just the pilot "detecting proestrus" mice. These were first litter offspring of dams with no treatment used to try to correlate vaginal smear, uterine mass, and LH surge. The samples were taken around 4:30-5:00p

The red line is `r proUterineCutoff` mg

The blue line is 140 mg

```{r named-1}
AcuteStress_off %>%
  filter(
    sex == "F",
    Cohort != 1,
    adultTrt == "CON",
    Dam_Strain == "CBA"
  ) %>%
  plotByUterineMass(yVar = maxLH, yLab = "max evening LH (ng/mL)") +
  geom_vline(xintercept = proUterineCutoff, color = "blue") +
  geom_vline(xintercept = 140, color = "red")
```
```{r}
AcuteStress_off %>%
  filter(
    sex == "F",
    Cohort != 1,
    adultTrt == "CON",
    Dam_Strain == "CBA",
    !is.na(maxLH)
  )%>%
  select(
    mouseID,
    ReproTract_mass,
    maxLH
  )
```


```{r eval=FALSE, include=FALSE}
# Cohort 5 Females - Detecting Proestrus
# These were first litter offspring of dams with no treatment used to try to correlate vaginal smear, uterine mass, and LH surge 
females_LH_0005 <- AcuteStress_off %>%
  filter(
    Cohort == 5,
    sex == "F"
  )

females_LH_0005 %>%
  plotByUterineMass(yVar = maxLH, "max evening LH (ng/mL)")
```

# Cohort 1 Females
These were sampled regardless of stage. 
P2-P9
B6 and CBA dams

## LH profile
```{r}
LH_off %>%
  filter(
    Cohort == 1
  ) %>%
  LHPlot() +
  facet_wrap(
    ~ adultTrt
  )
```


```{r}
femalesAcuteStress_0001 <- AcuteStress_off %>%
  filter(
    Cohort == 1,
    Dam_Strain == "CBA",
    sex == "F"
  )
```

### Uterine mass and LH
Uterine masses of the control CBA mice by max afternoon LH. Despite some high uterine masses, there were no detected surges that had started by 4p in these mice

```{r}
femalesAcuteStress_0001 %>%
  filter(
    adultTrt == "CON"
  ) %>%
  plotByUterineMass(yVar = maxLH, yLab = "max evening LH (ng/mL)")
```

```{r eval=FALSE, include=FALSE}
## Corticosterone and uterine mass
femalesAcuteStress_0001 %>%
  plotByUterineMass(yVar = cort_hr5, yLab = "corticosterone (ng/mL)")
```

```{r}
femalesCort_0001 <- Cort_off %>%
  filter(
    Cohort == 1,
    Dam_Strain == "CBA",
    sex == "F"
  )
```

## Corticosterone Response
This includes only the offspring of CBA dams

```{r}
femalesCort_0001_base <- baseCortPlot(femalesCort_0001)

femalesCort_0001_long <- longCortPlot(femalesCort_0001_base)
femalesCort_0001_long

femalesCort_0001_plot <- cortPlot(femalesCort_0001)
femalesCort_0001_plot
```

```{r}
femalesCort_0001 %>%
  cortAnova()
```

# Cohort 1 Males
```{r}
malesCort_0001 <- Cort_off %>%
  filter(
    Cohort == 1,
    Dam_Strain == "CBA",
    sex == "M"
  )
```

## Corticosterone Response
This includes only the offspring of CBA dams

```{r}
malesCort_0001_base <- baseCortPlot(malesCort_0001)

malesCort_0001_long <- longCortPlot(malesCort_0001_base)
malesCort_0001_long

malesCort_0001_plot <- cortPlot(malesCort_0001)
malesCort_0001_plot

malesCort_0001 %>%
  cortAnova()
```

# Females Cohort 2
```{r}
femalesCort_0002 <- Cort_off %>%
  filter(
    sex == "F",
    Cohort == 2
  )

femalesCort_0002_base <- baseCortPlot(femalesCort_0002)

femalesCort_0002_long <- longCortPlot(femalesCort_0002_base)
femalesCort_0002_long

femalesCort_0002_plot <- cortPlot(femalesCort_0002)
femalesCort_0002_plot

femalesAcuteStress_0002 <- AcuteStress_off %>%
  filter(
    sex == "F",
    Cohort == 2
  )

femalesCort_0002 %>%
  cortAnova()

AcuteStress_off %>%
  filter(
    sex == "F",
    Cohort == 2
  ) %>%
  getStressTrtNumbers()
```

## Uterine Mass By Group
```{r}
femalesAcuteStress_0002 %>%
  plotUterineMassByGroup(hLineVal = proUterineCutoff)
```

# Males Cohort 2
```{r}
malesCort_0002 <- Cort_off %>%
  filter(
    sex == "M",
    Cohort == 2
  )

malesCort_0002_base <- baseCortPlot(malesCort_0002)

malesCort_0002_long <- longCortPlot(malesCort_0002_base)
malesCort_0002_long

malesCort_0002_plot <- cortPlot(malesCort_0002)
malesCort_0002_plot
```

```{r males-cohort2-anova}
malesCort_0002 %>%
  cortAnova()
```

# Males - Second Litter Offspring
```{r}
malesAcuteStress_2ndLitter <- AcuteStress_off %>%
  filter(
    sex == "M",
    Litter_num == 2
  ) 
```

```{r}
malesAcuteStress_2ndLitter%>%
  group_by(
    earlyLifeTrt, adultTrt
  )%>%
  meanSummary(c(cort_hr0, cort_hr5))
```

```{r}
malesCort_2ndLitter <- Cort_off %>%
  filter(
    sex == "M",
    Litter_num == 2
  )
```


## Numbers

### Completed

```{r}
malesAcuteStress_2ndLitter %>%
  getStressTrtNumbers()
```

### Available
```{r}
LBN_data %>%
  filter(
    Cohort == 6,
    sex == "M",
    is.na(Sac_date)
  ) %>%
  group_by(
    earlyLifeTrt
  ) %>%
  summarise(
    n = n(),
    .groups = "drop"
  )
```


```{r}

malesCort_2ndLitter_base <- baseCortPlot(malesCort_2ndLitter)

malesCort_2ndLitter_long <- longCortPlot(malesCort_2ndLitter_base)
malesCort_2ndLitter_long

malesCort_2ndLitter_plot <- cortPlot(malesCort_2ndLitter, pointSize = 1.5)
malesCort_2ndLitter_plot
```

```{r}
malesCort_2ndLitter %>%
  cortAnova()
```

## Masses

### Seminal Vesicle Mass

```{r}
malesAcuteStress_2ndLitter %>%
  scatterPlotComboTrt(
    yVar = ReproTract_mass,
    yLab = "seminal vesicle mass (mg)"
  )
```

```{r}
malesAcuteStress_2ndLitter %>%
  filter(
    !is.na(ReproTract_mass)
  )%>%
  anova_test(
    dv = ReproTract_mass,
    between = c(earlyLifeTrt, adultTrt),
    type = 3
  ) %>%
  formatAnova()
```
#### By body mass

```{r}
malesAcuteStress_2ndLitter %>%
  scatterPlotComboTrt(
    yVar = ReproTract_mass_perBody_g,
    yLab = "seminal vesicle mass / body mass (mg/g)"
  )
```

```{r}
malesAcuteStress_2ndLitter %>%
  filter(
    !is.na(ReproTract_mass_perBody_g)
  )%>%
  anova_test(
    dv = ReproTract_mass_perBody_g,
    between = c(earlyLifeTrt, adultTrt),
    type = 3
  ) %>%
  formatAnova()
```

### Testicular Mass
```{r}
malesAcuteStress_2ndLitter %>%
  scatterPlotComboTrt(
    yVar = Gonad_mass,
    yLab = "testicular mass (mg)"
  )
```

```{r}
malesAcuteStress_2ndLitter %>%
  filter(
    !is.na(Gonad_mass)
  )%>%
  anova_test(
    dv = Gonad_mass,
    between = c(earlyLifeTrt, adultTrt),
    type = 3
  ) %>%
  formatAnova()
```
#### Per body mass
```{r}
malesAcuteStress_2ndLitter %>%
  scatterPlotComboTrt(
    yVar = Gonad_mass_perBody_g,
    yLab = "testicular mass / body mass (mg/g)"
  )
```

```{r}
malesAcuteStress_2ndLitter %>%
  filter(
    !is.na(Gonad_mass_perBody_g)
  )%>%
  anova_test(
    dv = Gonad_mass_perBody_g,
    between = c(earlyLifeTrt, adultTrt),
    type = 3
  ) %>%
  formatAnova()
```

### Adrenal Mass
```{r}
malesAcuteStress_2ndLitter %>%
  scatterPlotComboTrt(
    yVar = Adrenal_mass,
    yLab = "adrenal mass (mg)"
  )
```

```{r}
malesAcuteStress_2ndLitter %>%
  filter(
    !is.na(Adrenal_mass),
    # Adrenal_mass < 7
  )%>%
  anova_test(
    dv = Adrenal_mass,
    between = c(earlyLifeTrt, adultTrt),
    type = 3
  ) %>%
  formatAnova()
```
#### Per Body Mass
```{r}
malesAcuteStress_2ndLitter %>%
  filter(
    # Adrenal_mass < 7
  )%>%
  scatterPlotComboTrt(
    yVar = Adrenal_mass_perBody_g,
    yLab = "adrenal mass / body mass (mg/g)"
  )
```

```{r}
malesAcuteStress_2ndLitter %>%
  filter(
    !is.na(Adrenal_mass_perBody_g),
    # Adrenal_mass < 7
  )%>%
  anova_test(
    dv = Adrenal_mass_perBody_g,
    between = c(earlyLifeTrt, adultTrt),
    type = 3
  ) %>%
  formatAnova()
```
### Body Mass
```{r}
malesAcuteStress_2ndLitter %>%
  scatterPlotComboTrt(
    yVar = Body_mass_sac,
    yLab = "body mass (g)"
  )
```

```{r}
malesAcuteStress_2ndLitter %>%
  filter(
    !is.na(Body_mass_sac)
  )%>%
  anova_test(
    dv = Body_mass_sac,
    between = c(earlyLifeTrt, adultTrt),
    type = 3
  ) %>%
  formatAnova()
```

```{r eval=FALSE, include=FALSE}
ggsave(
  file.path(plotOutputFolder, "malesCort_LBN_0004.pdf"),
  malesCort_2ndLitter_plot + 
    guides(
      fill=guide_legend(nrow=2,byrow=TRUE),
      shape=guide_legend(nrow=2,byrow=TRUE),
      color=guide_legend(nrow = 2, byrow = TRUE),
      linetype=guide_legend(nrow = 2, byrow = TRUE)
    ) +
    theme(
      legend.title = element_blank(),
      legend.margin = margin(),
      legend.text = element_text(family = "Arial", size = 12)
    ),
  device = "pdf",
  width = 4,
  height = 2,
  units = "in",
  useDingbats = FALSE 
)
```

# Females - Second Litter
```{r}
femalesAcuteStress_2ndLitter <- AcuteStress_off %>%
  filter(
    sex == "F",
    Litter_num == 2
  )
femalesAcuteStress_2ndLitter %>%
  arrange(
    DOB,
    mouseID
  )
femalesAcuteStress_2ndLitter %>%
  filter(
    is.na(cort_hr0)
  )

femalesAcuteStress_2ndLitter %>%
  arrange(
    comboTrt,
    ReproTract_mass
  )
```

Group numbers, regardless of uterine mass
```{r}
femalesGroupNums_2ndLitter <- getStressTrtNumbers(femalesAcuteStress_2ndLitter)
femalesGroupNums_2ndLitter
```

Numbers over pro uterine mass cutoff of `r proUterineCutoff` mg

```{r}
femalesAcuteStress_2ndLitter %>%
  filter(
    #ReproTract_mass > proUterineCutoff
    Sac_cycle == "proestrus"
  ) %>%
  getStressTrtNumbers()
femalesAcuteStress_2ndLitter %>%
  filter(
    ReproTract_mass > proUterineCutoff
    #Sac_cycle == "proestrus"
  ) %>%
  getStressTrtNumbers()

# LH_code %>%
#   filter(
#     Litter_num == 2,
#     Sac_cycle == "proestrus",
#     comboTrt == "STD-ALPS"
#   ) %>%
#   arrange(
#     mouseID
#   )
```

```{r}
femalesAcuteStress_2ndLitter %>%
  filter(
    Sac_cycle != "proestrus" | is.na(Sac_cycle)
  )%>%
  getStressTrtNumbers()

femalesAcuteStress_2ndLitter %>%
  filter(
    ReproTract_mass<100,#proUterineCutoff,
    Sac_cycle == "diestrus"
  ) %>%
  getStressTrtNumbers()

```

Remaining second litter females
```{r}
LBN_data %>%
  filter(
    sex == "F",
    Litter_num == 2,
    is.na(Sac_date),
    is.na(Sac_stop_off)
  ) %>%
  group_by(
    earlyLifeTrt,
    Cohort
  ) %>%
  summarise(
    n = n(),
    .groups = "drop"
  )
```


## uterine masses

The red line is `r proUterineCutoff` mg

The blue line is 140 mg

```{r}
femalesAcuteStress_2ndLitter %>%
  plotUterineMassByGroup(hLineVal = proUterineCutoff)+
  geom_hline(yintercept = 140, color = "blue")
```

## Cort
This is only for the animals that were greater than the proestrus uterine cutoff value

```{r}
femalesCort_2ndLitter <- Cort_off %>%
  filter(
    sex == "F",
    Litter_num == 2,
    ReproTract_mass > proUterineCutoff
  )
femalesCort_2ndLitter_base <- baseCortPlot(femalesCort_2ndLitter)

femalesCort_2ndLitter_long <- longCortPlot(femalesCort_2ndLitter_base)
femalesCort_2ndLitter_long

femalesCort_2ndLitter_plot <- cortPlot(femalesCort_2ndLitter, pointSize = 1.5)
femalesCort_2ndLitter_plot
```

### Evening cort by uterine mass
```{r}
femalesAcuteStress_2ndLitter %>%
  plotByUterineMass(yVar = cort_hr5, yLab = "corticosterone (ng/mL)")
```

```{r}
femalesAcuteStress_2ndLitter %>%
  filter(
    SinglyHoused == TRUE
  )
```



# All CBA Females
This includes the P2-P9 CBA female first litter offspring (Cohort 1) and P4-11 first litter offspring (Cohort 2)

```{r}
Cort_off %>%
  filter(
    sex == "F",
    Dam_Strain == "CBA"
  ) %>%
  cortPlot()

Cort_off %>%
  filter(
    sex == "F",
    Dam_Strain == "CBA"
  ) %>%
  cortAnova()
```

# All CBA males
This includes the P2-P9 CBA male first litter offspring (Cohort 1), P4-P11 first litter offspring (Cohort 2), and P4-P11 second litter offspring (Cohort 4)

```{r}
Cort_off %>%
  filter(
    sex == "M",
    Dam_Strain == "CBA"
  ) %>%
  cortPlot()

Cort_off %>%
  filter(
    sex == "M",
    Dam_Strain == "CBA"
  ) %>%
  cortAnova() 
```

```{r}

```

