---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```
# Set up
Set-up the notebook. This script loads the environment, and contains the names for the data file, and sources the additional scripts that will be used for the analysis.
```{r GetReady}
source("./Scripts/LBN_0002_AGG_setUp.R")
dateToday = Sys.Date()
filterDateForTaskDFs = as.Date("2020-12-01") #Look for breed dates/DOBs after this date
```

# Load Data
The "load_LBN_data" function takes the data folder and excel file name and outputs a list with the processed dataframes. These have the demographic data and any "mutations" (calculated columns) added already.
The output of this chunk is each of these dataframes.
```{r LoadData, include=FALSE}
DFs <- load_LBN_data(
  dataFolder = DataFolder,
  excelName = LBN_DataName
)

Demo_dam <- DFs$Demo_dam
Demo_off <- DFs$Demo_off
Mass_off <- DFs$Mass_off
Maturation_off <- DFs$Maturation_off
EndPara_off <- DFs$EndPara_off
Cycles_off <- DFs$Cycles_off
AcuteStress_off <- DFs$AcuteStress_off
ChronicStress_off <- DFs$ChronicStress_off
LBN_all <- DFs$LBN_all
LBN_data <- DFs$LBN_data
CRH_dam <- DFs$CRH_dam
```

```{r}
library(imager)
library(gridExtra)
# install.packages("imager")
```

```{r}
baseFolder = "/Volumes/Shared3/Physiology-Moenter_Lab/gibsonag/LBN/LBN_0004/Cycles"
ncol = 4
maxRows = 3
```


```{r}
mouse = "01-D029-02_60"
plots <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
# str(plots)
# plots
# ggexport(plots, filename = "test.pdf")
# ?ggexport
```
```{r}
mouse = "02-D029-02_44"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "03-D029-02_46"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "04-D031-02_04"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "05-D031-02_06"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "06-D031-02_40"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "07-D033-02_04"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "08-D033-02_06"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "09-D033-02_40"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "10-D033-02_60"
arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "11-D033-02_44"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "12-D033-02_46"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "13-D030-02_04"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "14-D030-02_06"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "15-D030-02_40"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "16-D030-02_46"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "17-D030-02_66"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "18-D030-02_44"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "19-D032-02_06"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "20-D032-02_60"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "21-D036-02_04"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "22-D036-02_60"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```
```{r}
mouse = "23-D036-02_44"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "24-D036-02_66"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "25-D036-02_46"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "26-D035-02_60"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "27-D035-02_44"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "28-D035-02_66"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "29-D038-02_04"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "30-D038-02_06"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```

```{r}
mouse = "31-D038-02_40"
plot <- arrangeCycleImgs(
  mouse, 
  file.path(baseFolder, mouse), 
  file.path(OutputFolder, "reports", "cycles"), 
  ncol = ncol, maxRows = maxRows
)
```
