---
title: "R Notebook"
output: html_notebook
# fig-width: 11.5
# fig-height: 5
df-print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# knitr::opts_chunk$set(fig.width=11.5, fig.height=5) 
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
source("./01-scripts/04-filter-datasets.R")
source("./01-scripts/06-run-lqmm.R")
source("./01-scripts/06-run-LBN-stats.R")
source("./01-scripts/05-make-LBN-plots-modelError-manuscript.R")
source("./01-scripts/06-make-LBN-tables.R")
```

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
set_flextable_defaults(
  font.family = "Arial"
  , font.size = 11
)

doc <- read_docx("./manuscriptTemplate.docx")
supDoc <- read_docx("./manuscriptTemplate.docx")

saveTables <- function(){
  print(doc, target = "my_report.docx")
  print(supDoc, targe = "supplementalTable.docx")
}
```

# Column Sizes
```{r}
# # JNeuro values (in cm)
# twoCols <- 17.4
# oneAndHalfCols <- 11.5
# oneCol <- 8.5

# eNeuro values (in cm)
twoCols <- 17.6
oneAndHalfCols <- 11.6
oneCol <- 8.5

quarterLength <- 16.7/4
thirdLength <- 16.7/3
halfLength <- 16.7/2
twoThirdsLength <- 16.7*2/3
threeQuarterLength <- 16.7*3/4
fullLength <- 16.7

manuscriptFolder <- file.path(plotOutputFolder, "manuscript")
```

# Figure 1 - Dams figDams

```{r}
# trying to fix font errors
# this seems to work for not putting the axis label on top of the tick labels
# but the axes don't actually align with align_plots
# update - Maybe works???? IDK WHAT I DID!
set_null_device("png") 

# # this works for aligning the axes with align_plots
# # but then faceted plot yaxis label overlaps
# set_null_device("pdf")
# 
# # this works for aligning the axes with align_plots
# # but then faceted plot yaxis label overlaps
# set_null_device("cairo_pdf")
```


```{r}
figDamsPlots <- cowplot::align_plots(
  figDams_exits
  , figDams_offNest
  , align = "v"
  , axis = "l"
)

figDamsBehaviorPlots <- cowplot::align_plots(figDamsPlots[[1]], figDams_meanExits, figDamsPlots[[2]], figDams_meanOffNest, align = "h", axis = "bt")

figDamsRightPlots <- cowplot::align_plots(
  figDamsBehaviorPlots[[2]]
  , figDamsBehaviorPlots[[4]]
  , figDamsD
  , align = "v"
  , axis = "lr"
)

figDams_row1 <- align_plots(
  figDamsRightPlots[[3]]
  , figDams_mass
  , align = "h"
  , axis = "tb"
)

figDams_left <- plot_grid(
  plot_grid(
    NULL
    , figDams_row1[[2]]
    , nrow = 1
    , align = "h"
    , axis = "bt"
    , labels = c("A", "B")
    , label_fontfamily = "Arial"
    , label_size = textSize
  )
  , figDamsBehaviorPlots[[1]]
  , figDamsBehaviorPlots[[3]]
  , nrow = 3
  , labels = c("", "D", "F")
  , label_fontfamily = "Arial"
  , label_size = textSize
)

figDams_right <- plot_grid(
  figDams_row1[[1]]
  , figDamsRightPlots[[1]]
  , figDamsRightPlots[[2]]
  , labels = c("C", "E", "G")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , nrow = 3
)

figDams <- plot_grid(
  figDams_left
  , figDams_right
  , ncol = 2
  , rel_widths = c(3, 1)
)
  
figDams
```


```{r}
flexSave(
  "figDams"
  , plot = figDams
  , width = twoCols
  , height = fullLength - 0.1
  , units = "cm"
  , filePath = manuscriptFolder
)
```


## Table - counts of dams

```{r}
damCountTblNum <- 1
tableNum <- damCountTblNum
```


```{r}
tableCaption <- "Number of dams in each treatment group for studies reported in Figure 1. Dam behavior includes values for number of nest exits per hour and percent of time spent off the nest."

tbl <- dam_count_flexTable
tbl
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

## Table - dam mass

```{r}
testFormula <- getLMMFormula(damMass_lmm)
testFormula <- gsub("PND", "PND@", testFormula)
tableCaption <- paste0("Linear mixed model of the dam mass on PND4, 11, and 21 fit with the equation ", testFormula, ". PND was treated as a factor variable. PND = postnatal day")

tbl <- damMass_flexTable

tbl
```

```{r}
# damMassTblNum <- damCountTblNum + 1 #2
damMassTblNum <- 1 # first non supplemental
tableNum <- damMassTblNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### emmeans

```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed model of dam mass for early-life treatment and PND factors. CI = confidence interval; PND = postnatal day"

tbl <- damMass_lmm_emm_flexTable

tbl
```

```{r}
# damMassEmmTblNum <- damMassTblNum + 1
damMassEmmTblNum <- damCountTblNum + 1
tableNum <- damMassEmmTblNum
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

### pairs

```{r}
# damMassEmmPairsTblNum <- damMassEmmTblNum + 1
damMassEmmPairsTblNum <- damMassTblNum + 1
tableNum <- damMassEmmPairsTblNum
```

```{r}
tableCaption <- "Pairwise comparisons of contrasts from estimated marginal means of linear mixed model for dam mass. PND = postnatal day."

tbl <- damMass_emmPairs_flexTable
tbl
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Table - dam cort

```{r}
damCortTblNum <- damMassEmmPairsTblNum + 1
tableNum <- damCortTblNum
```

```{r}
tableCaption <- "Two-sided t-test of the effect of limited bedding and nesting (LBN) on serum corticosterone in dams on postnatal day 11. CI = confidence interval"

tbl <- damCort_flexTable
tbl
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Table - Dam behavior

```{r}
damBehaviorTblNum <- damCortTblNum + 1
tableNum <- damBehaviorTblNum
```

```{r}
tableCaption <- paste0("Dam behavior parameters analyzed with nonparametric longitudinal model using the nparLD package in R, with the ", numExits_nparLD$model.name, ". The subject variable was each dam, early-life treatment (standard or limited bedding and nesting cage) was the between-subject factor ('whole-plot' factor), and PND was the within-subject factor ('sub-plot' repeated factor). PND=postnatal day")

tbl <- damBehavior_flexTable
tbl
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


```{r eval=FALSE, include=FALSE}
numExits_nparLD$ANOVA.test

percOffNest_nparLD$ANOVA.test

damMass_lmm

damMass_lmm_EMM.earlyLifeTrt.pairs

damMass_lmm_EMM.PND.pairs

damCort_t.Test
```


# Figure 2 - Offspring maturation figOff

## grouped maturation
```{r}
figOffLeftPlots <- cowplot::align_plots(
  figOffA
  , figOffAge_model
  , figOffMass_model
  , align = "v", axis = "l"
)

figOffRightPlots <- cowplot::align_plots(
  figOff_femaleAGD
  , figOff_maleAGD
  , align = "vh", axis = "ltrb"
)

figOffMat <- plot_grid(
  plot_grid(
      figOffLeftPlots[[2]]
      , figOffRightPlots[[1]]
      , ncol = 2
      , rel_widths = c(3, 1)
      , labels = c("B", "D")
      , label_fontfamily = "Arial"
      , label_size = textSize
  )
  , plot_grid(
      figOffLeftPlots[[3]]
      , figOffRightPlots[[2]]
      , ncol = 2
      , rel_widths = c(3, 1)
      , labels = c("C", "")
      , label_fontfamily = "Arial"
      , label_size = textSize
  )
  , nrow = 2
)

figOff <- plot_grid(
  figOffLeftPlots[[1]]
  , figOffMat
  , nrow = 2
  , labels = c("A", NULL)
  , label_fontfamily = "Arial"
  , label_size = textSize
  , rel_heights = c(1.5, 2)
)
figOff
```

```{r}
flexSave(
  "figOff"
  , plot = figOff
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Table - offspring counts

```{r}
tbl <- massCount_flexTable
tbl
```

```{r}
# offMassCountTblNum <- damBehaviorTblNum + 1
# offMassCountTblNum <- damMassEmmTblNum + 1 # don't add
offMassCountTblNum <- damMassEmmTblNum  # not adding -> don't increment
tableNum <- offMassCountTblNum
tableCaption <- "Number of male and female offspring and litters with mass measurements at PND11, 21, 35, and 70. PND = postnatal day"
```


```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
# supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```


## Table - offspring mass

```{r}
tbl <- massLMM_flexTable
tbl
```


```{r}
# offMassTblNum <- offMassCountTblNum + 1
offMassTblNum <- damBehaviorTblNum + 1
tableNum <- offMassTblNum
```

```{r}
testFormula <- deparse(female_mass_lmm$call$formula)
testFormula <- gsub("lspline\\(day, c\\(21, 35\\)\\)", "PND@", testFormula)
testFormula <- paste(testFormula, collapse = " ")
testFormula <- gsub("\\s+", " ", testFormula)
tableCaption <- paste0("Linear mixed model of the offspring mass from PND11-72 fit with the equation ", testFormula, ". PND@: Linear splines at PND21 and 35 allow the model to change the slope of the line for the segments between PND11-21, from 21-35, and from 35-72. Male and female offspring were fit with separate models. PND = postnatal day")
```


```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### Table - male emmeans

```{r}
tbl <- maleMass_emm_flexTable
tbl
```

```{r}
# offMassTblNum_emm <- offMassTblNum + 1
offMassTblNum_emm <- offMassCountTblNum + 1 # not adding
tableNum <- offMassTblNum_emm
```

```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed model of male offspring mass for the interaction of early-life treatment and PND factors. CI = confidence interval. PND = postnatal day"
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

### Table - male emmeans comp

```{r}
tbl <- maleMass_emm.pairs_flexTable
tbl
```

```{r}
# offMassTblNum_emm_pairs <- offMassTblNum_emm + 1
offMassTblNum_emm_pairs <- offMassTblNum + 1
tableNum <- offMassTblNum_emm_pairs
```

```{r}
tableCaption <- "Pairwise comparisons of contrasts from estimated marginal means of linear mixed model for male offspring mass. PND = postnatal day."
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Table - count maturation
```{r}
tbl <- matCount_flexTable
tbl
```

```{r}
tableCaption <- "Number of offspring and litters with age and mass measurements for vaginal opening and first estrus in females and preputial separation in males"
```

```{r}
# offMatCountTblNum <- offMassTblNum_emm_pairs + 1
# offMatCountTblNum <- offMassTblNum_emm + 1
offMatCountTblNum <- offMassTblNum_emm
tableNum <- offMatCountTblNum
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
# supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```


## Table - VO, estrus, PPS

```{r}
tbl <- matMass_lmm_flexTable
tbl
```


```{r}
testFormula <- deparse(VO_age_lmm$call$formula)
testFormula <- gsub("VO_age", "maturation feature", testFormula)
tableCaption <- paste0("Linear mixed models for maturation with the equation ", testFormula, ". Models were fit for age and for mass at vaginal opening, first estrus, and preputial separation.")
```

```{r}
# offMatTblNum <- offMatCountTblNum + 1
offMatTblNum <- offMassTblNum_emm_pairs + 1
tableNum <- offMatTblNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Table - AGD

```{r}
tbl <- AGD_flexTable

tbl
```

```{r}
testFormula <- deparse(AGD_lmm$call$formula)
testFormula <- gsub("AGD_adult", "AGD", testFormula)
tableCaption <- paste0("Linear mixed models for anogenital distance (AGD) with the equation ", testFormula, ".")
```

```{r}
AGDTblNum <- offMatTblNum + 1
tableNum <- AGDTblNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### Table - AGD emms

```{r}
tbl <- AGD_lmm_emm_sex_flexTable
tbl
```

```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed model of anogenital distance for early-life treatment and sex. CI = confidence interval"
```

```{r}
# AGDTblNum_emm <- AGDTblNum + 1
AGDTblNum_emm <- offMatCountTblNum + 1
tableNum <- AGDTblNum_emm
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

### Table - AGD pairs

```{r}
tbl <- AGD_lmm_emm_sex.pairs_flexTable
tbl
```

```{r}
tableCaption <- "Pairwise comparisons of contrasts from estimated marginal means of linear mixed model for anogenital distance."
```

```{r}
# AGDTblNum_emm_pairs <- AGDTblNum_emm + 1
AGDTblNum_emm_pairs <- AGDTblNum + 1
tableNum <- AGDTblNum_emm_pairs
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 3 - Cycles

```{r}
figCyclesLeftPlots <- cowplot::align_plots(
  figCyclesA
  , figCycles_numCycles_model
  , align = "v", axis = "l"
)

figCycles2ndRow <- plot_grid(
  figCyclesLeftPlots[[2]]
  , figCycles_lengthLog_model
  , figCyclesD
  , ncol = 3
  , labels = c("B", "C", "D")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , align = "h"
  , axis = "bt"
  , rel_widths = c(1, 1, 2)
)

figCycles <- plot_grid(
  NULL
  , figCyclesLeftPlots[[1]]
  , figCycles2ndRow
  , nrow = 3
  , rel_heights = c(0.3, 2.2, 3)
  , labels = c("A", NULL, NULL)
  , label_fontfamily = "Arial"
  , label_size = textSize
)
figCycles
```

```{r}
flexSave(
  "figCycles"
  , plot = figCycles
  , width = twoCols
  , height = 9.5
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Cycles count

The reason that there are 74 STD females for masses and only 73 for cycles is that mouse 731 was the only female in the litter, and she was sacrificed at P72 after taking final mass sample. 

LBN drops from 74 to 73 because mouse 977 had hydrocephaly and was sacrificed PND24

```{r}
## No table, incorporate into text
cyclesFiltered %>%
  filter(
    !is.na(numCycles)
  ) %>%
  group_by(
    earlyLifeTrt
  ) %>%
  summarize(
    mice = n()
    , litters = n_distinct(damID)
    , .groups = "drop"
  )
```


## Table - Cycles length

```{r}
tbl <- cycles_flexTable
tbl
```

```{r}
cyclesNumFormula <- getLMMFormula(numCycles_lmm)
cyclesNumFormula <- gsub("numCycles", "# of cycles", cyclesNumFormula)

lengthCyclesFormula <- getLMMFormula(lengthCycles_log_lmm)
lengthCyclesFormula <- gsub("cycleLength", "cycle length", lengthCyclesFormula)

cycles_ChiSq_n <- cycles_ChiSq$n[1]

tableCaption <- paste0("Statistics for estrous cycles from postnatal days 70-90. The number of cycles was fit with the linear mixed model equation `", cyclesNumFormula, "`. The log of the mean cycle length in days was fit with equation `", lengthCyclesFormula, "`. The number of days spent in each cycle stage was assessed with a Chi-squared test (n = ", cycles_ChiSq_n, ").")
```


```{r}
cyclesTblNum <- AGDTblNum_emm_pairs + 1
tableNum <- cyclesTblNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 4 - Corticosterone

```{r}
figCort <- plot_grid(
  figCortA
  , figCortB
  , figCortC
  , nrow = 3
  , align = "vh", axis = "ltrb"
  , labels = c("A", "B", "C")
  , label_fontfamily = "Arial"
  , label_size = textSize
)

figCort

```

```{r}
flexSave(
  "figCort"
  , plot = figCort
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## count

```{r}
tbl <- cortCount_flexTable
tbl
```


```{r}
tableCaption <- "Number of litters and mice with serum corticosterone measurements before and after adult treatment. Abbreviations: STD, standard-reared; LBN, limited bedding and nesting; CON, adult control; ALPS, acute, layered, psychosocial stress in adulthood."
```

```{r}
# cortCountNum <- cyclesTblNum + 1
cortCountNum <- AGDTblNum_emm + 1
tableNum <- cortCountNum
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

## cort lmm 

```{r}
tbl <- cort_flexTable
tbl
```

```{r}
maleFormula <- getLMMFormula(male_cort_lmm)
maleFormula1 <- paste0(maleFormula[1], gsub("    \\(", "\\(", maleFormula[2]))

femaleFormula <- getLMMFormula(female_cort_lmm)
femaleFormula1 <- paste0(femaleFormula[1], gsub("    ", "", femaleFormula[2]))

maleFormula1
femaleFormula1

tableCaption <- paste0("Statistics for serum corticosterone in male and female offspring. Data from males were fit with the linear mixed model equation `", maleFormula1, "`. Data from females were fit with the linear mixed model equation `", femaleFormula1, "`.")
tableCaption
```

```{r}
# cortLMMNum <- cortCountNum + 1
cortLMMNum <- cyclesTblNum + 1
tableNum <- cortLMMNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### Male - Adult trt + time emm

```{r}
tbl <- maleCortLMM_emm_flexTable
tbl
```

```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed model in male mice of corticosterone for adult treatment (CON: control; ALPS: adult stress) and time (hr). Results are averaged over the levels of early-life treatment. The emmeans and confidence intervals (CI) are back-transformed from the log scale to the response scale (ng/mL)."
```

```{r}
# maleCortLMMNum_emm <- cortLMMNum + 1
maleCortLMMNum_emm <- cortCountNum + 1
tableNum <- maleCortLMMNum_emm
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

#### Male - Adult trt + time pairs

```{r}
tbl <- maleCortLMM_emm.pairs_flexTable
tbl
```

Holm p-value adjustment for 2 tests and Kenward-Roger for DF
```{r}
tableCaption <- "Pairwise comparison of estimated marginal means in male mice from linear mixed model of serum corticosterone for adult treatment (CON: control; ALPS: adult stress) and time (hr). Results are averaged over the levels of early-life treatment. Tests were performed on the log scale."
```

```{r}
# maleCortLMMNum_emm.pairs <- maleCortLMMNum_emm + 1
maleCortLMMNum_emm.pairs <- cortLMMNum + 1
tableNum <- maleCortLMMNum_emm.pairs
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### Female - Adult trt, time, cycle stage

```{r}
tbl <- femaleCortLMM_emm_3way_flexTable
tbl
```

```{r}
tableCaption <- "Estimated marginal means (emmean) in female mice from linear mixed model of serum corticosterone for adult treatment, time (hr), and estrous cycle stage. Results are averaged over the levels of early-life treatment. The emmeans and confidence intervals (CI) are back-transformed from the log scale to the response scale (ng/mL)."
```

```{r}
# femaleCortLMM_emm_num <- maleCortLMMNum_emm.pairs + 1
femaleCortLMM_emm_num <- maleCortLMMNum_emm + 1
tableNum <- femaleCortLMM_emm_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

#### Cycle stage + time pairs

```{r}
tbl <- femaleCortLMM_emm_3way.pairs_flexTable
tbl
```

```{r}
tableCaption <- "Pairwise comparison of estimated marginal means in female mice from linear mixed model of serum corticosterone for adult treatment, time (hr), and estrous cycle stage. Results are averaged over the levels of early-life treatment. Tests were performed on the log scale."
```

```{r}
# femaleCortLMM_emm_num.pairs <- femaleCortLMM_emm_num + 1
femaleCortLMM_emm_num.pairs <- maleCortLMMNum_emm.pairs + 1
tableNum <- femaleCortLMM_emm_num.pairs
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


# Figure 5 - Male masses - ALPS

```{r eval=FALSE, include=FALSE}
figMaleMassALPS_left <- align_plots(
  maleBodyMassAM_ALPS_plot+rremove("legend")
  , maleAdrenalMass_ALPS_plot
  , maleRelAdrenalMass_ALPS_plot
  , align = "v"
  , axis = "l"
)

figMaleMassALPS_middle <- align_plots(
  maleSeminalVesicleMass_ALPS_plot
  , maleRelSeminalVesicleMass_ALPS_plot
  , align = "v"
  , axis = "lr"
)
figMaleMassALPS_right <- align_plots(
  maleTestesMass_ALPS_plot
  , maleRelTestesMass_ALPS_plot
  , align = "v"
  , axis = "lr"
)

figMaleMassALPS <- plot_grid(
  get_legend(maleBodyMassAM_ALPS_plot)
  , plot_grid(
    figMaleMassALPS_left[[1]]
    , malePercChangeBodyMass_ALPS_plot
    , nrow = 1
  ),
  plot_grid(
    figMaleMassALPS_left[[2]]
    , figMaleMassALPS_middle[[1]]
    , figMaleMassALPS_right[[1]]
    , nrow = 1
  ),
  plot_grid(
    figMaleMassALPS_left[[3]]
    , figMaleMassALPS_middle[[2]]
    , figMaleMassALPS_right[[2]]
    , nrow = 1
  )
  , nrow = 4
  , rel_heights = c(0.1, 1, 1, 1)
)
figMaleMassALPS
```

3-by-3 layout
```{r eval=FALSE, include=FALSE}
figMaleMassALPS <- plot_grid(
  get_legend(maleBodyMassAM_ALPS_plot)
  , plot_grid(
    maleBodyMassAM_ALPS_plot + rremove("legend")
    , malePercChangeBodyMass_ALPS_plot
    , NULL
    , maleAdrenalMass_ALPS_plot
    , maleSeminalVesicleMass_ALPS_plot
    , maleTestesMass_ALPS_plot
    , maleRelAdrenalMass_ALPS_plot
    , maleRelSeminalVesicleMass_ALPS_plot
    , maleRelTestesMass_ALPS_plot
    , nrow = 3
    , ncol = 3
    , align = "hv"
    , axis = "tlbr"
    , labels = c("A", "B", "", "C", "E", "G", "D", "F", "H")
  )
  , nrow = 2
  ,rel_heights = c(0.1, 3)
)
figMaleMassALPS
```


4-by-2 layout, AM
```{r eval=FALSE, include=FALSE}
figMaleMassALPS <- plot_grid(
  get_legend(maleBodyMassAM_ALPS_plot)
  , plot_grid(
    maleBodyMassAM_ALPS_plot + rremove("legend")
    , malePercChangeBodyMass_ALPS_plot
    , maleAdrenalMass_ALPS_plot
    , maleRelAdrenalMass_ALPS_plot
    , maleSeminalVesicleMass_ALPS_plot
    , maleRelSeminalVesicleMass_ALPS_plot
    , maleTestesMass_ALPS_plot
    , maleRelTestesMass_ALPS_plot
    # , nrow = 3
    , ncol = 2
    , align = "hv"
    , axis = "tlbr"
    , labels = c("A", "B", "C", "D", "E", "F", "G", "H")
  )
  , nrow = 2
  ,rel_heights = c(0.1, 3)
)
figMaleMassALPS
```

4-by-2 layout, PM
```{r}
figMaleMassALPS <- plot_grid(
  plot_grid(
    maleBodyMassAM_ALPS_plot
    , maleAdrenalMass_ALPS_plot
    , maleSeminalVesicleMass_ALPS_plot
    , maleTestesMass_ALPS_plot
    , ncol = 1
    , align = "v"
    , axis = "lr"
    , labels = c("A", "C", "E", "G")
    , label_fontfamily = "Arial"
    , label_size = textSize
  ), 
  plot_grid(
    malePercChangeBodyMass_ALPS_plot
    , maleRelAdrenalMassPM_ALPS_plot
    , maleRelSeminalVesicleMassPM_ALPS_plot
    , maleRelTestesMassPM_ALPS_plot
    , ncol = 1
    , align = "v"
    , axis = "lr"
    , labels = c("B", "D", "F", "H")
    , label_fontfamily = "Arial"
    , label_size = textSize
  )
  , ncol = 2
  , rel_widths = c(1, 1)
)
figMaleMassALPS
```


```{r}
flexSave(
  "figMaleMassALPS"
  , plot = figMaleMassALPS
  , width = twoCols
  , height = 18
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Count

```{r}
tbl <- maleMass_ALPSAM_counts_flexTable
tbl
tbl <- maleMass_ALPSPM_counts_flexTable
tbl
```

```{r}
tableCaption <- "Number of litters and male mice with mass measurements on the day of adult treatment. Abbreviations: STD, standard-reared; LBN, limited bedding and nesting; CON, adult control; ALPS, acute, layered, psychosocial stress in adulthood."
```

```{r}
# maleMass_ALPS_countsNum <- femaleCortLMM_emm_num.pairs + 1
maleMass_ALPS_countsNum <- femaleCortLMM_emm_num + 1
tableNum <- maleMass_ALPS_countsNum
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```


## lmm

```{r}
tbl <- maleALPS_RelAM_flexTable
tbl
tbl <- maleALPS_RelPM_flexTable
tbl
```


```{r}
tableCaption <- "Statistics from linear mixed models of male masses on day of adult treatment. Data were fit with the formula `feature ~ early-life treatment * adult treatment + (1 | dam)`."
```

```{r}
# maleMass_ALPS_lmm_num <- maleMass_ALPS_countsNum + 1
maleMass_ALPS_lmm_num <- femaleCortLMM_emm_num.pairs + 1
tableNum <- maleMass_ALPS_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### EMM
```{r}
tbl <- maleALPS_RelAM_EMM_flexTable
tbl
tbl <- maleALPS_RelPM_EMM_flexTable
tbl
```


```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed models of male masses for the effects of early-life treatment (STD: standard rearing; LBN: limited bedding and nesting) and adult treatment (CON: control; ALPS: adult stress). CI = confidence interval."
```

```{r}
# maleMass_ALPS_lmm_emm_num <- maleMass_ALPS_lmm_num + 1
maleMass_ALPS_lmm_emm_num <- maleMass_ALPS_countsNum + 1
tableNum <- maleMass_ALPS_lmm_emm_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

### Pairs

```{r}
tbl <- maleALPS_RelAM_EMM.pairs_flexTable
tbl
tbl <- maleALPS_RelPM_EMM.pairs_flexTable
tbl
```

```{r}
tableCaption <- "Pairwise comparison of estimated marginal means from linear mixed models of male masses for the effects of early-life treatment (STD: standard rearing; LBN: limited bedding and nesting) and adult treatment (CON: control; ALPS: adult stress)."
```

```{r}
# maleMass_ALPS_lmm_emm.pairs_num <- maleMass_ALPS_lmm_emm_num + 1
maleMass_ALPS_lmm_emm.pairs_num <- maleMass_ALPS_lmm_num + 1
tableNum <- maleMass_ALPS_lmm_emm.pairs_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


# Figure 6 - Male cort administration

```{r eval=FALSE, include=FALSE}
figMaleCortAdmin_aligned <- align_plots(
  maleBodyMassAM_dosage_plot
  , maleAdrenalMass_dosage_plot
  , maleSeminalVesicleMass_dosage_plot
  , maleTestesMass_dosage_plot
  , malePercChangeBodyMass_dosage_plot
  , maleRelAdrenalMass_dosage_plot
  , maleRelSeminalVesicleMass_dosage_plot
  , maleRelTestesMass_dosage_plot
  , cortAdmin_cort
  , align = "v"
  , axis = "l"
)

figMaleMass_dosage <- plot_grid(
  figMaleCortAdmin_aligned[[1]]
  , figMaleCortAdmin_aligned[[2]]
  , figMaleCortAdmin_aligned[[3]]
  , figMaleCortAdmin_aligned[[4]]
  , figMaleCortAdmin_aligned[[5]]
  , figMaleCortAdmin_aligned[[6]]
  , figMaleCortAdmin_aligned[[7]]
  , figMaleCortAdmin_aligned[[8]]
  , nrow = 3
  , ncol = 3
  , align = "h"
  , axis = "tb"
  , labels = c("B", "D", "F", "H", "C", "E", "G", "I")
)

figMaleCortAdmin <- plot_grid(
  figMaleCortAdmin_aligned[[9]]
  , figMaleMass_dosage
  , nrow = 2
  , rel_heights = c(1.5, 3.3)
  , labels = c("A", "")
)
figMaleCortAdmin
```

```{r eval=FALSE, include=FALSE}
figMaleCortAdmin_left <- align_plots(
  cortAdmin_cort
  , maleAdrenalMass_dosage_plot
  , maleRelAdrenalMass_dosage_plot
  , align = "v"
  , axis = "l"
)
figMaleCortAdmin_middle <- align_plots(
  maleSeminalVesicleMass_dosage_plot
  , maleRelSeminalVesicleMass_dosage_plot
  , align = "v"
  , axis = "l"
)
figMaleCortAdmin_right <- align_plots(
  maleTestesMass_dosage_plot
  , maleRelTestesMass_dosage_plot
  , align = "v"
  , axis = "l"
)
figMaleCortAdmin_top <- align_plots(
  maleBodyMassAM_dosage_plot
  , malePercChangeBodyMass_dosage_plo
  , align = "vh"
  , axis = "tblr"
)

figMaleCortAdmin_row1 <- plot_grid(
  figMaleCortAdmin_left[[1]]
  , figMaleCortAdmin_top[[1]]
  , figMaleCortAdmin_top[[2]]
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("A", "B", "C")
  , rel_widths = c(2, 1, 1)
)
figMaleCortAdmin_row2 <- plot_grid(
  figMaleCortAdmin_left[[2]]
  , figMaleCortAdmin_middle[[1]]
  , figMaleCortAdmin_right[[1]]
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("D", "F", "H")
)
figMaleCortAdmin_row3 <- plot_grid(
  figMaleCortAdmin_left[[3]]
  , figMaleCortAdmin_middle[[2]]
  , figMaleCortAdmin_right[[2]]
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("E", "G", "I")
)

figMaleCortAdmin <- plot_grid(
  figMaleCortAdmin_row1
  , figMaleCortAdmin_row2
  , figMaleCortAdmin_row3
  , nrow = 3
  , rel_heights = c(0.9, 1, 1)
)

figMaleCortAdmin
```

```{r}
figMaleCortAdmin_left <- align_plots(
  maleAdrenalMass_dosage_plot
  , maleRelAdrenalMassPM_dosage_plot
  , align = "v"
  , axis = "l"
)
figMaleCortAdmin_middle <- align_plots(
  maleSeminalVesicleMass_dosage_plot
  , maleRelSeminalVesicleMassPM_dosage_plot
  , align = "v"
  , axis = "l"
)
figMaleCortAdmin_right <- align_plots(
  maleTestesMass_dosage_plot
  , maleRelTestesMassPM_dosage_plot
  , align = "v"
  , axis = "l"
)

figMaleCortAdmin_row1 <- plot_grid(
  maleBodyMassAM_dosage_plot
  , cortAdmin_cort
  , malePercChangeBodyMass_dosage_plot
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("A", "B", "C")
  , rel_widths = c(1, 2, 1)
  , label_fontfamily = "Arial"
  , label_size = textSize
)
figMaleCortAdmin_row2 <- plot_grid(
  figMaleCortAdmin_left[[1]]
  , figMaleCortAdmin_middle[[1]]
  , figMaleCortAdmin_right[[1]]
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("D", "F", "H")
  , label_fontfamily = "Arial"
  , label_size = textSize
)
figMaleCortAdmin_row3 <- plot_grid(
  figMaleCortAdmin_left[[2]]
  , figMaleCortAdmin_middle[[2]]
  , figMaleCortAdmin_right[[2]]
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("E", "G", "I")
  , label_fontfamily = "Arial"
  , label_size = textSize
)

figMaleCortAdmin <- plot_grid(
  figMaleCortAdmin_row1
  , figMaleCortAdmin_row2
  , figMaleCortAdmin_row3
  , nrow = 3
  , rel_heights = c(1, 1, 1)
)

figMaleCortAdmin
```


```{r}
flexSave(
  "figMaleCortAdmin"
  , plot = figMaleCortAdmin
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Cort count

```{r}
tbl <- malesCortAdmin_cortCount_flexTable
tbl
```

```{r}
tableCaption <- "Number of litters and mice with serum corticosterone measurements during male corticosterone administration studies in vehicle treated (0mg/kg) and corticsterone treated (2mg/kg) groups (Figure 6a)."
```

```{r}
# malesCortAdmin_cortCount_num <- maleMass_ALPS_lmm_emm.pairs_num + 1
# malesCortAdmin_cortCount_num <- maleMass_ALPS_lmm_emm_num + 1
malesCortAdmin_cortCount_num <- maleMass_ALPS_lmm_emm_num
tableNum <- malesCortAdmin_cortCount_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
# supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

## Cort LMM 

```{r}
tbl <- maleCortAdmin_cort_flexTable
tbl
```

```{r}
maleCortAdmin_cort_formula <-  getLMMFormula(maleCortAdmin_cort_lmm)

tableCaption <- paste0("Statistics for serum corticosterone in males with vehicle or corticosterone administration. Data were fit with the linear mixed model equation `", maleCortAdmin_cort_formula, "`.")
```
```{r}
# malesCortAdmin_cortLMM_num <- malesCortAdmin_cortCount_num + 1
malesCortAdmin_cortLMM_num <- maleMass_ALPS_lmm_emm.pairs_num + 1
tableNum <- malesCortAdmin_cortLMM_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### EMM

```{r}
tbl <- maleCortAdmin_cortLMM_emm_flexTable
tbl
```

```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed model of serum corticosterone for the interaction of dosage (vehicle: 0mg/kg; corticosterone: 2mg/kg) and time. The emmeans and confidence intervals (CI) are back-transformed from the log scale to the response scale (ng/mL)."
```

```{r}
# malesCortAdmin_cortLMM_EMM_num <- malesCortAdmin_cortLMM_num + 1
malesCortAdmin_cortLMM_EMM_num <- malesCortAdmin_cortCount_num + 1
tableNum <- malesCortAdmin_cortLMM_EMM_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

### pairs

```{r}
tbl <- maleCortAdmin_cortLMM_emm.pairs_flexTable
tbl
```

```{r}
tableCaption <- "Pairwise comparison of estimated marginal means from linear mixed model of serum corticosterone for the interaction of dosage (vehicle: 0mg/kg; corticosterone: 2mg/kg) and time."
```

```{r}
# malesCortAdmin_cortLMM_EMM.pairs_num <- malesCortAdmin_cortLMM_EMM_num + 1
malesCortAdmin_cortLMM_EMM.pairs_num <- malesCortAdmin_cortLMM_num + 1
tableNum <- malesCortAdmin_cortLMM_EMM.pairs_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Mass count 

```{r}
tbl <- maleMassCortAM_counts_flexTable 
tbl
tbl <- maleMassCortPM_counts_flexTable
tbl
```


```{r}
tableCaption <- "Number of litters and male mice with mass measurements on the day of vehicle (0mg/kg) or corticosterone (2mg/kg) treatment."
```

```{r}
# maleCortAdmin_massCount_num <- malesCortAdmin_cortLMM_EMM.pairs_num + 1
# maleCortAdmin_massCount_num <- malesCortAdmin_cortLMM_EMM_num + 1
maleCortAdmin_massCount_num <- malesCortAdmin_cortLMM_EMM_num
tableNum <- maleCortAdmin_massCount_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
# supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

## mass LMM

```{r}
tbl <- male_dosage_RelAM_flexTable
tbl

tbl <- male_dosage_RelPM_flexTable
tbl
```

```{r}
tableCaption <- "Statistics from linear mixed models of male masses on day of vehicle (0mg/kg) or corticosterone (2mg/kg) treatment. Data were fit with the formula `feature ~ dosage + (1 | dam)`."
```

```{r}
# maleCortAdmin_mass_lmm_num <- maleCortAdmin_massCount_num + 1
maleCortAdmin_mass_lmm_num <- malesCortAdmin_cortLMM_EMM.pairs_num + 1
tableNum <- maleCortAdmin_mass_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### EMM

```{r}
tbl <- male_dosage_RelAM_EMM_flexTable
tbl

tbl <- male_dosage_RelPM_EMM_flexTable
tbl
```

```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed models of male masses on day of vehicle (0mg/kg) or corticosterone (2mg/kg) treatment. CI = confidence interval."
```

```{r}
# maleCortAdmin_mass_lmm_emm_num <- maleCortAdmin_mass_lmm_num + 1
maleCortAdmin_mass_lmm_emm_num <- maleCortAdmin_massCount_num + 1
tableNum <- maleCortAdmin_mass_lmm_emm_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

### Pairs

```{r}
tbl <- male_dosage_RelAM_EMM.pairs_flexTable
tbl

tbl <- male_dosage_RelPM_EMM.pairs_flexTable
tbl
```

```{r}
tableCaption <- "Pairwise comparison of estimated marginal means from linear mixed models of male masses on day of vehicle (0mg/kg) or corticosterone (2mg/kg) treatment."
```

```{r}
# maleCortAdmin_mass_lmm_emm.pairs_num <- maleCortAdmin_mass_lmm_emm_num + 1
maleCortAdmin_mass_lmm_emm.pairs_num <- maleCortAdmin_mass_lmm_num + 1
tableNum <- maleCortAdmin_mass_lmm_emm.pairs_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


```{r eval=FALSE, include=FALSE}
maleBodyMassAM_dosage_lmm
malePercChangeBodyMass_dosage_lmm
maleAdrenalMass_dosage_lmm
maleRelAdrenalMass_dosage_lmm
maleRelAdrenalMassPM_dosage_lmm
maleSeminalVesicleMass_dosage_lmm
maleRelSeminalVesicleMass_dosage_lmm
maleRelSeminalVesicleMassPM_dosage_lmm
maleTestesMass_dosage_lmm
maleRelTestesMass_dosage_lmm
maleRelTestesMassPM_dosage_lmm
```

# Figure 7 - Female masses

```{r eval=FALSE, include=FALSE}
figFemalesMasses_plots <- align_plots(
    femaleBodyMassAM_ALPS_plot + rremove("legend") 
    , femalePercChangeBodyMass_ALPS_plot
    , femaleAdrenalMass_ALPS_plot
    , femaleUterineMass_ALPS_plot
    , femaleRelAdrenalMass_ALPS_plot
    , femaleRelUterineMass_ALPS_plot
    , align = "hv"
    , axis = "lrtb"
)

figFemalesMasses <- plot_grid(
  get_legend(femaleBodyMassAM_ALPS_plot)
  , plot_grid(
    figFemalesMasses_plots[[1]]
    , figFemalesMasses_plots[[2]]
    , ncol = 2
    , labels = c("A", "B")
  )
  , plot_grid(
    figFemalesMasses_plots[[3]]
    , figFemalesMasses_plots[[5]]
    , ncol = 2
    , labels = c("C", "D")
  )
  , plot_grid(
    figFemalesMasses_plots[[4]]
    , figFemalesMasses_plots[[6]]
    , ncol = 2
    , labels = c("E", "F")
  )
  , nrow = 4
  , rel_heights = c(0.1, 1, 1, 1)
)
figFemalesMasses
```
```{r}
figFemalesMasses_plots <- align_plots(
    femaleBodyMassAM_ALPS_plot + rremove("legend") 
    , femalePercChangeBodyMass_ALPS_plot
    , femaleAdrenalMass_ALPS_plot
    , femaleUterineMass_ALPS_plot
    , femaleRelAdrenalMassPM_ALPS_plot
    , femaleRelUterineMassPM_ALPS_plot
    , align = "hv"
    , axis = "lrtb"
)

figFemalesMasses_plots_left <- align_plots(
    femaleBodyMassAM_ALPS_plot + rremove("legend") 
    , femaleAdrenalMass_ALPS_plot
    , femaleUterineMass_ALPS_plot
    , align = "hv"
    , axis = "lrtb"
)

figFemalesMasses_plots_right <- align_plots(
    femalePercChangeBodyMass_ALPS_plot
    , femaleRelAdrenalMassPM_ALPS_plot
    , femaleRelUterineMassPM_ALPS_plot
    , align = "hv"
    , axis = "lrtb"
)

figFemalesMasses <- plot_grid(
  # get_legend(femaleBodyMassAM_ALPS_plot)
  plot_grid(
    figFemalesMasses_plots_left[[1]]
    , figFemalesMasses_plots_right[[1]]
    , ncol = 2
    , labels = c("A", "B")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , rel_widths = c(0.95, 1)
  )
  , plot_grid(
    figFemalesMasses_plots_left[[2]]
    , figFemalesMasses_plots_right[[2]]
    , ncol = 2
    , labels = c("C", "D")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , rel_widths = c(0.95, 1)
  )
  , plot_grid(
    figFemalesMasses_plots_left[[3]]
    , figFemalesMasses_plots_right[[3]]
    , ncol = 2
    , labels = c("E", "F")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , rel_widths = c(0.95, 1)
  )
  , nrow = 3
  , rel_heights = c(1, 1, 1)
  # , nrow = 4
  # , rel_heights = c(0.1, 1, 1, 1)
)
figFemalesMasses
```

```{r}
flexSave(
  "figFemalesMasses"
  , plot = figFemalesMasses
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Count

```{r}
tbl <- femaleMass_ALPSAM_counts_flexTable
tbl

tbl <- femaleMass_ALPSPM_counts_flexTable
tbl
```


```{r}
tableCaption <- "Number of litters and female mice with mass measurements on the day of adult treatment. Abbreviations: STD, standard-reared; LBN, limited bedding and nesting; CON, adult control; ALPS, acute, layered, psychosocial stress in adulthood."
```

```{r}
# femaleMass_ALPS_countsNum <- maleCortAdmin_mass_lmm_emm.pairs_num + 1
femaleMass_ALPS_countsNum <- maleCortAdmin_mass_lmm_emm_num + 1
tableNum <- femaleMass_ALPS_countsNum
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

## LMM

```{r}
tbl <- femaleALPS_RelAM_flexTable
tbl

tbl <- femaleALPS_RelPM_flexTable
tbl
```

```{r}
tableCaption <- "Statistics from linear mixed models of female masses on day of adult treatment. Data were fit with the formula `feature ~ early-life treatment * adult treatment * cycle stage + (1 | dam)`."
```

```{r}
# femaleMass_ALPS_lmm_num <- femaleMass_ALPS_countsNum + 1
femaleMass_ALPS_lmm_num <- maleCortAdmin_mass_lmm_emm.pairs_num + 1
tableNum <- femaleMass_ALPS_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

### EMM

```{r}
tbl <- femaleALPS_RelAM_EMM_flexTable
tbl

tbl <- femaleALPS_RelPM_EMM_flexTable
tbl
```

```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed models of female masses on day of adult treatment. CI = confidence interval; STD = standard rearing; LBN = limited bedding and nesting; ALPS = adult stress."
```


```{r}
# femaleMass_ALPS_lmm_emm_num <- femaleMass_ALPS_lmm_num + 1
femaleMass_ALPS_lmm_emm_num <- femaleMass_ALPS_countsNum + 1
tableNum <- femaleMass_ALPS_lmm_emm_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

### Pairs

```{r}
tbl <- femaleALPS_RelAM_EMM.pairs_flexTable
tbl 

tbl <- femaleALPS_RelPM_EMM.pairs_flexTable
tbl
```

```{r}
tableCaption <- "Pairwise comparison of estimated marginal means from linear mixed models of female masses on day of adult treatment. STD = standard rearing; LBN = limited bedding and nesting; ALPS = adult stress."
```

```{r}
# femaleMass_ALPS_lmm_emm.pairs_num <- femaleMass_ALPS_lmm_emm_num + 1
femaleMass_ALPS_lmm_emm.pairs_num <- femaleMass_ALPS_lmm_num + 1
tableNum <- femaleMass_ALPS_lmm_emm.pairs_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

```{r eval=FALSE, include=FALSE}
femaleBodyMassAM_ALPS_lmm 
femalePercChangeBodyMass_ALPS_lmm
femalePercChangeBodyMass_ALPS_lmm_emm_adultTrt.pairs
femaleAdrenalMass_ALPS_lmm
femaleAdrenalMass_ALPS_lmm_emm_earlyLifeTrt.pairs
femaleRelAdrenalMass_ALPS_lmm
femaleUterineMass_ALPS_lmm
femaleUterineMass_ALPS_lmm_emm_sacCycle.pairs
# weak trend for interaction
femaleUterineMass_ALPS_lmm_emm_sacCycleAdultTrt.pairs
femaleRelUterineMass_ALPS_lmm
femaleRelUterineMass_ALPS_lmm_emm_sacCycle.pairs
#weak trend for interaction
femaleRelUterineMass_ALPS_lmm_emm_sacCycleAdultTrt.pairs
```


# Figure 8 - LH

```{r eval=FALSE, include=FALSE}
# figLH_diAfternoon
# 
# figLH_ephysMax
# 
# figLH_ephysSurged
# 
# figLH_samplingTime
# 
# figLH_samplingMax
# 
# figLH_samplingSurged

row1 <- plot_grid(
  figLH_diAfternoon
  , figLH_ephysMax
  , figLH_ephysSurged
  , align = "hv"
  , axis = "tblr"
  , nrow = 1
  , labels = c("A", "B", "C")
)

row3 <- plot_grid(
  figLH_samplingMax
  , figLH_samplingSurged
  , NULL
  , nrow = 1
  , labels = c("E", "F", "")
)



figLH <- plot_grid(
  row1
  , figLH_samplingTime
  , row3
  , nrow = 3
  , rel_heights = c(1, 2, 1)
  , labels = c("", "D", "")
)

figLH

```

```{r eval=FALSE, include=FALSE}
plot_grid(
  plot_grid(
    figLH_diAfternoon
    , figLH_samplingTime
    , align = "hv"
    , axis = "tblr"
    , nrow = 1
    , labels = c("A", "D")
    , rel_widths = c(1, 2)
  )
  , plot_grid(
    figLH_ephysMax
    , figLH_samplingMax
    , align = "hv"
    , axis = "tblr"
    , nrow = 1
    , labels = c("B", "E")
  )
  , plot_grid(
    figLH_ephysSurged
    , figLH_samplingSurged
    , align = "hr"
    , axis = "tblr"
    , labels = c("C", "F")
  )
  , nrow = 3
)
```

```{r eval=FALSE, include=FALSE}

row1 <- plot_grid(
  figLH_diAfternoon
  , figLH_ephysMax
  , figLH_ephysSurged
  , align = "hv"
  , axis = "tblr"
  , nrow = 1
  , labels = c("A", "B", "C")
)

col3 <- plot_grid(
  figLH_samplingMax
  , figLH_samplingSurged
  , ncol = 1
  , labels = c("E", "F")
  , align = "hv"
  , axis = "tblr"
)



figLH <- plot_grid(
  row1
  , plot_grid(
    figLH_samplingTime
    , col3
    , ncol = 2
    , rel_widths = c(2, 1)
    , labels = c("D", "")
  )
  , nrow = 2
  , rel_heights = c(1, 2)
)

figLH

```

```{r eval=FALSE, include=FALSE}

LH_aligned <- align_plots(
  figLH_diAfternoon
  , figLH_ephysMax
  , figLH_ephysSurged
  , figLH_samplingTime
  , figLH_samplingMax
  , figLH_samplingSurged
  , align = "hv"
  , axis = "tblr"
)

row1 <- plot_grid(
  LH_aligned[[1]]
  , LH_aligned[[2]]
  , LH_aligned[[3]]
  , nrow = 1
  , labels = c("A", "B", "C")
)

col3 <- plot_grid(
  LH_aligned[[5]]
  , LH_aligned[[6]]
  , ncol = 1
  , labels = c("E", "F")
  , align = "hv"
  , axis = "tblr"
)



figLH <- plot_grid(
  row1
  , plot_grid(
    LH_aligned[[4]]
    , col3
    , ncol = 2
    , rel_widths = c(2, 1)
    , labels = c("D", "")
  )
  , nrow = 2
  , rel_heights = c(1, 2)
)

figLH

```

```{r}
figLH <- plot_grid(
  figLH_diAfternoon
  , figLH_ephysMax
  , figLH_ephysSurged
  , figLH_samplingTime_STDCON
  , figLH_samplingTime_STDALPS
  , figLH_samplingMax
  , figLH_samplingTime_LBNCON
  , figLH_samplingTime_LBNALPS
  , figLH_samplingSurged
  , nrow = 3
  , align = "hv"
  , axis = "tblr"
  , labels = c("A", "B", "C", "D", "", "E", "", "", "F")
  , label_fontfamily = "Arial"
  , label_size = textSize
)

figLH

```



```{r}
flexSave(
  "figLH"
  , plot = figLH
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Count

```{r}
tbl <- LHCount_flexTable
tbl
```

```{r}
tableCaption <- "Number of litters and mice with LH measurements following adult stress treatment for animals studied on diestrus or proestrus. Proestrous animals were either used for later electrophysiology (ephys) studies or for repeated hourly LH sampling around the time of lights out. (STD: standard rearing; LBN: limited bedding and nesting; CON: control; ALPS: adult stress)"
```


```{r}
# LHCount_num <- femaleMass_ALPS_lmm_emm.pairs_num + 1
# LHCount_num <- femaleMass_ALPS_lmm_emm_num + 1
LHCount_num <- femaleMass_ALPS_lmm_emm_num
tableNum <- LHCount_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
# supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

## Di LMM
```{r}
tbl <- LH_diAfternoon_flexTable
tbl
```


```{r}
tableCaption <- "Statistics from linear mixed models of average afternoon (2.5h before lights out and at lights out) LH on day of adult treatment in diestrous females. Data were fit with the formula `average LH ~ early-life treatment * adult treatment + (1 | dam)`."
```

```{r}
# LH_di_lmm_num <- LHCount_num + 1
LH_di_lmm_num <- femaleMass_ALPS_lmm_emm.pairs_num + 1
tableNum <- LH_di_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Pro LMM

```{r}
tbl <- LH_pro_flexTable
tbl
```


```{r}
tableCaption <- "Statistics from linear mixed models of maximum evening LH on day of adult treatment in proestrous females. Proestrous animals were either used for later electrophysiology studies (sampled only 2.5 and 2hrs before lights out) or for repeated hourly LH sampling around the time of lights out. Data were fit with the formula `max LH ~ early-life treatment * adult treatment + (1 | dam)`."
```

```{r}
LH_pro_lmm_num <- LH_di_lmm_num + 1
tableNum <- LH_pro_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


### EMM

```{r}
tbl <- LH_proLMM_EMM_flexTable
tbl
```

```{r}
tableCaption <- "Estimated marginal means (emmean) from linear mixed models of maximum evening LH on day of adult treatment in proestrous females. Proestrous animals were either used for later electrophysiology studies (sampled only 2.5 and 2hrs before lights out) or for repeated hourly LH sampling around the time of lights out. CI = confidence interval; STD = standard rearing; LBN = limited bedding and nesting; ALPS = adult stress."
```


```{r}
# LH_pro_lmm_emm_num <- LH_pro_lmm_num + 1
LH_pro_lmm_emm_num <- LHCount_num + 1
tableNum <- LH_pro_lmm_emm_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
supDoc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, supDoc)
```

### pairs

```{r}
tbl <- LH_proLMM_EMM.pairs_flexTable
tbl
```

```{r}
tableCaption <- "Pairwise comparisons of estimated marginal means from linear mixed models of of maximum evening LH on day of adult treatment in proestrous females. Proestrous animals were either used for later electrophysiology studies (sampled only 2.5 and 2hrs before lights out) or for repeated hourly LH sampling around the time of lights out. STD = standard rearing; LBN = limited bedding and nesting; ALPS = adult stress."
```

```{r}
# LH_pro_lmm_num <- LH_pro_lmm_emm_num + 1
LH_pro_lmm_pairs_num <- LH_pro_lmm_num + 1
tableNum <- LH_pro_lmm_pairs_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Chi-squared

```{r}
tbl <- propSurgedChiSq_flexTable
tbl
```

```{r}
propSurged_ChiSq_n <- propSurged.Chi.Sq.res$n[1]

tableCaption <- paste0("Statistics for a Chi-squared test (n = ", propSurged_ChiSq_n, ") of the effect of early-life treatment on the proportion of animals stressed in adulthood with an LH surge.")
```

```{r}
# propSurged_num <- LH_pro_lmm_pairs_num + 1
propSurged_num <- LH_pro_lmm_pairs_num
tableNum <- propSurged_num
```

```{r}
# doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Peak Time

```{r}
tbl <- LH_pro_peakTime_flexTable
tbl
```


```{r}
tableCaption <- "Statistics from linear mixed models of the time (h) of maximum evening LH on day of adult treatment in proestrous females with repeated hourly LH sampling around the time of lights out. Data were fit with the formula `time at max LH ~ early-life treatment * adult treatment + (1 | dam)`."
```

```{r}
LH_pro_peakTime_lmm_num <- LH_pro_lmm_num + 1
tableNum <- LH_pro_peakTime_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


# Figure 9 - GABA PSCs - passives and frequency

```{r}
figGABA1stRow <- plot_grid(
  figGABAa_model
  , figGABAb_model
  , figGABAc_model
  , figGABAd_model
  , ncol = 4
  , labels = c("A", "B", "C", "D")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , align = "vh"
  , axis = "lrtb"
)

figGABA2ndRow <- plot_grid(
  figGABAe_model
  , NULL
  , ncol = 2
  , labels = c("E", "F")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , rel_widths = c(1, 2)
)

# figGABA3rdRow <- plot_grid(
#   figGABA2a_model
#   , figGABA2b_model
#   , figGABA2c_model
#   , figGABA2d_model
#   , ncol = 4
#   , labels = c("G", "H", "I", "J")
#   , label_fontfamily = "Arial"
#   , label_size = textSize
#   , align = "vh"
#   , axis = "lrtb"
# )

figGABA <- plot_grid(
  get_legend(femaleBodyMassAM_ALPS_plot)
  , figGABA1stRow
  # , figGABA2ndRow
  # , figGABA3rdRow
  , nrow = 2
  , rel_heights = c(0.1, 1)
  # , rel_heights = c(0.1, 1, 1.2)
  # , rel_heights = c(.8, 1, .8)
)

figGABA
```

```{r}
flexSave(
  "figGABA"
  , plot = figGABA
  , width = twoCols
  # , height = 28/2
  , height = 7
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Count 
Not making table for paper

```{r}
tbl <- GABApsc_cellCounts_flexTable
tbl
```

## LMMs
```{r}
tbl <- pscLMMs_flexTable
tbl
```


```{r}
tableCaption <- "Statistics from linear mixed models of electrophysiology properties on day of adult treatment. The mean value for each cell was calculated, and data were fit with the formula `feature ~ early-life treatment * adult treatment + (1 | dam) + (1 | mouseID)`."
```

```{r}
psc_LMM_num <- propSurged_num + 1
tableNum <- psc_LMM_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## # of events

```{r}
tbl <- numEvents_nb.GLMM_Anova_flexTable
tbl
```

```{r}
numEvents_formula <-  getLMMFormula(numEvents_nb.GLMM_sum)

numEvents_formula <- gsub("numEvents", "# events per 240s", numEvents_formula)

tableCaption <- paste0("Statistics for number of post-synaptic current (PSC) events per 240s in GnRH neurons on the day of adult treatment. As the frequency data were skewed right and included zeros, a generalized linear mixed effects negative binomial model was used. Data were fit with the model equation `", numEvents_formula, "`. The joint_tests function of the emmeans package was used to obtain these p-value estimates from the model." )
```
```{r}
numEvents_GLMM_num <- psc_LMM_num + 1
tableNum <- numEvents_GLMM_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


```{r}
tbl <- psc_medianLQMMs_flexTable
tbl
```


```{r}
tableCaption <- paste0("Statistics for post-synaptic current (PSC) properties in GnRH neurons on the day of adult treatment. To test if treatments altered the median values of properties for all PSCs, linear quantile mixed models were fit with the model equation `log10(feature) ~ early-life treatment * adult treatment` using the package LQMM. The grouping factor was cell. The joint_tests function of the emmeans package was used to obtain these p-value estimates from the model." )
```
```{r}
LQMM_medians_num <- numEvents_GLMM_num + 1
tableNum <- LQMM_medians_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


# Figure 10 - PSC properties

```{r}

figGABA2 <- plot_grid(
  NULL
  , plot_grid(
    NULL
    , figGABAe_model
    , figGABA2a_model
    , figGABA2b_model
    , figGABA2c_model
    , figGABA2d_model
    , ncol = 3
    , labels = c("B", "C", "D", "E", "F", "G")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , align = "vh"
    , axis = "lrtb"
  )
  , nrow = 2
  , rel_heights = c(1, 2)
  , labels = c("A", "")
  , label_fontfamily = "Arial"
  , label_size = textSize
)

figGABA2
```


```{r eval=FALSE, include=FALSE}
figGABA2_left <- plot_grid(
  relPeak_byCell
  , riseTime_byCell
  , decayTime_byCell
  , fwhm_byCell
  , nrow = 4
  , labels = c("A", "C", "E", "G")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , align = "vh"
  , axis = "lrtb"
)

figGABA2_right <- plot_grid(
  relPeak_byTrt
  , riseTime_byTrt
  , decayTime_byTrt
  , fwhm_byTrt
  , nrow = 4
  , labels = c("B", "D", "F", "H")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , align = "vh"
  , axis = "lrtb"
)

figGABA2 <- plot_grid(
  figGABA2_left
  , figGABA2_right
  , ncol = 2
  # , rel_widths = c(2, 1)
)

figGABA2

```

```{r}
flexSave(
  "figPSC_props"
  , plot = figGABA2
  , width = twoCols
  # , height = 28/2
  , height = 28*2/3
  , units = "cm"
  , filePath = manuscriptFolder
)
```





