---
title: "AGG Comittee Meeting 2022-11-01"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
source("./01-scripts/04-filter-datasets.R")
source("./01-scripts/05-make-LBN-plots.R")
source("./01-scripts/06-make-LBN-ANOVAs_noLitter.R")
```

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

# Set-up
```{r}
figureNum <- 1

pptBaseName <- makeBaseNameFunc("")

plotFolder <- file.path(plotOutputFolder, "2023-03-12")

imgType <-"png"

exportImg <- exportImg_forPurposeFunc(
  imgType = imgType
  , figNumFunc = pptBaseName
  , plotFolder = plotFolder
  , compType = currentCompType
)

exportFullPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  exportImg(
    plot = plot
    , fileBaseName = baseName
    , figNum = figNum
    , units = "in"
    , width = 11.5
    , height = 5
  )
}

exportHalfPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 5.67
  #   , height = 5
  # )
}

exportThirdPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 3.6
  #   , height = 5
  # )
}

exportQuarterPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 3.2
  #   , height = 5
  # )
}

editableImgs <- TRUE
pptAddOneGraph <- function(
    title = slideTitle
    , plot = last_plot()
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_oneGraph(
    officer_ppt, 
    title, 
    plot, 
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddOneTable <- function(
    table
    , title = slideTitle
    , officer_ppt = ppt
    , dontFormat = TRUE
){
  officer_ppt <- addSlide_oneTable(
    officer_ppt, 
    title, 
    table, 
    dontFormat = dontFormat
  )
  return(officer_ppt)
}

pptUneditAddOneGraph <- function(
    title = slideTitle
    , plot = last_plot()
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_oneGraph(
    officer_ppt, 
    title, 
    plot, 
    makeEditable = FALSE
  )
  return(officer_ppt)
}

pptAddTwoGraphs <- function(
    plot1
    , plot2
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_twoGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2,
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddTwoGraphsMoreLeft <- function(
    plot1
    , plot2
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_twoGraphMoreLeft(
    officer_ppt, 
    title, 
    plot1, 
    plot2,
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddGraphTable <- function(
    plot
    , table
    , title = slideTitle
    , officer_ppt = ppt
    , dontFormat = TRUE
){
  officer_ppt <- addSlide_graphTable(
    officer_ppt, 
    title, 
    plot, 
    table,
    makeEditable = editableImgs
    , dontFormat = dontFormat
    , textSize = textSize
  )
  return(officer_ppt)
}

pptAddFourGraphs <- function(
    plot1
    , plot2
    , plot3
    , plot4
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_fourGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2, 
    plot3,
    plot4,
    makeEditable = editableImgs
    )
  return(officer_ppt)
}

pptAddThreeGraphs <- function(
    plot1
    , plot2
    , plot3
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_threeGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2, 
    plot3,
    makeEditable = editableImgs
    )
  return(officer_ppt)
}

pptAddStats <- function(
    statsText
    , officer_ppt = ppt
){
  officer_ppt <- addStatsToBottom(
    officer_ppt,
    statsText
  )
}

pptAddTwoStats <- function(
    statsText1
    , statsText2
    , officer_ppt = ppt
){
  officer_ppt <- addTwoStatsToGraphs(
    officer_ppt,
    statsText1,
    statsText2
  )
}

pptAddSectionHead <- function(
    title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_sectionHead(
    officer_ppt
    , title
  )
}
```

```{r}
# make powerpoint and title slide
ppt <- read_pptx("genericPPT.pptx")
ppt <- add_slide(ppt, layout = "Title Slide")

# layout_properties(ppt, layout="Title Slide")

subText <- "Amanda Gibson\nSBN Data"
ppt <- ph_with(
  ppt,
  value = subText,
  location = ph_location_label("Subtitle 2")
)

# Run this function to save the PPT file to the disk
# On windows, don't run if the PPT file is open
savePPT <- makeSavePPTFunc(
  presPPT = ppt
  , presFolder = plotFolder
  , presFileName = "AGG_LBN_data"
  , addDate = TRUE
)
```

```{r}
ppt <- pptAddSectionHead("Limited bedding and nesting")
```

# Dams

```{r}
damFilteredInfo <- damFiltered %>%
    select(
      - CyclesFolder
      , - cyclingFolderPath
      , -ends_with("Duration")
      ,-ends_with("Num_exits")
      ,-ends_with("Num_entries")
      ,-ends_with("_off_nest")
      ,-ends_with("_on_nest")
    ) %>%
    relocate(
      damID
      , cohort
      , litterNum
      , DOB
      , Litter_size
      , earlyLifeTrt
      , Dam_Mass_P4
      , Dam_Mass_P11
      , Dam_Mass_P21
      , starts_with("Cort_dam")
    ) %>%
    arrange(
      cohort
      , DOB
    )
```

## Corticosterone

```{r}
damCort_plot
fileBaseName <- "damCort_P11"
slideTitle <- "Effect of LBN on dam corticosterone"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
damCortANOVA_df

damCortSummary <- damFiltered %>%
  group_by(
    litterNum
    , earlyLifeTrt
  ) %>%
  meanSummary(Cort_dam_P11)

damCortSummary
```

```{r}
pptAddOneTable(
  damCortANOVA,
  title = slideTitle
)

pptAddOneTable(
  damCortSummary
  , title = slideTitle
  , dontFormat = FALSE
)
```

## Mass


```{r}
damMass_plot

fileBaseName <- "damMass"
slideTitle <- "Effect of LBN on dam mass"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```


```{r}
damMassANOVA

damMassSummary <- damFiltered %>%
  group_by(
    litterNum
    , earlyLifeTrt
  ) %>%
  meanSummary(c(Dam_Mass_P4, Dam_Mass_P11, Dam_Mass_P21)) %>%
  arrange(
    variable,
    litterNum,
    earlyLifeTrt
  )

damMassSummary
```

```{r}
pptAddOneTable(
  damMassANOVA,
  title = slideTitle
)

pptAddOneTable(
  damMassSummary
  , title = slideTitle
  , dontFormat = FALSE
)
```

```{r}
saveDFsToExcel(
  "damInfo",
  "damInfo" = damFilteredInfo,
  "damCort" = damCortSummary,
  "damCortAnova" = damCortANOVA_df,
  "damMass" = damMassSummary,
  "damMassAnova" = damMassANOVA_df,
  saveFolder = plotFolder
)
```


# Dam Behavior
```{r}
damBehavior_plot
```


<!-- ## P5-P6 analysis -->

<!-- I've analyzed additional times for P5-P6 analysis across cohorts 2, 4, 6, 7, 8 -->

<!-- ### First litters -->

<!-- ```{r} -->
<!-- damBehavior_plot_indivLines_time_1stL_no9 -->

<!-- fileBaseName <- "damBehavior_firstLitter_no9" -->
<!-- slideTitle <- "Effect of LBN on primiparous dam behavior on P5-P6" -->

<!-- exportFullPPTSlide() -->
<!-- ppt <- pptAddOneGraph() -->
<!-- ``` -->

<!-- ### Second litters -->

<!-- ```{r} -->
<!-- damBehavior_plot_indivLines_time_2ndL_no9 -->

<!-- fileBaseName <- "damBehavior_secondLitter_all" -->
<!-- slideTitle <- "Effect of LBN on multiparous dam behavior on P5-P6" -->
<!-- exportFullPPTSlide() -->
<!-- ppt <- pptAddOneGraph() -->
<!-- ``` -->

<!-- ## ZT1, ZT15, and ZT19 -->

<!-- Based on feedback from Jessica Bolton, they analyze starting 1h after light transitions. -->

<!-- For Cohort 9, we have video monitoring for the full P4-P11 period -->

<!-- ```{r} -->
<!-- damBehavior_plot_days_1stL_cohort9 -->

<!-- damBehaviorFiltered_ZTs %>% -->
<!--   filter( -->
<!--     cohort == 9 -->
<!--   ) -->

<!-- fileBaseName <- "damBehavior_firstLitter" -->
<!-- slideTitle <- "Effect of LBN on primiparous dam behavior from P4-P11" -->
<!-- exportFullPPTSlide() -->
<!-- ppt <- pptAddOneGraph() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- saveDFsToExcel( -->
<!--   "damBehavior", -->
<!--   damBehaviorFiltered_ZTs %>% -->
<!--     select( -->
<!--       damID:litterNum -->
<!--       , earlyLifeTrt -->
<!--       , ParaType -->
<!--       , Litter_size -->
<!--       , cohort -->
<!--       , DOB -->
<!--     ) %>% -->
<!--     arrange( -->
<!--       earlyLifeTrt -->
<!--       , cohort -->
<!--       , DOB -->
<!--       , damID -->
<!--       , PND -->
<!--       , time -->
<!--     ), -->
<!--   saveFolder = plotFolder -->
<!-- ) -->
<!-- ``` -->


```{r}
figureNum <- figureNum + 1
```


# Dam Corticosterone

```{r eval=FALSE, include=FALSE}
damCort_plot

fileBaseName = "DamCort_P11"
slideTitle <- "Effect of LBN on dam corticosterone on P11"

exportFullPPTSlide()
ppt <- pptAddOneGraph()

ppt <- pptAddStats(damCortANOVA_par)
```

```{r eval=FALSE, include=FALSE}
figureNum <- figureNum + 1
```

# Body mass

## First litter

```{r}
mass_plot_1stL

fileBaseName = "mass_litter1"
slideTitle <- "Effect of LBN on body mass in first litter offspring"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```
### 11-21

```{r}
mass_plot_1stL +
  coord_cartesian(x = c(11, 21), y = c(0, 16))

fileBaseName = "mass_litter1_P21"
slideTitle <- "Effect of LBN on body mass in first litter offspring"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```
### 22-35

```{r}
mass_plot_1stL +
  coord_cartesian(x = c(22, 35), y = c(0, 25))

fileBaseName = "mass_litter1_P35"
slideTitle <- "Effect of LBN on body mass in first litter offspring"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```
### 42-72

```{r}
mass_plot_1stL +
  coord_cartesian(x = c(42, 72))

fileBaseName = "mass_litter1_P72"
slideTitle <- "Effect of LBN on body mass in first litter offspring"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

## Second litter

```{r eval=FALSE, include=FALSE}
mass_plot_2ndL

fileBaseName = "mass_litter2"
slideTitle <- "Effect of LBN on body mass in second litter offspring"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r eval=FALSE, include=FALSE}
figureNum <- figureNum + 1
```

# Maturation

```{r}
ppt <- pptAddSectionHead("Offspring maturation")
```

```{r}
maturationFiltered %>%
  countMiceAndLitters(filterByVar = VO_age, groupingVars = vars(sex, earlyLifeTrt))
maturationFiltered %>%
  countMiceAndLitters(filterByVar = Estrus_age, groupingVars = vars(sex, earlyLifeTrt))
maturationFiltered %>%
  countMiceAndLitters(filterByVar = PreputialSep_age, groupingVars = vars(sex, earlyLifeTrt))

maturationFiltered %>%
  filter(
    sex == "F"
    , earlyLifeTrt == "STD"
    , !is.na(VO_age)
  )

VO_age_lmm <- lmer(
  VO_age ~ earlyLifeTrt + (1|damID)
  , data = maturationFiltered %>% filter(sex == "F")
)

print(anova(VO_age_lmm))
summary(VO_age_lmm) 

maturationFiltered %>% filter(sex == "F") %>%
  group_by(earlyLifeTrt) %>%
  meanSummary(VO_age)

maturationFiltered %>%
  filter(
    sex == "F"
    , is.na(Estrus_age) & !is.na(VO_age)
  )
```



## VO

```{r}
VO_age_plot

fileBaseName = "VO_age_litterNum"
exportHalfPPTSlide()

VO_mass_plot

fileBaseName = "VO_mass_litterNum"
exportHalfPPTSlide()

slideTitle <- "LBN did not alter age or mass at vaginal opening"

ppt <- pptAddTwoGraphs(VO_age_plot, VO_mass_plot)

ppt <- pptAddTwoStats(
  VO_age_ANOVA_par
  , VO_mass_ANOVA_par
)
```

## First Estrus

```{r}
Estrus_age_plot

fileBaseName = "Estrus_age_litterNum"
exportHalfPPTSlide()

Estrus_mass_plot

fileBaseName = "Estrus_mass_litterNum"
exportHalfPPTSlide()

slideTitle <- "LBN did not alter age or mass at first estrus"

ppt <- pptAddTwoGraphs(Estrus_age_plot, Estrus_mass_plot)

ppt <- pptAddTwoStats(
  Estrus_age_ANOVA_par
  , Estrus_mass_ANOVA_par
)

```


## Preputial Separation

```{r}
PreputialSep_age_plot

fileBaseName = "PreputialSep_age_litterNum"
exportHalfPPTSlide()

PreputialSep_mass_plot

fileBaseName = "PreputialSep_mass_litterNum"
exportHalfPPTSlide()

slideTitle <- "LBN did not alter age or mass at preputial separation"

ppt <- pptAddTwoGraphs(PreputialSep_age_plot, PreputialSep_mass_plot)

PreputialSep_age_ANOVA
PreputialSep_mass_ANOVA

ppt <- pptAddTwoStats(
  PreputialSep_age_ANOVA_par
  , PreputialSep_mass_ANOVA_par
)
```

```{r}
figureNum <- figureNum + 1
```

## Cumulative Frequency

### First litter
```{r}
VO_cumFreq_plot_1stL
fileBaseName <- "VO_freq_plot_1stL"

exportThirdPPTSlide()

Estrus_cumFreq_plot_1stL
fileBaseName <- "Estrus_freq_plot_1stL"

exportThirdPPTSlide()

PreputialSep_cumFreq_plot_1stL
fileBaseName <- "PreputialSep_freq_plot_1stL"

exportThirdPPTSlide()

slideTitle <- "Cumuluative frequency plots - first litters"

ppt <- pptAddThreeGraphs(
  VO_cumFreq_plot_1stL
  , Estrus_cumFreq_plot_1stL
  , PreputialSep_cumFreq_plot_1stL
)

```

### Second litter
```{r eval=FALSE, include=FALSE}
VO_cumFreq_plot_2ndL
fileBaseName <- "VO_freq_plot_2ndL"

exportThirdPPTSlide()

Estrus_cumFreq_plot_2ndL
fileBaseName <- "Estrus_freq_plot_2ndL"

exportThirdPPTSlide()

PreputialSep_cumFreq_plot_2ndL
fileBaseName <- "PreputialSep_freq_plot_2ndL"

exportThirdPPTSlide()

slideTitle <- "Cumuluative frequency plots - second litters"

ppt <- pptAddThreeGraphs(
  VO_cumFreq_plot_2ndL
  , Estrus_cumFreq_plot_2ndL
  , PreputialSep_cumFreq_plot_2ndL
)

```


```{r eval=FALSE, include=FALSE}
figureNum <- figureNum + 1
```

# Cycles

```{r}
ppt <- pptAddSectionHead("Estrous cycles")
```

## First litters

```{r}
repCycles_STD_1stL
fileBaseName <- "repCycles_STD_1stL"
exportThirdPPTSlide()

repCycles_LBN_1stL
fileBaseName <- "repCycles_LBN_1stL"
exportThirdPPTSlide()

percDaysStage_1stL
fileBaseName <- "percDaysStage_1stL"
exportThirdPPTSlide()

slideTitle <- "Cycles (P70-90) of first litter offspring"
ppt <- addSlide_DemoCycles(
  ppt,
  slideTitle,
  repCycles_STD_1stL,
  repCycles_LBN_1stL,
  percDaysStage_1stL
)
```

## Second litters

```{r eval=FALSE, include=FALSE}
repCycles_STD_2ndL
fileBaseName <- "repCycles_STD_2ndL"
exportThirdPPTSlide()

repCycles_LBN_2ndL
fileBaseName <- "repCycles_LBN_2ndL"
exportThirdPPTSlide()

percDaysStage_2ndL
fileBaseName <- "percDaysStage_2ndL"
exportThirdPPTSlide()

slideTitle <- "Cycles (P70-90) of second litter offspring"
ppt <- addSlide_DemoCycles(
  ppt,
  slideTitle,
  repCycles_STD_2ndL,
  repCycles_LBN_2ndL,
  percDaysStage_2ndL
)
```


```{r}
figureNum <- figureNum + 1
```


# Corticosterone Response to ALPS

```{r}
anova(
  lmer(
    cort ~ time * sex * earlyLifeTrt * adultTrt + (1|mouseID)
    , data = 
      cortFiltered_M_DiPro %>%
      filter(
        Sac_cycle == "proestrus" | sex == "M"
      )
  )
)

anova(
  lmer(
    cort ~ time *earlyLifeTrt * adultTrt + (1|mouseID)
    , data = 
      cortFiltered_M_DiPro %>%
      filter(
        Sac_cycle == "proestrus"
        , mouseID != 723
      )
  )
)
anova(
  lmer(
    cort ~ time *earlyLifeTrt * adultTrt + (1|mouseID)
    , data = 
      cortFiltered_M_DiPro %>%
      filter(
        Sac_cycle == "proestrus"
        # , mouseID != 723
      )
  )
)

acuteStressFilteredPro %>%
  group_by(
    earlyLifeTrt, adultTrt
  ) %>%
meanSummary(cort_hr5)

mean2SD <- 244.63+2*222.6
mean2SD

acuteStressFilteredPro %>%
  select(
    mouseID
    , cort_hr5
  ) %>%
  filter(
    mouseID == 723
  )

cortFilteredPro %>%
  anova_test(
    dv = cort
    , wid = mouseID
    , within = time
    , between = c(earlyLifeTrt, adultTrt)
  ) %>%
  formatAnova()

cortFilteredPro %>%
  filter(
    mouseID != 723
  ) %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = cort
    , wid = mouseID
    , between = c(earlyLifeTrt, adultTrt)
  ) %>%
  get_anova_table() %>%
  as_tibble() %>%
  mutate(
    p.adj = p * 2 # doing two cycle stage comparisons
  )

cortFilteredPro %>%
  filter(
    mouseID != 723
    , time == 5
  ) %>%
  group_by(
    adultTrt
  ) %>%
  anova_test(
    dv = cort
    , wid = mouseID
    , between = earlyLifeTrt
  ) %>%
  get_anova_table() %>%
  as_tibble() %>%
  mutate(
    p.adj = p * 2 # doing two cycle stage comparisons
  )


GABApscsFilteredPropsFreq %>%
  anova_test(
    dv = frequency
    , between = c(earlyLifeTrt, adultTrt)
  )

GABApscsFilteredPropsFreq %>%
  anova_test(
    dv = relPeak
    , between = c(earlyLifeTrt, adultTrt)
  )


acuteStressFilteredPro %>%
  group_by(
    earlyLifeTrt,
    adultTrt
  ) %>%
  meanSummary(cort_hr5)

cortFilteredPro %>%
  group_by(
    time
    , earlyLifeTrt
    , adultTrt
  ) %>%
  meanSummary(
    cort
  )

```


```{r}
cortFilteredPro_no723 <- cortFilteredPro %>%
  filter(
    mouseID != 723
  )

anova(
  lmer(
    cort ~ earlyLifeTrt * adultTrt * time + (1|mouseID)
    , cortFilteredPro
  )
)

lmm_proCort_no723 <- lmer(
    cort ~ earlyLifeTrt * adultTrt * time + (1|mouseID)
    , cortFilteredPro_no723
  )

summary(lmm_proCort_no723)
anova(
  lmm_proCort_no723
)

cortFilteredPro %>%
  anova_test(
    dv = cort
    , wid = mouseID
    , between = c(earlyLifeTrt, adultTrt)
    , within = time
  ) %>%
  formatAnova()

cortFilteredPro_no723 %>%
  anova_test(
    dv = cort
    , wid = mouseID
    , between = c(earlyLifeTrt, adultTrt)
    , within = time
  ) %>%
  formatAnova()

cortFilteredPro_no723 %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = cort
    , wid = mouseID
    , between = c(earlyLifeTrt, adultTrt)
  ) %>%
  get_anova_table() %>%
  as_tibble() %>%
  mutate(
    p.adj = p * 2 # doing two cycle stage comparisons
  ) %>%
  formatAdjAnova()

cortFilteredPro_no723 %>%
  filter(
    time == 5
  ) %>%
  group_by(
    adultTrt
  ) %>%
  anova_test(
    dv = cort
    , wid = mouseID
    , between = c(earlyLifeTrt)
  ) %>%
  get_anova_table() %>%
  as_tibble() %>%
  mutate(
    p.adj = p * 2 # doing two cycle stage comparisons
  ) %>%
  formatAdjAnova()

cortFilteredPro_no723 %>%
 group_by(
    time
    , earlyLifeTrt
    , adultTrt
  ) %>%
  meanSummary(
    cort
  )
```

```{r}
tbl <- coef(summary(lmer(
  mass ~ sex * earlyLifeTrt * day + (1 | mouseID) + (1 | damID)
  , data = mass_long %>%
    filter(
      day <= 21 & day >= 11
    )
))) %>%
  as.data.frame() %>%
  rownames_to_column("effect") %>%
  flextable() %>%
  colformat_double(digits = 3)

tbl$`Pr(>|t|)`
```

```{r}
mass_long %>%
  filter(
    day <= 21 & day >= 11
  ) %>%
  runLMM(
    mass ~ sex * earlyLifeTrt * day + (1 | mouseID) + (1 | damID)
  )
```



```{r}
ppt <- pptAddSectionHead("Response to adult stress")
```

## Plots

### Males
```{r}
maleCortPlot
fileBaseName <- "maleCortPlot"
exportFullPPTSlide()
slideTitle <- "LBN did not alter response to ALPS in males"
ppt <- pptAddOneGraph()

ppt <- pptAddStats(maleCort_3wayANOVA_par)
```


### Females

##### Uterine mass

```{r}
uterineMassByGroup_byStage_bothL

fileBaseName <- "uterineMassByGroup_byStage_bothL"
exportFullPPTSlide()

slideTitle <- "Uterine mass distribution by cycle stage and treatment"
ppt <- pptAddOneGraph()
```

```{r eval=FALSE, include=FALSE}
uterineMassByGroup_byStage_1stL

fileBaseName <- "uterineMassByGroup_byStage_1stL"
exportFullPPTSlide()

slideTitle <- "Uterine mass distribution by cycle stage and treatment - first litter successes"
ppt <- pptAddOneGraph()
```

```{r eval=FALSE, include=FALSE}
uterineMassByGroup_byStage_2ndL

fileBaseName <- "uterineMassByGroup_byStage_2ndL"
exportFullPPTSlide()

slideTitle <- "Uterine mass distribution by cycle stage and treatment - second litter successes"
ppt <- pptAddOneGraph()
```


```{r eval=FALSE, include=FALSE}
diCortPlot
fileBaseName <- "diCortPlot"
exportFullPPTSlide()
slideTitle <- "LBN-ALPS mice have a higher corticosterone response than STD-ALPS on diestrus"
ppt <- pptAddOneGraph()
```

```{r}
proCortPlot_no723 <- cortFilteredPro %>%
  filter(
    mouseID != 723
  ) %>%
  plotCort_bothL()
proCortPlot_no723
fileBaseName <- "proCortPlot_no723"
exportFullPPTSlide()


proCortPlot
fileBaseName <- "proCortPlot"
exportFullPPTSlide()
slideTitle <- "LBN did not alter response to ALPS on proestrus"
ppt <- pptAddOneGraph()
```

#### ANOVAs

```{r}

cort3way_pro

ppt <- addSlide_oneTable(
  ppt,
  "Corticosterone response of LBN proestrus, first litter mice",
  cort3way_byCycle,
  dontFormat = TRUE
)

```

<!-- 4-way ANOVA - LBN x ALPS x Cycle Stage x Time -->

<!-- ```{r} -->
<!-- cort4wayANOVA -->
<!-- # ppt <- addSlide_oneTable( -->
<!-- #   ppt, -->
<!-- #   "Females - 4way ANOVA of early-life trt x adult trt x time x stage", -->
<!-- #   cort4wayANOVA, -->
<!-- #   dontFormat = TRUE -->
<!-- # ) -->

<!-- getFText(cort4wayANOVA_df, "earlyLifeTrt:adultTrt:Sac_cycle:time") -->
<!-- ``` -->



<!-- There is a significant 4-way interaction, so do the 3-way interaction of  -->
<!-- LBN x ALPS x Time for each cycle stage. Correct for two comparisons -->

<!-- ```{r} -->

<!-- cort3way_byCycle -->

<!-- # ppt <- addSlide_oneTable( -->
<!-- #   ppt, -->
<!-- #   "LBN diestrous mice with respond differently to CON vs ALPS than than STD diestrous", -->
<!-- #   cort3way_byCycle, -->
<!-- #   dontFormat = TRUE -->
<!-- # ) -->

<!-- cort3way_byCycle_df %>% -->
<!--   filter( -->
<!--     Sac_cycle == "diestrus" -->
<!--   ) %>% -->
<!--   getFText( -->
<!--     "earlyLifeTrt:adultTrt:time", -->
<!--     doAdj = TRUE -->
<!--   ) -->

<!-- cort3way_byCycle_df %>% -->
<!--   filter( -->
<!--     Sac_cycle == "proestrus" -->
<!--   ) %>% -->
<!--   getFText( -->
<!--     "adultTrt:time", -->
<!--     doAdj = TRUE -->
<!--   ) -->
<!-- ``` -->

<!-- For diestrous mice, there is a 3-way interaction of LBN x ALPS x time -->

<!-- For proestrous mice, there is a 2-way interaction of ALPS x time -->


<!-- Follow-up the diestrous mice with a 2-way interaction between  -->
<!-- LBN x ALPS at each time. Adjust the p-values for two levels of time -->

<!-- ```{r} -->
<!-- diCort2way_byTime -->
<!-- # ppt <- addSlide_oneTable( -->
<!-- #   ppt, -->
<!-- #   "Early-life and adult trt interact to affect post-trt cort values in diestrous mice", -->
<!-- #   diCort2way_byTime, -->
<!-- #   dontFormat = TRUE -->
<!-- # ) -->

<!-- diCort2way_byTime_df %>% -->
<!--   filter( -->
<!--     time == 5 -->
<!--   ) %>% -->
<!--   getFText( -->
<!--     "earlyLifeTrt:adultTrt" -->
<!--     , doAdj = TRUE -->
<!--   ) -->
<!-- ``` -->


<!-- At the end of the paradigm, there is an interaction between LBN and ALPS for -->
<!-- the diestrous mice. This means that LBN changes the way that the mice -->
<!-- respond to the ALPS paradigm in diestrous mice. -->



<!-- For the diestrous mice at the end of the paradigm, group by adult treatment -->
<!-- and see if the early-life mice are significantly different. -->
<!-- Adjust for making two treatment comparisons -->

<!-- ```{r} -->

<!-- diCortPost_byALPS -->

<!-- # ppt <- addSlide_oneTable( -->
<!-- #   ppt, -->
<!-- #   "STD and LBN diestrous mice differ in cort after ALPS trt", -->
<!-- #   diCortPost_byALPS, -->
<!-- #   dontFormat = TRUE -->
<!-- # ) -->

<!-- diCortPost_byALPS_df %>% -->
<!--   filter( -->
<!--     adultTrt == "ALPS" -->
<!--   ) %>% -->
<!--   getFText( -->
<!--     "earlyLifeTrt", -->
<!--     doAdj = TRUE -->
<!--   ) -->
<!-- diCortPost_byALPS_df %>% -->
<!--   filter( -->
<!--     adultTrt == "CON" -->
<!--   ) %>% -->
<!--   getFText( -->
<!--     "earlyLifeTrt", -->
<!--     doAdj = TRUE -->
<!--   ) -->
<!-- ``` -->

<!-- For the proestrous mice, follow up the ALPS x time interaction. -->

<!-- Group by time, see if there is an effect of ALPS -->

<!-- ```{r} -->
<!-- proCort_byTime -->
<!-- # ppt <- addSlide_oneTable( -->
<!-- #   ppt, -->
<!-- #   "ALPS proestrous mice have higher post-trt cort than CON mice", -->
<!-- #   proCort_byTime, -->
<!-- #   dontFormat = TRUE -->
<!-- # ) -->

<!-- proCort_byTime_df %>% -->
<!--   filter( -->
<!--     time == "5" -->
<!--   ) %>% -->
<!--   getFText( -->
<!--     "adultTrt" -->
<!--     , doAdj = TRUE -->
<!--   ) -->
<!-- ``` -->


# LH response to ALPS

<!-- ## Second litter -->
<!-- ```{r} -->
<!-- LHplot_pro_2ndL -->

<!-- fileBaseName <- "proLHresponse_2ndL" -->
<!-- exportFullPPTSlide() -->

<!-- slideTitle <- "Effect of LBN and ALPS on proestrous LH release in second litters" -->
<!-- ppt <- pptAddOneGraph() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- LHamp_2ndL_plot -->

<!-- fileBaseName <- "LHamp_2ndL" -->
<!-- exportFullPPTSlide() -->


<!-- fileBaseName <- "LHamp_2ndL_half" -->
<!-- exportHalfPPTSlide() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- percSurgedPlot_2ndL -->

<!-- fileBaseName <- "LHsurged_2ndL" -->
<!-- exportHalfPPTSlide() -->

<!-- slideTitle <- "More second litter LBN-ALPS mice exhibited an LH surge than STD-ALPS mice" -->
<!-- ppt <- pptAddTwoGraphsMoreLeft( -->
<!--   LHamp_2ndL_plot -->
<!--   , percSurgedPlot_2ndL -->
<!-- ) -->
<!-- ``` -->


## First litter
```{r}
LHplot_pro_1stL

fileBaseName <- "proLHresponse_1stL"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on proestrous LH release in first litters up to 2h before lights out"
ppt <- pptAddOneGraph()
```
```{r}
LHamp_1stL_plot

fileBaseName <- "LHamp_1stL"
exportFullPPTSlide()
fileBaseName <- "LHamp_1stL_half"
exportHalfPPTSlide()
```
```{r}
percSurgedPlot_1stL

fileBaseName <- "LHsurged_1stL"
exportHalfPPTSlide()

slideTitle <- "LBN may be delaying the start of the LH surge"
ppt <- pptAddTwoGraphsMoreLeft(
  LHamp_1stL_plot
  , percSurgedPlot_1stL
)
```

# Cort administration

```{r}
source(file.path(scriptsFolder, "cortAdmin-get-datasets.R"))
source(file.path(scriptsFolder, "07-make-cortAdmin-plots.R"))

```

```{r}
BD_ALPS_plot
fileBaseName <- "BD_ALPS_plot"
exportFullPPTSlide()

slideTitle <- "ALPS increases corticosterone - add BD pic"
ppt <- pptAddOneGraph()
```
```{r}
BD_comboNutALPS_plot
fileBaseName <- "BD_comboNutALPS_plot"
exportFullPPTSlide()

slideTitle <- "Feeding corticosterone recapitulates its pattern during ALPS - add BD pic"
ppt <- pptAddOneGraph()
```


# GABA PSCs

```{r}
ppt <- pptAddSectionHead("GABA PSCs to GnRH neurons on proestrus")
```

## Passives
```{r}
RinputPlot
fileBaseName <- "Rinput"
exportQuarterPPTSlide()


RseriesPlot
fileBaseName <- "Rseries"
exportQuarterPPTSlide()

capacitancePlot

fileBaseName <- "capacitance"
exportQuarterPPTSlide()

holdingCurrPlot
fileBaseName <- "holdingCurr"
exportQuarterPPTSlide()


slideTitle <- "Passive properties for GABA recordings"
ppt <- pptAddFourGraphs(
  RseriesPlot
  , RinputPlot
  , capacitancePlot
  , holdingCurrPlot
)
```

```{r}
RseriesANOVA
RinputANOVA
capacitanceANOVA
holdingCurrANOVA
GABAfreqANOVA
GABAampANOVA

GABApscsFilteredPropsFreq %>%
  countMiceAndLitters(frequency, vars(earlyLifeTrt, adultTrt))
```


```{r}
RseriesANOVA

slideTitle <- "Series resistance does not differ with LBN or ALPS"
ppt <- pptAddOneGraph(
  plot = RseriesPlot
)

ppt <- pptAddStats(RseriesANOVA_par)

RinputANOVA

slideTitle <- "LBN cells have a lower input resistance than STD cells"
ppt <- pptAddOneGraph(
  plot = RinputPlot
)

ppt <- pptAddStats(RinputANOVA_par)


capacitanceANOVA
slideTitle <- "Capacitance does not differ with LBN or ALPS"
ppt <- pptAddOneGraph(
  plot = capacitancePlot
) 

ppt <- pptAddStats(capacitanceANOVA_par)

holdingCurrANOVA
slideTitle <- "There is a trend for lower holding current in LBN cells"
ppt <- pptAddOneGraph(
  plot = holdingCurrPlot
)

ppt <- pptAddStats(holdingCurrANOVA_par)
```

```{r}
GABAfreqPlot
fileBaseName <- "GABAfreqPlot"
exportFullPPTSlide()

GABAfreqANOVA

slideTitle <- "Frequency of GABA PSCs does not differ with early-life or adult treatment"
ppt <- pptAddOneGraph(
  plot = GABAfreqPlot
)

ppt <- pptAddStats(GABAfreqANOVA_par)

GABAampPlot
fileBaseName <- "GABAampPlot"
exportFullPPTSlide()

GABAampANOVA
slideTitle <- "Amplitude of GABA PSCs does not differ with early-life or adult treatment"
ppt <- pptAddOneGraph(
  plot = GABAampPlot
)

ppt <- pptAddStats(GABAampANOVA_par)
```





