---
title: "AGG LBN Data Update - 2022"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
source("./01-scripts/04-filter-datasets.R")
source("./01-scripts/05-make-LBN-plots.R")
source("./01-scripts/06-make-LBN-ANOVAs.R")
```

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

# Set-up
```{r}
figureNum <- 1

pptBaseName <- makeBaseNameFunc("")

plotFolder <- file.path(plotOutputFolder, "LBN_Fall2022")

imgType <-"png"

exportImg <- exportImg_forPurposeFunc(
  imgType = imgType
  , figNumFunc = pptBaseName
  , plotFolder = plotFolder
  , compType = currentCompType
)

exportFullPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 11.5
  #   , height = 5
  # )
}

exportHalfPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 5.67
  #   , height = 5
  # )
}

exportThirdPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 3.6
  #   , height = 5
  # )
}

exportQuarterPPTSlide <- function(
    plot = last_plot()
    , baseName = fileBaseName
    , figNum = figureNum
){
  # exportImg(
  #   plot = plot
  #   , fileBaseName = baseName
  #   , figNum = figNum
  #   , units = "in"
  #   , width = 3.2
  #   , height = 5
  # )
}

editableImgs <- TRUE
pptAddOneGraph <- function(
    title = slideTitle
    , plot = last_plot()
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_oneGraph(
    officer_ppt, 
    title, 
    plot, 
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptUneditAddOneGraph <- function(
    title = slideTitle
    , plot = last_plot()
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_oneGraph(
    officer_ppt, 
    title, 
    plot, 
    makeEditable = FALSE
  )
  return(officer_ppt)
}

pptAddTwoGraphs <- function(
    plot1
    , plot2
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_twoGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2,
    makeEditable = editableImgs
  )
  return(officer_ppt)
}

pptAddFourGraphs <- function(
    plot1
    , plot2
    , plot3
    , plot4
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_fourGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2, 
    plot3,
    plot4,
    makeEditable = editableImgs
    )
  return(officer_ppt)
}

pptAddThreeGraphs <- function(
    plot1
    , plot2
    , plot3
    , title = slideTitle
    , officer_ppt = ppt
){
  officer_ppt <- addSlide_threeGraph(
    officer_ppt, 
    title, 
    plot1, 
    plot2, 
    plot3,
    makeEditable = editableImgs
    )
  return(officer_ppt)
}
```

```{r}
# make powerpoint and title slide
ppt <- read_pptx("genericPPT.pptx")
ppt <- add_slide(ppt, layout = "Title Slide")
ppt <- ph_with(
  ppt,
  value = paste("LBN data on", Sys.Date()),
  location = ph_location_label("Title 1")
)

# Run this function to save the PPT file to the disk
# On windows, don't run if the PPT file is open
savePPT <- makeSavePPTFunc(
  presPPT = ppt
  , presFolder = plotFolder
  , presFileName = "AGG_LBN_data"
  , addDate = TRUE
)
```

# Cohort Information

-   Cohort 1

    -   CBA and B6 dams

    -   P2-P9

All later cohorts are CBA dams, P4-P11

-   Cohort 2
    -   First litter
    -   Winter 2021
    -   Females diestrous cort
-   Cohort 3
    -   First litter
    -   Used for body mass / maturation judgments
    -   Not included in data in this report, as different amounts of handling of offspring
    -   Dams rebred for Cohort 4
-   Cohort 4
    -   Second litter
    -   Spring/summer 2021
    -   Females proestrous cort/LH
-   Cohort 5
    -   Used for body mass/maturation judgments
    -   Used for determining proestrus
    -   Not included in data in this report
    -   Dams rebred for Cohort 6
-   Cohort 6
    -   Second litter
    -   Spring/summer 2021
    -   Females proestrous cort/LH and diestrous cort/LH
-   Cohort 7
    -   First litter
    -   Fall 2021/Winter 2022
    -   Females proestrous cort/LH (to 0.5h after ALPS) then GABA recordings
-   Cohort 8
    -   Second litter
    -   Fall 2021/Winter 2022
    -   Females diestrous cort/LH
-   Cohort 9
    -   Fall 2022/Winter 2023
    -   Females to be used for
        -   Proestrous cort/LH to 2h after lights out

        -   GABA recordings

        -   Excitability of GnRH neurons

```{r}
slideTitle <- "Cohort Information"

listLevels <- c(
  1, 2, 2,
  1, 2, 2, 2, 2, 
  1, 2, 2, 2, 
  1, 2, 2, 2, 2,
  1, 2, 2, 2,
  1, 2, 2, 2,
  1, 2, 2, 2,
  1, 2, 2, 2, 2, 2
  )
slideText <- block_list(
  makeBullet("Cohort 2"),
    makeBullet("Winter 2021"),
    makeBullet("Females diestrous cort"),
  makeBullet("Cohort 3"),
    makeBullet("First litter"),
    makeBullet("Used for body mass / maturation judgments"),
    makeBullet("Not included in data in this report, as different amounts of handling of offspring"),
    makeBullet("Dams rebred for Cohort 4"),
  makeBullet("Cohort 4"),
    makeBullet("Second litter"),
    makeBullet("Spring/summer 2021"),
    makeBullet("Females proestrous cort/LH"),
  makeBullet("Cohort 5"),
    makeBullet("Used for body mass/maturation judgments"),
    makeBullet("Used for determining proestrus"),
    makeBullet("Not included in data in this report"),
    makeBullet("Dams rebred for Cohort 6"),
  makeBullet("Cohort 6"),
    makeBullet("Second litter"),
    makeBullet("Spring/summer 2021"),
    makeBullet("Females proestrous cort/LH and diestrous cort/LH"),
  makeBullet("Cohort 7"),
    makeBullet("First litter"),
    makeBullet("Fall 2021/Winter 2022"),
    makeBullet("Females proestrous cort/LH (to 0.5h after ALPS) then GABA recordings"),
  makeBullet("Cohort 8"),
    makeBullet("Second litter"),
    makeBullet("Fall 2021/Winter 2022"),
    makeBullet("Females diestrous cort/LH"),
  makeBullet("Cohort 9"),
    makeBullet("Fall 2022/Winter 2023"),
    makeBullet("Females to be used for"),
    makeBullet("Proestrous cort/LH to 2h after lights out"),
    makeBullet("GABA recordings"),
    makeBullet("Excitability of GnRH neurons")
)

ppt <- addSlide_text(
  ppt,
  slideTitle,
  slideText,
  listLevels
)
```

# Dam Behavior

## ZT1 and ZT15

Based on feedback from Jessica Bolton, they analyze starting 1h after light transitions.

For Cohort 9, we have video monitoring for the full P4-P11 period

```{r}
slideTitle <- "ZT1 and ZT15"


listLevels <- c(
  1, 1
  )
slideText <- block_list(
  makeBullet("Based on feedback from Jessica Bolton, they analyze starting 1h after light transitions"),
  makeBullet("For Cohort 9, we have video monitoring for the full P4-P11 period")
)

ppt <- addSlide_text(
  ppt,
  slideTitle,
  slideText,
  listLevels
)
```

### First litters

```{r}
damBehavior_plot_days_1stL

fileBaseName <- "damBehavior_firstLitter"
slideTitle <- "Effect of LBN on naive dam behavior over time"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

### Second litters

```{r}
damBehavior_plot_days_2ndL

fileBaseName <- "damBehavior_secondLitter"
slideTitle <- "Effect of LBN on experienced dam behavior over time"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
# 1 -> 2
figureNum <- figureNum + 1
```

## P5-P6 analysis

I've analyzed additional times for P5-P6 analysis across cohorts 2, 4, 6, 7, 8

```{r}
slideTitle <- "P5-P6 Analysis"


listLevels <- c(
  1
  )
slideText <- block_list(
  makeBullet("I've analyzed additional times for P5-P6 analysis across cohorts 2, 4, 6, 7, 8")
)

ppt <- addSlide_text(
  ppt,
  slideTitle,
  slideText,
  listLevels
)
```

### First litters

```{r}
damBehavior_plot_time_1stL

fileBaseName <- "damBehavior_firstLitter_all"
slideTitle <- "Effect of LBN on naive dam behavior P5-P6"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

### Second litters

```{r}
damBehavior_plot_time_2ndL

fileBaseName <- "damBehavior_secondLitter_all"
slideTitle <- "Effect of LBN on experienced dam behavior P5-P6"
exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

## ANOVA

Ultimately, if we focus on ZT1 and ZT15, could do a three-way ANOVA of

-   Treatment

    -   STD vs LBN

-   Day

    -   PND4-11

-   Time

    -   ZT1 ZT15

We wouldn't be able to look at first litter versus second litter with this analysis, though. Ultimately, we may be able to compare how the PND5 ZT15 and PND6 ZT1 times compare with the new, prolonged recordings, compared to the original, limited recordings.

The biggest difference I've seen still appears to be at the ZT19 time, which may still be worth also analyzing for the new recordings

```{r}
slideTitle <- "Behavior analysis"


listLevels <- c(
  1,1, 1
  )
slideText <- block_list(
  makeBullet("Ultimately, if we focus on ZT1 and ZT15, could do a three-way ANOVA of treatment (STD vs LBN), time (ZT1 vs ZT15), day (P4-P11). We wouldn't be able to compare second litter behavior with this analysis, though, because we only have P5 ZT15 and P6 ZT1."),
  makeBullet("we may be able to compare how the PND5 ZT15 and PND6 ZT1 times compare with the new, prolonged recordings, compared to the original, limited recordings."),
  makeBullet("The biggest difference I've seen still appears to be at the ZT19 time, which may still be worth also analyzing for the new recordings")
)

ppt <- addSlide_text(
  ppt,
  slideTitle,
  slideText,
  listLevels
)
```

```{r eval=FALSE, include=FALSE}

damBehaviorAnova <- dam_behavior_filtered %>%
  anova_test(
    dv = Num_exits,
    wid = damID,
    between = c(earlyLifeTrt, litterNum),
    within = c(time)
  ) 

damBehaviorAnova$ANOVA%>%
  myDisplay()

dam_behavior_filtered %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = Num_exits,
    between = c(earlyLifeTrt)
  ) %>%
  adjust_pvalue(method = "bonferroni")
```

```{r}
# 2 -> 3
figureNum <- figureNum + 1
```

# Dam Corticosterone

```{r}
damCort_plot

fileBaseName = "DamCort_P11"
slideTitle <- "Effect of LBN on dam corticosterone on P11"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

```{r}
ppt <- addSlide_oneTable(
  ppt,
  "Effect of LBN on dam corticosterone on P11",
  damCortANOVA
)
```

```{r}
# 3 -> 4
figureNum <- figureNum + 1
```

# Body mass

## First litter

```{r}
mass_plot_1stL

fileBaseName = "mass_litter1"
slideTitle <- "Effect of LBN on body mass in first litter offspring"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

## Second litter

```{r}
mass_plot_2ndL

fileBaseName = "mass_litter2"
slideTitle <- "Effect of LBN on body mass in second litter offspring"

exportFullPPTSlide()
ppt <- pptAddOneGraph()
```

## Linear mixed effects model

I've divided up the mass data into three epochs that are roughly linear looking on the graphs

-   P11-P21

-   P22-P35

-   P42-P72

I think that the linear mixed effects model is more appropriate than an ANOVA here because it takes into account the "meaning" of time (age), and we can incorporate all of the mass data without having an absurd number of comparisons as would be required with an ANOVA

```{r}
slideTitle <- "Mass linear mixed effects model"


listLevels <- c(
  1, 2, 2, 2, 
  1
  )
slideText <- block_list(
  makeBullet("I've divided up the mass data into three epochs that are roughly linear looking on the graphs"),
  makeBullet("P11-P21"),
  makeBullet("P22-P35"),
  makeBullet("P42-P72"),
  makeBullet("I think that the linear mixed effects model is more appropriate than an ANOVA here because it takes into account the \"meaning\" of time (age), and we can incorporate all of the mass data without having an absurd number of comparisons as would be required with an ANOVA")
)

ppt <- addSlide_text(
  ppt,
  slideTitle,
  slideText,
  listLevels
)
```

```{r include=FALSE}
library("lmerTest")
library("lme4")
library("emmeans")
```

## Before weaning

```{r}
preWeanMass_mod <- lmer(
  mass ~ earlyLifeTrt*sex*day + Litter_size + litterNum + (1 | damID),
  data = mass_long %>% 
    mutate(Litter_size = as.integer(Litter_size)) %>% 
    filter(
      day > 4,
      day <= 21
    ) %>%
    mutate(
      day = day - 11 # make it so that day 11 is 0 so intercept makes sense
    )
)
summary(preWeanMass_mod)
anova(preWeanMass_mod)


# https://stats.stackexchange.com/questions/331238/post-hoc-pairwise-comparison-of-interaction-in-mixed-effects-lmer-model
# Don't know how to do the post-hoc here because day is a numeric variable

# emm = emmeans(preWeanMass_mod, ~ earlyLifeTrt * sex * day)
emm = emmeans(preWeanMass_mod, ~ earlyLifeTrt * sex)
pairs(emm, simple = "each")
```

There's a three-way interaction between age, sex, and early-life treatment before weaning. However, I don't know how to do the post-hoc analysis for this, because day is a continuous, numeric variable and not a discrete factor. For that reason, I've done the two-way comparison for now, but will need to return to this.

```{r}
ppt <- ppt %>%
  addSlide_oneTable(
    "Effect of LBN on body mass before weaning",
    anova(preWeanMass_mod) %>% as_tibble(rownames = " ")
  )
```

```{r}
slideTitle <- "Pre-weaning mass linear mixed effects model"


listLevels <- c(
  1
  )
slideText <- block_list(
  makeBullet("There's a three-way interaction between age, sex, and early-life treatment before weaning. However, I don't know how to do the post-hoc analysis for this, because day is a continuous, numeric variable and not a discrete factor. For that reason, I've done the two-way comparison for now, but will need to return to this.")
)

ppt <- addSlide_text(
  ppt,
  slideTitle,
  slideText,
  listLevels
)
```

```{r eval=FALSE, include=FALSE}
ppt <- ppt %>%
  addSlide_oneTable(
    "Effect of LBN on body mass before weaning",
    emmPairs %>% as.data.frame()
  )
```

## 22 to 35

```{r}
postWeanMass_mod <- lmer(
  mass ~ earlyLifeTrt*sex*day + Litter_size + litterNum + (1 | damID),
  data = mass_long %>% 
    mutate(Litter_size = as.integer(Litter_size)) %>% 
    filter(
      day > 21,
      day <= 35
    )
)
summary(postWeanMass_mod)
anova(postWeanMass_mod)


# https://stats.stackexchange.com/questions/331238/post-hoc-pairwise-comparison-of-interaction-in-mixed-effects-lmer-model
emm = emmeans(postWeanMass_mod, ~ earlyLifeTrt * sex)
emmPairs <- pairs(emm, simple = "each")
emmPairs

```

```{r}
ppt <- ppt %>%
  addSlide_oneTable(
    "Effect of LBN on body mass P22-P35",
    anova(postWeanMass_mod) %>% as_tibble(rownames = " ")
  )
```

```{r}
ppt <- ppt %>%
  addSlide_oneTable(
    "Effect of LBN on body mass P22-P35",
    emmPairs %>% as.data.frame()
  )
```

## P42 to P72

There are no differences by early-life treatment at this age

```{r}
adultMass_mod <- lmer(
  mass ~ earlyLifeTrt*sex*day + Litter_size + litterNum + (1 | damID),
  data = mass_long %>% 
    mutate(Litter_size = as.integer(Litter_size)) %>% 
    filter(
      day > 35
    )
)
summary(adultMass_mod)
anova(adultMass_mod)
```

```{r}
ppt <- ppt %>%
  addSlide_oneTable(
    "Effect of LBN on body mass P42-P72",
    anova(adultMass_mod) %>% as_tibble(rownames = " ")
  )
```

```{r}
slideTitle <- "Adult mass linear mixed effects model"


listLevels <- c(
  1
  )
slideText <- block_list(
  makeBullet("There are no differences by early-life treatment at this age")
)

ppt <- addSlide_text(
  ppt,
  slideTitle,
  slideText,
  listLevels
)
```

```{r}
# 4 -> 5
figureNum <- figureNum + 1
```

# Maturation

## VO

```{r}
VO_age_plot

fileBaseName = "VO_age_litterNum"
exportHalfPPTSlide()

VO_mass_plot

fileBaseName = "VO_mass_litterNum"
exportHalfPPTSlide()

slideTitle <- "Effect of LBN on vaginal opening"

ppt <- pptAddTwoGraphs(VO_age_plot, VO_mass_plot)

VO_age_ANOVA
VO_mass_ANOVA

ppt <- addSlide_oneTable(
  ppt,
  "Effect of LBN and experience on age at vaginal opening",
  VO_age_ANOVA %>% formatAnova(16),
  dontFormat=TRUE
)
ppt <- addSlide_oneTable(
  ppt,
  "Effect of LBN and experience on mass at vaginal opening",
  VO_mass_ANOVA %>% formatAnova(16),
  dontFormat=TRUE
)
```

## First Estrus

```{r}
Estrus_age_plot

fileBaseName = "Estrus_age_litterNum"
exportHalfPPTSlide()

Estrus_mass_plot

fileBaseName = "Estrus_mass_litterNum"
exportHalfPPTSlide()

slideTitle <- "Effect of LBN on first estrus"

ppt <- pptAddTwoGraphs(Estrus_age_plot, Estrus_mass_plot)

Estrus_age_ANOVA
Estrus_mass_ANOVA

ppt <- addSlide_oneTable(
  ppt,
  "Effect of LBN and experience on age at first estrus",
  Estrus_age_ANOVA %>% formatAnova(16),
  dontFormat=TRUE
)
ppt <- addSlide_oneTable(
  ppt,
  "Effect of LBN and experience on mass at first estrus",
  Estrus_mass_ANOVA %>% formatAnova(16),
  dontFormat=TRUE
)
```


## Preputial Separation

```{r}
PreputialSep_age_plot

fileBaseName = "PreputialSep_age_litterNum"
exportHalfPPTSlide()

PreputialSep_mass_plot

fileBaseName = "PreputialSep_mass_litterNum"
exportHalfPPTSlide()

slideTitle <- "Effect of LBN on preputial separation"

ppt <- pptAddTwoGraphs(PreputialSep_age_plot, PreputialSep_mass_plot)

PreputialSep_age_ANOVA
PreputialSep_mass_ANOVA

ppt <- addSlide_oneTable(
  ppt,
  "Effect of LBN and experience on age at preputial separation",
  PreputialSep_age_ANOVA %>% formatAnova(16),
  dontFormat=TRUE
)
ppt <- addSlide_oneTable(
  ppt,
  "Effect of LBN and experience on mass at preputial separation",
  PreputialSep_mass_ANOVA %>% formatAnova(16),
  dontFormat=TRUE
)
```

```{r}
# 5 -> 6
figureNum <- figureNum + 1
```

## Cumulative Frequency

### First litter
```{r}
VO_cumFreq_plot_1stL
fileBaseName <- "VO_freq_plot_1stL"

exportThirdPPTSlide()

Estrus_cumFreq_plot_1stL
fileBaseName <- "Estrus_freq_plot_1stL"

exportThirdPPTSlide()

PreputialSep_cumFreq_plot_1stL
fileBaseName <- "PreputialSep_freq_plot_1stL"

exportThirdPPTSlide()

slideTitle <- "Cumuluative frequency plots - first litters"

ppt <- pptAddThreeGraphs(
  VO_cumFreq_plot_1stL
  , Estrus_cumFreq_plot_1stL
  , PreputialSep_cumFreq_plot_1stL
)

```

### Second litter
```{r}
VO_cumFreq_plot_2ndL
fileBaseName <- "VO_freq_plot_2ndL"

exportThirdPPTSlide()

Estrus_cumFreq_plot_2ndL
fileBaseName <- "Estrus_freq_plot_2ndL"

exportThirdPPTSlide()

PreputialSep_cumFreq_plot_2ndL
fileBaseName <- "PreputialSep_freq_plot_2ndL"

exportThirdPPTSlide()

slideTitle <- "Cumuluative frequency plots - second litters"

ppt <- pptAddThreeGraphs(
  VO_cumFreq_plot_2ndL
  , Estrus_cumFreq_plot_2ndL
  , PreputialSep_cumFreq_plot_2ndL
)

```

```{r}
maturationFiltered %>%
  anova_test(
    dv = VO_age,
    between = c(earlyLifeTrt, litterNum)
  )
maturation_byDam_f %>%
  filter(
    cohort != 9
  ) %>%
  anova_test(
    dv = VO_age,
    between = c(earlyLifeTrt, litterNum)
  )
```

```{r}
# 6 -> 7
figureNum <- figureNum + 1
```
# Cycles

## First litters

```{r}
repCycles_STD_1stL
fileBaseName <- "repCycles_STD_1stL"
exportThirdPPTSlide()

repCycles_LBN_1stL
fileBaseName <- "repCycles_LBN_1stL"
exportThirdPPTSlide()

percDaysStage_1stL
fileBaseName <- "percDaysStage_1stL"
exportThirdPPTSlide()

slideTitle <- "Cycles (P70-90) of first litter offspring"
ppt <- addSlide_DemoCycles(
  ppt,
  slideTitle,
  repCycles_STD_1stL,
  repCycles_LBN_1stL,
  percDaysStage_1stL
)
```

## Second litters

```{r}
repCycles_STD_2ndL
fileBaseName <- "repCycles_STD_2ndL"
exportThirdPPTSlide()

repCycles_LBN_2ndL
fileBaseName <- "repCycles_LBN_2ndL"
exportThirdPPTSlide()

percDaysStage_2ndL
fileBaseName <- "percDaysStage_2ndL"
exportThirdPPTSlide()

slideTitle <- "Cycles (P70-90) of second litter offspring"
ppt <- addSlide_DemoCycles(
  ppt,
  slideTitle,
  repCycles_STD_2ndL,
  repCycles_LBN_2ndL,
  percDaysStage_2ndL
)
```


```{r}
# 7 -> 8
figureNum <- figureNum + 1
# figureNum <- 8
```

# Uterine mass

```{r}
uterineMassByGroup_byStage_bothL

fileBaseName <- "uterineMassByGroup_byStage_bothL"
exportFullPPTSlide()

slideTitle <- "Uterine mass distribution by cycle stage and treatment"
ppt <- pptAddOneGraph()
```

```{r}
uterineMassByGroup_byStage_1stL

fileBaseName <- "uterineMassByGroup_byStage_1stL"
exportFullPPTSlide()

slideTitle <- "Uterine mass distribution by cycle stage and treatment - first litter successes"
ppt <- pptAddOneGraph()
```

```{r}
uterineMassByGroup_byStage_2ndL

fileBaseName <- "uterineMassByGroup_byStage_2ndL"
exportFullPPTSlide()

slideTitle <- "Uterine mass distribution by cycle stage and treatment - second litter successes"
ppt <- pptAddOneGraph()
```


```{r}
# 8 -> 9
figureNum <- figureNum + 1
# figureNum <- 9
```

# Corticosterone Response to ALPS

## Plots

### Males
```{r}
maleCortPlot
fileBaseName <- "maleCortPlot"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in males"
ppt <- pptAddOneGraph()

maleCortPlot_1stL
fileBaseName <- "maleCortPlot_1stL"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in first litter males"
ppt <- pptAddOneGraph()

maleCortPlot_2ndL
fileBaseName <- "maleCortPlot_2ndL"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in second litter males"
ppt <- pptAddOneGraph()
```

```{r}
maleCort_3wayANOVA
ppt <- addSlide_oneTable(
  ppt,
  "Males - 3way ANOVA of early-life trt x adult trt x time",
  maleCort_3wayANOVA,
  dontFormat = TRUE
)
```

### Females
```{r}
diCortPlot
fileBaseName <- "diCortPlot"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in diestrous mice"
ppt <- pptAddOneGraph()

diCortPlot_1stL
fileBaseName <- "diCortPlot_1stL"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in first litter diestrous mice"
ppt <- pptAddOneGraph()

diCortPlot_2ndL
fileBaseName <- "diCortPlot_2ndL"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in second litter diestrous mice"
ppt <- pptAddOneGraph()
```

```{r}
proCortPlot
fileBaseName <- "proCortPlot"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in proestrous mice"
ppt <- pptAddOneGraph()

proCortPlot_1stL
fileBaseName <- "proCortPlot_1stL"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in first litter proestrous mice"
ppt <- pptAddOneGraph()

proCortPlot_2ndL
fileBaseName <- "proCortPlot_2ndL"
exportFullPPTSlide()
slideTitle <- "Effect of LBN on ALPS response in second litter proestrous mice"
ppt <- pptAddOneGraph()
```

#### ANOVAs

4-way ANOVA - LBN x ALPS x Cycle Stage x Time

```{r}
cort4wayANOVA
ppt <- addSlide_oneTable(
  ppt,
  "Females - 4way ANOVA of early-life trt x adult trt x time x stage",
  cort4wayANOVA,
  dontFormat = TRUE
)
```


There is a significant 4-way interaction, so do the 3-way interaction of 
LBN x ALPS x Time for each cycle stage. Correct for two comparisons

```{r}

cort3way_byCycle

ppt <- addSlide_oneTable(
  ppt,
  "LBN diestrous mice with respond differently to CON vs ALPS than than STD diestrous",
  cort3way_byCycle,
  dontFormat = TRUE
)
```

For diestrous mice, there is a 3-way interaction of LBN x ALPS x time

For proestrous mice, there is a 2-way interaction of ALPS x time


Follow-up the diestrous mice with a 2-way interaction between 
LBN x ALPS at each time. Adjust the p-values for two levels of time

```{r}
diCort2way_byTime
ppt <- addSlide_oneTable(
  ppt,
  "Early-life and adult trt interact to affect post-trt cort values in diestrous mice",
  diCort2way_byTime,
  dontFormat = TRUE
)
```


At the end of the paradigm, there is an interaction between LBN and ALPS for
the diestrous mice. This means that LBN changes the way that the mice
respond to the ALPS paradigm in diestrous mice.



For the diestrous mice at the end of the paradigm, group by adult treatment
and see if the early-life mice are significantly different.
Adjust for making two treatment comparisons

```{r}

diCortPost_byALPS

ppt <- addSlide_oneTable(
  ppt,
  "STD and LBN diestrous mice differ in cort after ALPS trt",
  diCortPost_byALPS,
  dontFormat = TRUE
)
```

For the proestrous mice, follow up the ALPS x time interaction.

Group by time, see if there is an effect of ALPS

```{r}
proCort_byTime
ppt <- addSlide_oneTable(
  ppt,
  "ALPS proestrous mice have higher post-trt cort than CON mice",
  diCortPost_byALPS,
  dontFormat = TRUE
)
```


# LH response to ALPS
```{r}
LHplot_pro_bothL

fileBaseName <- "proLHresponse_bothL"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on proestrous LH release"
ppt <- pptAddOneGraph()


LHplot_pro_bothL_zoom
fileBaseName <- "proLHresponse_bothL_zoom"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on proestrous LH release"
ppt <- pptUneditAddOneGraph()
```

## First litter
```{r}
LHplot_pro_1stL

fileBaseName <- "proLHresponse_1stL"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on proestrous LH release in first litters up to 2h before lights out"
ppt <- pptAddOneGraph()


LHplot_pro_1stL_zoom
fileBaseName <- "proLHresponse_1stL_zoom"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on proestrous LH release in first litters up to 2h before lights out"
ppt <- pptUneditAddOneGraph()
```
```{r}
LHamp_1stL_plot

fileBaseName <- "LHamp_1stL"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on max proestrous LH in first litters up to 2h before lights out"
ppt <- pptAddOneGraph()
```
```{r}
percSurgedPlot_1stL

fileBaseName <- "LHsurged_1stL"
exportFullPPTSlide()

slideTitle <- "Percent of first litter mice with a detectable LH surge up to 2h before lights out"
ppt <- pptAddOneGraph()
```


## Second litter
```{r}
LHplot_pro_2ndL

fileBaseName <- "proLHresponse_2ndL"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on proestrous LH release in second litters out to 1h after lights out"
ppt <- pptAddOneGraph()


LHplot_pro_2ndL_zoom
fileBaseName <- "proLHresponse_bothL_zoom"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on proestrous LH release in second litters out to 1h after lights out"
ppt <- pptUneditAddOneGraph()
```

```{r}
LHamp_2ndL_plot

fileBaseName <- "LHamp_2ndL"
exportFullPPTSlide()

slideTitle <- "Effect of LBN and ALPS on max proestrous LH in second litters out to 1h after lights out"
ppt <- pptAddOneGraph()
```
```{r}
percSurgedPlot_2ndL

fileBaseName <- "LHsurged_2ndL"
exportFullPPTSlide()

slideTitle <- "Percent of second litter mice with a detectable LH surge out to 1h after lights out"
ppt <- pptAddOneGraph()
```

# GABA PSCs

## Passives
```{r}
RinputPlot
fileBaseName <- "Rinput"
exportQuarterPPTSlide()


RseriesPlot
fileBaseName <- "Rseries"
exportQuarterPPTSlide()

newCap <- capacitancePlot +
  facet_wrap(
    ~earlyLifeTrt + adultTrt
    , ncol = 4
    , scales = "free_x"
    , strip.position = "bottom"
  ) +
  theme(
    axis.text.x = element_blank()
  )
fileBaseName <- "capacitance"
exportQuarterPPTSlide()

holdingCurrPlot
fileBaseName <- "holdingCurr"
exportQuarterPPTSlide()


slideTitle <- "Passive properties for GABA recordings"
ppt <- pptAddFourGraphs(
  RseriesPlot
  , RinputPlot
  # , capacitancePlot
  , newCap
  , holdingCurrPlot
)
```

