---
title: "R Notebook"
output: html_notebook
# fig-width: 11.5
# fig-height: 5
df-print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=11.5, fig.height=5) 
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
source("./01-scripts/04-filter-datasets.R")
source("./01-scripts/05-make-LBN-plots-manuscript.R")
source("./01-scripts/06-make-LBN-ANOVAs_noLitter.R")
```

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

# Column Sizes
```{r}
# JNeuro values (in cm)
twoCols <- 17.4
oneAndHalfCols <- 11.5
oneCol <- 8.5
```

# Figure 1 - Dams figDams

```{r}
# trying to fix font errors
# set_null_device("pdf")
```


```{r}
figDamsPlots <- align_plots(figDamsB, figDamsC, align = "v", axis = "l")

figDams <- plot_grid(
  NULL
  , figDamsPlots[[1]]
  , plot_grid(
    figDamsPlots[[2]]
    , figDamsD
    , ncol = 2
    , labels = c("C", "D")
    , align = "vh"
    , axis = "bt"
    , label_fontfamily = "Arial"
    , label_size = textSize
  )
  , nrow = 3
  , labels = c("A", "B", NULL)
  # , align = "hv"
  # , axis = "lb"
  , label_fontfamily = "Arial"
  , label_size = textSize
  , rel_heights = c(0.5, 1, 1)
)

figDams

flexSave(
  "figDams"
  , width = twoCols
  , heigh = 28/3*2
  , units = "cm"
)
```



# Offspring

## Body mass of offspring seems to follow three roughly linear patterns: P11-P21, P22-P35, P42-P72

```{r}
mass_plot_1stL
```

## Body mass of mass LBN pups seems most impacted by the paradigm

```{r}
mass_plot_1stL +
  coord_cartesian(x = c(11, 21), y = c(0, 16))
```

## Body mass of mass LBN pups seems most impacted by the paradigm

```{r}
lmm <- mass_long %>%
  filter(
    day >= 11 & day <= 21
  ) %>%
  mutate(
    day = day - 11
  ) %>%
  runLMM(
    mass ~ earlyLifeTrt * day * sex + (1|damID) + (1|mouseID)
  )

lmm$anova %>% formatLMM_ppt()
```

## Body mass of mass LBN pups seems most impacted by the paradigm


```{r}

lmm$coefs %>% formatLMM_ppt()

coefs <- lmm$coefs

mass11Intercept <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "(Intercept)"
    , valCol = "Estimate"
  )

mass11LBN <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN"
    , valCol = "Estimate"
  )

mass11Sex <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "sexM"
    , valCol = "Estimate"
  )

mass11PND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "day"
    , valCol = "Estimate"
  )

mass11LBNchangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:day"
    , valCol = "Estimate"
  )

mass11LBNchangeSex <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:sexM"
    , valCol = "Estimate"
  )

mass11SexChangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "day:sexM"
    , valCol = "Estimate"
  )

mass11SexLBNchangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:day:sexM"
    , valCol = "Estimate"
  )
```

## Body mass of mass LBN pups seems most impacted by the paradigm

- Predicted body mass on P11:
  - STD female: `r round(mass11Intercept, 1)`g. 
  - LBN female: `r round(mass11Intercept+mass11LBN, 1)`g. 
  - STD male: `r round(mass11Intercept+mass11Sex, 1)`g
  - LBN male: `r round(mass11Intercept+mass11LBN+mass11Sex+mass11LBNchangeSex, 1)`g
- Predicted change in body mass from P11 to P21:
  - STD female: `r round(mass11PND*10, 1)`g
  - LBN female: `r round((mass11PND+mass11LBNchangePND)*10, 1)`g
  - STD male: `r round((mass11PND+mass11SexChangePND)*10, 1)`g
  - LBN male: `r round((mass11PND+mass11SexChangePND+mass11SexLBNchangePND+mass11LBNchangePND)*10, 1)`g
  
## After weaning, female LBN pups are a little bit slower to gain body mass

```{r}
mass_plot_1stL +
  coord_cartesian(x = c(22, 35), y = c(0, 25))
```

## After weaning, female LBN pups are a little bit slower to gain body mass

```{r}
lmm <- mass_long %>%
  filter(
    day >= 22 & day <= 35
  ) %>%
  mutate(
    day = day - 22
  ) %>%
  runLMM(
    mass ~ earlyLifeTrt * day * sex + (1|damID) + (1|mouseID)
  )

lmm$anova %>% formatLMM_ppt()
```


## After weaning, female LBN pups are a little bit slower to gain body mass

```{r}

lmm$coefs %>% formatLMM_ppt()

coefs <- lmm$coefs

mass22Intercept <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "(Intercept)"
    , valCol = "Estimate"
  )

mass22LBN <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN"
    , valCol = "Estimate"
  )

mass22Sex <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "sexM"
    , valCol = "Estimate"
  )

mass22PND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "day"
    , valCol = "Estimate"
  )

mass22LBNchangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:day"
    , valCol = "Estimate"
  )

mass22LBNchangeSex <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:sexM"
    , valCol = "Estimate"
  )

mass22SexChangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "day:sexM"
    , valCol = "Estimate"
  )

mass22SexLBNchangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:day:sexM"
    , valCol = "Estimate"
  )
```

## After weaning, female LBN pups are a little bit slower to gain body mass

- Predicted body mass on P22:
  - STD female: `r round(mass22Intercept, 1)`g
  - LBN female: `r round(mass22Intercept+mass22LBN, 1)`g
  - STD male: `r round(mass22Intercept+mass22LBN+mass22Sex+mass22LBNchangeSex, 1)`g
  - LBN male: `r round(mass22Intercept+mass22LBN+mass22Sex+mass22LBNchangeSex, 1)`g
- Change in body mass from P22 to P35:
  - STD female: `r round(mass22PND*13, 1)`g
  - LBN female: `r round((mass22PND+mass22LBNchangePND)*13, 1)`g. 
  - STD male: `r round((mass22PND+mass22SexChangePND)*13, 1)`g
  - LBN male: `r round((mass22PND+mass22SexChangePND+mass22SexLBNchangePND+mass22LBNchangePND)*13, 1)`g
  
  
## From P42 to P72, LBN males may gain slighly less than STD males, but may be of low biological significance


```{r}
mass_plot_1stL +
  coord_cartesian(x = c(42, 72))
```

## From P42 to P72, LBN males may gain slighly less than STD males, but may be of low biological significance

```{r}
lmm <- mass_long %>%
  filter(
    day >= 42
  ) %>%
  mutate(
    day = day - 42
  ) %>%
  runLMM(
    mass ~ earlyLifeTrt * day * sex + (1|damID) + (1|mouseID)
  )

lmm$anova %>% formatLMM_ppt()

```

## From P42 to P72, LBN males may gain slighly less than STD males, but may be of low biological significance

```{r}

coefs <- lmm$coefs

coefs %>% formatLMM_ppt()

mass42Intercept <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "(Intercept)"
    , valCol = "Estimate"
  )

mass42LBN <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN"
    , valCol = "Estimate"
  )

mass42Sex <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "sexM"
    , valCol = "Estimate"
  )

mass42PND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "day"
    , valCol = "Estimate"
  )

mass42LBNchangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:day"
    , valCol = "Estimate"
  )

mass42LBNchangeSex <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:sexM"
    , valCol = "Estimate"
  )

mass42SexChangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "day:sexM"
    , valCol = "Estimate"
  )

mass42SexLBNchangePND <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:day:sexM"
    , valCol = "Estimate"
  )
```

## From P42 to P72, LBN males may gain slighly less than STD males, but may be of low biological significance

- Predicted body mass on P42:
  - STD female: `r round(mass42Intercept, 1)`g
  - LBN female: `r round(mass42Intercept+mass42LBN, 1)`g
  - STD male: `r round(mass42Intercept+mass42LBN+mass42Sex+mass42LBNchangeSex, 1)`g
  - LBN male: `r round(mass42Intercept+mass42LBN+mass42Sex+mass42LBNchangeSex, 1)`g
- Change in body mass per week from P42 to P72:
  - STD female: `r round(mass42PND*7, 1)`g
  - LBN female: `r round((mass42PND+mass42LBNchangePND)*7, 1)`g. 
  - STD male: `r round((mass42PND+mass42SexChangePND)*7, 1)`g
  - LBN male: `r round((mass42PND+mass42SexChangePND+mass42SexLBNchangePND+mass42LBNchangePND)*7, 1)`g
  
  
## Vaginal opening was not altered by LBN

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2

VO_age_plot
VO_mass_plot
```

## Vaginal opening was not altered by LBN

```{r}
lmm_age <- maturationFiltered %>%
  filter(
    sex == "F"
  ) %>%
  runLMM(
    VO_age ~ earlyLifeTrt + (1|damID)
  )

lmm_mass <- maturationFiltered %>%
  filter(
    sex == "F"
  ) %>%
  runLMM(
    VO_mass ~ earlyLifeTrt + (1|damID)
  )

# combine into one table
lmm_age$anova %>%
  mutate(
    effect = "VO age - earlyLifeTrt"
  ) %>%
  bind_rows(
    lmm_mass$anova %>%
      mutate(
        effect = "VO mass - earlyLifeTrt"
      )
  ) %>%
  rename(
    p = `Pr(>F)`
  )
```

## First estrus was not altered by LBN

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2

Estrus_age_plot
Estrus_mass_plot
```

## First estrus was not altered by LBN

```{r}
lmm_age <- maturationFiltered %>%
  filter(
    sex == "F"
  ) %>%
  runLMM(
    Estrus_age ~ earlyLifeTrt + (1|damID)
  )

lmm_mass <- maturationFiltered %>%
  filter(
    sex == "F"
  ) %>%
  runLMM(
    Estrus_mass ~ earlyLifeTrt + (1|damID)
  )

# combine into one table
lmm_age$anova %>%
  mutate(
    effect = "Estrus age - earlyLifeTrt"
  ) %>%
  bind_rows(
    lmm_mass$anova %>%
      mutate(
        effect = "Estrus mass - earlyLifeTrt"
      )
  ) %>%
  rename(
    p = `Pr(>F)`
  )
```

## Preputial separation was not altered by LBN

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2

PreputialSep_age_plot
PreputialSep_mass_plot
```

## Preputial separation was not altered by LBN

```{r}
lmm_age <- maturationFiltered %>%
  filter(
    sex == "M"
  ) %>%
  runLMM(
    PreputialSep_age ~ earlyLifeTrt + (1|damID)
  )

lmm_mass <- maturationFiltered %>%
  filter(
    sex == "M"
  ) %>%
  runLMM(
    PreputialSep_mass ~ earlyLifeTrt + (1|damID)
  )

# combine into one table
lmm_age$anova %>%
  mutate(
    effect = "Preputial separation age - earlyLifeTrt"
  ) %>%
  bind_rows(
    lmm_mass$anova %>%
      mutate(
        effect = "Preputial separation mass - earlyLifeTrt"
      )
  ) %>%
  rename(
    p = `Pr(>F)`
  )
```

# Estrous cycles - creating functions to analyze cycles

## Characterizing estrous cycles

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2
repCycles_STD_1stL
repCycles_LBN_1stL
```

## Characterizing estrous cycles

:::: {.columns}

::: {.column width="50%"}

```{r fig.height=5, fig.width=5.67}
repCycles_STD_1stL +
  geom_point(aes(color = isStartCycle, alpha = isStartCycle))+
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red", "STD" = "grey30", "LBN" = "cyan4"))+
  scale_alpha_manual(values = c("FALSE" = .1, "TRUE" = 1))
```

:::

::: {.column width="50%"}

::: {.incremental}

- Cycle start day: An estrous day that is preceded by either a proestrous or diestrous day
- Cycle length: # days between two cycle start days
- Track
  - Day of first cycle start
  - Day of last cycle start
  - Days that are "outside" of a cycle (before first cycle start or after last)

:::

:::

::::

## LBN does not alter estrous cycles

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2

cyclesFiltered %>%
  scatterPlotLBN(
    yVar = numCycles
    , yLab = "# of cycles from P70-P90"
    , dotSize = 3
    , textSize = 16
  )

cyclesFiltered %>%
  scatterPlotLBN(
    yVar = cycleLength
    , yLab = "cycle length (days)"
    , dotSize = 3
    , textSize = 16
  )

```

## LBN does not alter estrous cycles

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2


cyclesFiltered %>%
  scatterPlotLBN(
    yVar = firstCycleDay
    , yLab = "first cycle day"
    , dotSize = 3
    , textSize = 16
  )

cyclesFiltered %>%
  scatterPlotLBN(
    yVar = percDaysInCycles
    , yLab = "% days in a cycle"
    , dotSize = 3
    , textSize = 16
  )
```

```{r}
lmm_numCycles <- cyclesFiltered %>%
  runLMM(
    numCycles ~ earlyLifeTrt + (1|damID)
  )
lmm_cycleLength <- cyclesFiltered %>%
  runLMM(
    cycleLength ~ earlyLifeTrt + (1|damID)
  )
lmm_firstCycleDay <- cyclesFiltered %>%
  runLMM(
    firstCycleDay ~ earlyLifeTrt + (1|damID)
  )
lmm_percDaysInCycles <- cyclesFiltered %>%
  runLMM(
    percDaysInCycles ~ earlyLifeTrt + (1|damID)
  )

lmm_numCycles$anova %>%
  mutate(
    effect = "# cycles - earlyLifeTrt"
  ) %>%
  bind_rows(
    lmm_cycleLength$anova %>%
      mutate(
        effect = "cycle length - earlyLifeTrt"
      )
  ) %>%
  bind_rows(
    lmm_firstCycleDay$anova %>%
      mutate(
        effect = "first cycle day - earlyLifeTrt"
      )
  ) %>%
  bind_rows(
    lmm_percDaysInCycles$anova %>%
      mutate(
        effect = "% days in cycles - earlyLifeTrt"
      )
  ) %>%
  rename(
    p = `Pr(>F)`
  )
```

## LBN does not alter the percent of days in estrous cycle stages

```{r}
percDaysStage_1stL
```

# Response to ALPS

## LBN does not affect corticosterone response in males

```{r}
maleCortPlot_1stL
```

## LBN led to increased post-ALPS serum corticosterone in proestrous females

```{r}
proCortPlot_no723 <- cortFilteredPro %>%
  filter(
    mouseID != 723
  ) %>%
  plotCort_bothL()
proCortPlot_no723
```

## The effect of LBN on ALPS is influenced by sex

```{r}
#| tbl-colwidths: [45, 11, 11, 11, 11, 11]
lmm <- cortFiltered_M_DiPro %>%
  filter(
    mouseID != 723
  ) %>%
  runLMM(
    cort ~ sex * earlyLifeTrt * adultTrt * time + (1|mouseID)
  )

lmm$coefs %>% formatLMM_ppt()

coefs <- lmm$coefs

cortIntercept <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "(Intercept)"
    , valCol = "Estimate"
  )

cortTime <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "time"
    , valCol = "Estimate"
  )

cortTime5h <- cortTime * 5

cortALPSTime <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "adultTrtALPS:time"
    , valCol = "Estimate"
  )

femaleSTDALPS5h <- cortTime5h + cortALPSTime * 5

cortMaleALPSTime <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "sexM:adultTrtALPS:time"
    , valCol = "Estimate"
  )

# not a significant contributor to the model
maleSTDALPS5h <- femaleSTDALPS5h + cortMaleALPSTime * 5

cortLBNALPStime <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "earlyLifeTrtLBN:adultTrtALPS:time"
    , valCol = "Estimate"
  )

femaleLBNALPS5h <- femaleSTDALPS5h + cortLBNALPStime * 5

cortMaleLBNALPSTime <- coefs %>%
  getValWhereOtherValTrue(
    matchCol = "effect"
    , matchVal = "sexM:earlyLifeTrtLBN:adultTrtALPS:time"
    , valCol = "Estimate"
  )
maleLBNALPS5h <- femaleLBNALPS5h + cortMaleLBNALPSTime *5
```

## The effect of LBN on ALPS is influenced by sex

- The estimated serum corticosterone level at the beginning of the paradigm is `r cortIntercept`ng/mL, and is not altered by sex or early-life treatment
- For adult CON animals
  - cort is expected to increase about `r cortTime5h`ng/mL at the end of the paradigm
  - this is not altered by sex or early-life treatment
- For adult ALPS animals, the expected cort rise for each group is:
  - pro STD-ALPS: `r femaleSTDALPS5h`
  - pro LBN-ALPS: `r femaleLBNALPS5h`
  - male STD-ALPS: `r maleSTDALPS5h` - note that this is not different than pro STD-ALPS
  - male LBN-ALPS: `r maleLBNALPS5h`

# GABA PSCs

## LBN and ALPS do not affect the frequency or amplitude of GABA PSCs

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2
GABAfreqPlot
GABAampPlot
```

## LBN and ALPS do not affect passive properties or recording quality

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2


RinputPlot

RseriesPlot

```

## LBN and ALPS do not affect passive properties or recording quality

```{r fig.height=5, fig.width=5.67}
#| layout-ncol: 2


capacitancePlot


holdingCurrPlot
```
