---
title: "NGP Seminar Data"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
```

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

```{r}
litterNum_label <- c(
  "1" = "first litter",
  "2" = "second litter"
)

facetForLitterNum <- facet_grid(
    cols = vars(litterNum),
    labeller = labeller(
      litterNum = litterNum_label
    )
  )

figureNum <- 1

pptBaseName <- function(figNum) {
  baseName = paste0("ICN_fig", figNum, "_")
  return(baseName)
}

subFolder <- "NGP_retreat"

imgType <- "png"
```

# ALPS response
## First and Second litters


```{r}
Cort_off_filtered <- Cort_off %>%
  filter(
    cohort == 2 | cohort == 4 | cohort == 6 | cohort == 7 | cohort == 8,
    Litter_size >= 5,
    !is.na(cort),
    !exclude
  ) %>%
  mutate(
    adjMax = ifelse(cort >= 500, TRUE, FALSE),
    adjMin = ifelse(cort <= 1.95, TRUE, FALSE),
    cort = ifelse(cort >= 500, 500, ifelse(cort <= 1.95, 1.95, cort))
  )
thisSex <- "F"

cortByCycle <- Cort_off_filtered %>%
  filter(
    sex == thisSex,
    (Sac_cycle == "proestrus" & ReproTract_mass >= 125) | (Sac_cycle == "diestrus" & ReproTract_mass <= 100),
    mouseID != 653
  )

```


4-way ANOVA - LBN x ALPS x Cycle Stage x Time

```{r}

cortByCycle %>%
  cortAnova(
    byCycle = TRUE
  )

```


There is a significant 4-way interaction, so do the 3-way interaction of 
LBN x ALPS x Time for each cycle stage. Correct for two comparisons

```{r}

cortByCycle %>%
  group_by(
    Sac_cycle
  ) %>%
  anova_test(
    dv = cort,
    wid = mouseID,
    between = c(earlyLifeTrt, adultTrt),
    within = time
  ) %>%
  # adjust_pvalue() %>%
  get_anova_table() %>%
  as_tibble() %>%
  mutate(
    p.adj = p * 2 # doing two cycle stage comparisons
  ) %>%
  # adjust_pvalue(method = "bonferroni") %>%
  formatAdjAnova()
  
```

For diestrous mice, there is a 3-way interaction of LBN x ALPS x time

For proestrous mice, there is a 2-way interaction of ALPS x time


Follow-up the diestrous mice with a 2-way interaction between 
LBN x ALPS at each time. Adjust the p-values for two levels of time

```{r}
cortByCycle %>%
  filter(
    Sac_cycle == "diestrus"
  ) %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = cort,
    wid = mouseID,
    between = c(earlyLifeTrt, adultTrt)
  ) %>%
  # adjust_pvalue() %>%
  # adjust_pvalue(method = "bonferroni") %>%
  get_anova_table() %>%
  as_tibble() %>%
  mutate(
    p.adj = p * 2 # doing two time comparisons
  ) %>%
  formatAdjAnova()
```


At the end of the paradigm, there is an interaction between LBN and ALPS for
the diestrous mice. This means that LBN changes the way that the mice
respond to the ALPS paradigm in diestrous mice.



For the diestrous mice at the end of the paradigm, group by adult treatment
and see if the early-life mice are significantly different.
Adjust for making two treatment comparisons

```{r}

cortByCycle %>%
  filter(
    Sac_cycle == "diestrus",
    time == 5
  ) %>%
  group_by(
    adultTrt
  ) %>%
  anova_test(
    dv = cort,
    wid = mouseID,
    between = c(earlyLifeTrt)
  ) %>%
  # adjust_pvalue() %>%
  adjust_pvalue(method = "bonferroni") %>%
  formatAdjAnova()
```

For the proestrous mice, follow up the ALPS x time interaction.

Group by time, see if there is an effect of ALPS

```{r}
cortByCycle %>%
  filter(
    Sac_cycle == "proestrus"
  ) %>%
  group_by(
    time
  ) %>%
  anova_test(
    dv = cort,
    wid = mouseID,
    between = c(adultTrt)
  ) %>%
  # adjust_pvalue() %>%
  adjust_pvalue(method = "bonferroni") %>%
  formatAdjAnova()
```

### proestrus 

```{r}
Cort_off_bySex <- Cort_off_filtered %>%
  filter(
    sex == thisSex,
    Sac_cycle == "proestrus" & ReproTract_mass >= 125,
    mouseID != 653
  )

basePlot <- Cort_off_bySex %>%
  baseCortPlot(
    dotSize = 2
  )

plot <- basePlot %>%
  longCortPlot(
    fontSize = 16
    , zoom_y = TRUE
    , ymin = 0
    , ymax = 550
    , zoom_x = TRUE
    , xmin = -2
    , xmax = 7
  ) +
  ylab("corticosterone (ng/mL)") + 
  scale_y_continuous(
    breaks = c(0, 100, 200, 300, 400, 500)
  )
  
plot

fileBaseName = "femalesCort_pro"
thisWidth = 5.5
thisHeight = 5
thisUnits = "in"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

### Diestrus 

```{r}
Cort_off_bySex <- Cort_off_filtered %>%
  filter(
    sex == thisSex,
    Sac_cycle == "diestrus" & ReproTract_mass <= 100,
    mouseID != 653
  )

Cort_off_bySex

basePlot <- Cort_off_bySex %>%
  baseCortPlot(
    dotSize = 2
  )

plot <- basePlot %>%
  longCortPlot(
    fontSize = 16
    , zoom_y = TRUE
    , ymin = 0
    , ymax = 550
    , zoom_x = TRUE
    , xmin = -2
    , xmax = 7
  )+
  ylab("corticosterone (ng/mL)")+ 
  scale_y_continuous(
    breaks = c(0, 100, 200, 300, 400, 500)
  )
plot

fileBaseName = "femalesCort_di"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
# 1 -> 2
figureNum = 1
figureNum <- figureNum + 1
```


# LH

## Second litter

```{r}
LH_filtered <- LH_off %>%
  filter(
    Litter_size >= 5,
    litterNum == 2,
    Sac_cycle == "proestrus" & ReproTract_mass >= 125
  )

tempLHPlot <- function(
  df,
  ymax = 40
){
  df %>%
    LHPlot(
    fontSize = 16,
    dotSize = 2,
    zoom_y = TRUE,
    ymin = 0,
    ymax = ymax
  ) +
  theme(
    legend.position = "none"
  ) +
  facet_wrap(~comboTrt, scales = "free")
}

plot <- LH_filtered %>%
  mutate(
    comboTrt = factor(comboTrt, levels = c("STD-CON", "LBN-CON", "STD-ALPS", "LBN-ALPS"))
  ) %>%
  tempLHPlot()

plot 

thisWidth = 7
thisHeight = 5

fileBaseName = "LH_combined_second"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```
```{r}
surgedDF <- AcuteStress_off %>%
  mutate(
    surged = maxLH > 3
  ) %>%
  filter(
    Sac_cycle == "proestrus",
    ReproTract_mass >= 125,
    Litter_size >= 5,
    litterNum == 2
    , cohort == 4 | cohort == 6
  ) 
surgedDF
```

```{r}
# 2 -> 3
figureNum <- figureNum + 1
```

```{r}
plot <- surgedDF %>%
  plotLHAmp_comboTrt(
    3,
    textSize = 16,
    dotSize = 2,
    angleX = FALSE
  )+ 
  coord_cartesian(ylim = c(0, 40))

plot 
thisHeight = 5
thisWidth = 5.5

fileBaseName = "LH_amplitude_second"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```

```{r}
plot <- surgedDF %>%
  plotLHTime_comboTrt(
    3,
    textSize = 16,
    dotSize = 2,
    angleX = FALSE
  )

plot 
thisHeight = 5
thisWidth = 5.5

fileBaseName = "LH_time_second"

flexSave(
  baseName = fileBaseName,
  thisFilePrefix = pptBaseName(figureNum),
  plot = plot,
  fileType = imgType,
  filePath = file.path(plotOutputFolder, subFolder),
  width = thisWidth,
  height = thisHeight,
  units = thisUnits,
  compType = currentCompType,
  shinySettings = FALSE
)
```




<!-- ```{r} -->
<!-- # 3 -> 4 -->
<!-- figureNum <- figureNum + 1 -->
<!-- ``` -->


<!-- ```{r} -->
<!-- # 4 -> 5 -->
<!-- figureNum <- figureNum + 1 -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # 5 -> 6 -->
<!-- figureNum <- figureNum + 1 -->
<!-- ``` -->


<!-- ```{r} -->
<!-- # 6 -> 7 -->
<!-- figureNum <- figureNum + 1 -->
<!-- ``` -->

