---
title: "R Notebook"
output: html_notebook
# fig-width: 11.5
# fig-height: 5
df-print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# knitr::opts_chunk$set(fig.width=11.5, fig.height=5) 
# options(digits=3)
```

```{r include=FALSE}
source("./01-scripts/01-set-up.R")
source(file.path(scriptsFolder, "02-get-datasets.R"))
source("./01-scripts/04-filter-datasets.R")
source("./01-scripts/06-run-LBN-stats.R")
source("./01-scripts/05-make-LBN-plots-modelError-manuscript.R")
source("./01-scripts/06-make-LBN-tables.R")
```

```{r eval=FALSE, include=FALSE}
source("./01-scripts/05.5-run-GABA-dist-analysis.R")
```


# Documents 

```{r}
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
set_flextable_defaults(
  font.family = "Arial"
  , font.size = 11
)

doc <- read_docx("./manuscriptTemplate.docx")
supDoc <- read_docx("./manuscriptTemplate.docx")
pairsDoc <- read_docx("./manuscriptTemplate.docx")

saveTables <- function(){
  print(doc, target = "my_report.docx")
  print(supDoc, target = "supplementalTable.docx")
  print(pairsDoc, target = "pairsTable.docx")
}
```

## Pairs table

```{r}
source("./01-scripts/06-make-LBN-table-pairs.R")
tableCaption <- "Pairs table"
tbl <- pairsFlextable
tbl
```

```{r}
pairsDoc <- addTableAndCaptionToDoc(tbl, tableCaption, 2, pairsDoc)
```


# Column Sizes
```{r}
# # JNeuro values (in cm)
# twoCols <- 17.4
# oneAndHalfCols <- 11.5
# oneCol <- 8.5

# eNeuro values (in cm)
twoCols <- 17.6
oneAndHalfCols <- 11.6
oneCol <- 8.5

quarterLength <- 16.7/4
thirdLength <- 16.7/3
halfLength <- 16.7/2
twoThirdsLength <- 16.7*2/3
threeQuarterLength <- 16.7*3/4
fullLength <- 16.7

manuscriptFolder <- file.path(plotOutputFolder, "manuscript")
```

# Comparison of cort from control and nutella mice
```{r}
source(file.path(scriptsFolder, "cortAdmin-get-datasets.R"))

cortPro_Nutella <- cortFilteredPro %>%
  filter(
    adultTrt == "CON"
    , earlyLifeTrt == "STD"
    , time == 5
  ) %>%
  mutate(
    trt = "CON"
  ) %>%
  bind_rows(
    cortAdminCortDF %>%
      filter(
        dosage == 0
        , time == 5
      ) %>%
      mutate(
        trt = "Nutella"
      )
  )

cortPro_Nutella %>%
  group_by(
    trt
  ) %>%
  meanSummary(cort)

cortPro_Nutella %>%
  t_test(
    cort ~ trt
  )
```

# Figure 1 - Dams figDams

```{r}
# trying to fix font errors
# this seems to work for not putting the axis label on top of the tick labels
# but the axes don't actually align with align_plots
# update - Maybe works???? IDK WHAT I DID!
set_null_device("png") 

# # this works for aligning the axes with align_plots
# # but then faceted plot yaxis label overlaps
# set_null_device("pdf")
# 
# # this works for aligning the axes with align_plots
# # but then faceted plot yaxis label overlaps
# set_null_device("cairo_pdf")
```


```{r}
figDamsPlots <- cowplot::align_plots(
  figDams_exits
  , figDams_offNest
  , align = "v"
  , axis = "l"
)

figDamsBehaviorPlots <- cowplot::align_plots(figDamsPlots[[1]], figDams_meanExits, figDamsPlots[[2]], figDams_meanOffNest, align = "h", axis = "bt")

figDamsRightPlots <- cowplot::align_plots(
  figDamsBehaviorPlots[[2]]
  , figDamsBehaviorPlots[[4]]
  , figDamsD
  , align = "v"
  , axis = "lr"
)

figDams_row1 <- align_plots(
  figDamsRightPlots[[3]]
  , figDams_mass
  , align = "h"
  , axis = "tb"
)

figDams_left <- plot_grid(
  plot_grid(
    NULL
    , figDams_row1[[2]]
    , nrow = 1
    , align = "h"
    , axis = "bt"
    , labels = c("A", "B")
    , label_fontfamily = "Arial"
    , label_size = textSize
  )
  , figDamsBehaviorPlots[[1]]
  , figDamsBehaviorPlots[[3]]
  , nrow = 3
  , labels = c("", "D", "E")
  , label_fontfamily = "Arial"
  , label_size = textSize
)

figDams_right <- plot_grid(
  figDams_row1[[1]]
  , figDamsRightPlots[[1]]
  , figDamsRightPlots[[2]]
  , labels = c("C", "", "")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , nrow = 3
)

figDams <- plot_grid(
  figDams_left
  , figDams_right
  , ncol = 2
  , rel_widths = c(3, 1)
)
  
figDams
```

```{r}
flexSave(
  "figDams_allRainbow"
  , plot = figDams
  , width = twoCols
  , height = fullLength - 0.1
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Table - counts of dams

```{r}
damCountTblNum <- 1
tableNum <- "1-1"
```


```{r}
tableCaption <- "Number of dams in each treatment group for studies reported in Figure 1. Dam behavior includes values for number of nest exits per hour and percent of time spent off the nest."

tbl <- dam_count_flexTable
tbl
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Table - dam mass

```{r}
testFormula <- getLMMFormula(damMass_lmm)
testFormula <- gsub("PND", "PND@", testFormula)
# tableCaption <- paste0("Linear mixed model of the dam mass on PND4, 11, and 21 fit with the equation ", testFormula, ". PND was treated as a factor variable. PND = postnatal day")

tableCaption <- "dam mass and dam behavior"

tbl <- damTable_earlyLifePND_flexTable

tbl
```

```{r}
damMassTblNum <- "1-2"
tableNum <- damMassTblNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Table - dam cort

```{r}
tableCaption <- "Two-sided t-test of the effect of limited bedding and nesting (LBN) on serum corticosterone in dams on postnatal day 11. CI = confidence interval"

tbl <- damCort_flexTable
tbl
```


# Figure 2 - Offspring maturation figOff

## grouped maturation
```{r}
figOffLeftPlots <- cowplot::align_plots(
  figOffA_indiv
  , figOffAge_model
  , figOffMass_model
  , figOffA_group
  , align = "v", axis = "l"
)

figOffRightPlots <- cowplot::align_plots(
  figOff_femaleAGD
  , figOff_maleAGD
  , align = "vh", axis = "ltrb"
)

figOffMat <- plot_grid(
  plot_grid(
      figOffLeftPlots[[2]]
      , figOffRightPlots[[1]]
      , ncol = 2
      , rel_widths = c(3, 1)
      , labels = c("B", "D")
      , label_fontfamily = "Arial"
      , label_size = textSize
  )
  , plot_grid(
      figOffLeftPlots[[3]]
      , figOffRightPlots[[2]]
      , ncol = 2
      , rel_widths = c(3, 1)
      , labels = c("C", "")
      , label_fontfamily = "Arial"
      , label_size = textSize
  )
  , nrow = 2
)

figOff <- plot_grid(
  figOffLeftPlots[[4]]
  , figOffMat
  , nrow = 2
  , labels = c("A", NULL)
  , label_fontfamily = "Arial"
  , label_size = textSize
  , rel_heights = c(1.5, 2)
)
figOff
```

```{r}
flexSave(
  "figOff"
  , plot = figOff
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

```{r}
flexSave(
  "figOffIndiv"
  , plot = figOffA_indiv
  , width = oneCol*.9
  , height = fullLength/3/1.3
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Table - offspring counts

```{r}
tbl <- massCount_flexTable
tbl
```


## Table - offspring mass

```{r}
tbl <- massLMM_flexTable
tbl
```


```{r}
offMassTblNum <- "2-1"
tableNum <- offMassTblNum
```

```{r}
testFormula <- deparse(female_mass_lmm$call$formula)
testFormula <- gsub("lspline\\(day, c\\(21, 35\\)\\)", "PND@", testFormula)
testFormula <- paste(testFormula, collapse = " ")
testFormula <- gsub("\\s+", " ", testFormula)
tableCaption <- paste0("Linear mixed model of the offspring mass from PND11-72 fit with the equation ", testFormula, ". PND@: Linear splines at PND21 and 35 allow the model to change the slope of the line for the segments between PND11-21, from 21-35, and from 35-72. Male and female offspring were fit with separate models. PND = postnatal day")
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


## Table - count maturation
```{r}
tbl <- matCount_flexTable
tbl
```


## Table - VO, estrus, PPS

```{r}
tbl <- matMass_lmm_flexTable
tbl
```


```{r}
testFormula <- deparse(VO_age_lmm$call$formula)
testFormula <- gsub("VO_age", "maturation feature", testFormula)
tableCaption <- paste0("Linear mixed models for maturation with the equation ", testFormula, ". Models were fit for age and for mass at vaginal opening, first estrus, and preputial separation.")
```

```{r}
offMatTblNum <- "2-2"
tableNum <- offMatTblNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Table - AGD

```{r}
tbl <- AGD_flexTable

tbl
```

```{r}
testFormula <- deparse(AGD_lmm$call$formula)
testFormula <- gsub("AGD_adult", "AGD", testFormula)
tableCaption <- paste0("Linear mixed models for anogenital distance (AGD) with the equation ", testFormula, ".")
```

```{r}
AGDTblNum <- "2-3"
tableNum <- AGDTblNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 3 - Cycles

```{r}
figCyclesLeftPlots <- cowplot::align_plots(
  figCyclesA
  , figCycles_numCycles_model
  , align = "v", axis = "l"
)

figCycles2ndRow <- plot_grid(
  figCyclesLeftPlots[[2]]
  , figCycles_lengthLog_model
  , figCyclesD
  , ncol = 3
  , labels = c("B", "C", "D")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , align = "h"
  , axis = "bt"
  , rel_widths = c(1, 1, 2)
)

figCycles <- plot_grid(
  NULL
  , figCyclesLeftPlots[[1]]
  , figCycles2ndRow
  , nrow = 3
  , rel_heights = c(0.3, 2.2, 3)
  , labels = c("A", NULL, NULL)
  , label_fontfamily = "Arial"
  , label_size = textSize
)
figCycles
```

```{r}
flexSave(
  "figCycles"
  , plot = figCycles
  , width = twoCols
  , height = 9.5
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Cycles count

The reason that there are 74 STD females for masses and only 73 for cycles is that mouse 731 was the only female in the litter, and she was sacrificed at P72 after taking final mass sample. 

LBN drops from 74 to 73 because mouse 977 had hydrocephaly and was sacrificed PND24

```{r}
## No table, incorporate into text
cyclesFiltered %>%
  filter(
    !is.na(numCycles)
  ) %>%
  group_by(
    earlyLifeTrt
  ) %>%
  summarize(
    mice = n()
    , litters = n_distinct(damID)
    , .groups = "drop"
  )
```


## Table - Cycles length

```{r}
tbl <- cycles_flexTable
tbl
```

```{r}
cyclesNumFormula <- getLMMFormula(numCycles_lmm)
cyclesNumFormula <- gsub("numCycles", "# of cycles", cyclesNumFormula)

lengthCyclesFormula <- getLMMFormula(lengthCycles_log_lmm)
lengthCyclesFormula <- gsub("cycleLength", "cycle length", lengthCyclesFormula)

cycles_ChiSq_n <- cycles_ChiSq$n[1]

tableCaption <- paste0("Statistics for estrous cycles from postnatal days 70-90. The number of cycles was fit with the linear mixed model equation `", cyclesNumFormula, "`. The log of the mean cycle length in days was fit with equation `", lengthCyclesFormula, "`. The number of days spent in each cycle stage was assessed with a Chi-squared test (n = ", cycles_ChiSq_n, ").")
```


```{r}
cyclesTblNum <- "3-1"
tableNum <- cyclesTblNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 4 - Corticosterone

```{r}
figCort_byAdult <- plot_grid(
  figCortA_adult +
    theme(
      plot.margin = unit(c(0.3,0.1,0,0.1), "cm")
    )
  , figCort_females_adult
  , nrow = 1
  , rel_widths = c(1, 2)
  , align = "vh", axis = "ltrb"
  , labels = c("A", "B")
  , label_fontfamily = "Arial"
  , label_size = textSize
)

figCort_byAdult
```

```{r}
flexSave(
  "figCort"
  , plot = figCort_byAdult
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

```{r}
cortFilteredFemales %>%
  filter(
    cort > 450
  )
```


## count

```{r}
tbl <- cortCount_flexTable
tbl
```

```{r}
tableCaption <- "Number of litters and mice with serum corticosterone measurements before and after adult treatment. Abbreviations: STD, standard-reared; LBN, limited bedding and nesting; CON, adult control; ALPS, acute, layered, psychosocial stress in adulthood."
```

```{r}
cortCountNum <- "4-1"
tableNum <- cortCountNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## cort lmm 

```{r}
tbl <- cort_flexTable
tbl
```

```{r}
maleFormula <- getLMMFormula(male_cort_lmm)
maleFormula1 <- paste0(maleFormula[1], gsub("    \\(", "\\(", maleFormula[2]))

femaleFormula <- getLMMFormula(female_cort_lmm)
femaleFormula1 <- paste0(femaleFormula[1], gsub("    ", "", femaleFormula[2]))

maleFormula1
femaleFormula1

tableCaption <- paste0("Statistics for serum corticosterone in male and female offspring. Data from males were fit with the linear mixed model equation `", maleFormula1, "`. Data from females were fit with the linear mixed model equation `", femaleFormula1, "`.")
tableCaption
```

```{r}
cortLMMNum <- "4-2"
tableNum <- cortLMMNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 4-1 - Male masses - ALPS

4-by-2 layout, PM
```{r}
figMaleMassALPS <- plot_grid(
  plot_grid(
    maleBodyMassAM_ALPS_plot
    , maleAdrenalMass_ALPS_plot
    , maleSeminalVesicleMass_ALPS_plot
    , maleTestesMass_ALPS_plot
    , ncol = 1
    , align = "v"
    , axis = "lr"
    , labels = c("A", "C", "E", "G")
    , label_fontfamily = "Arial"
    , label_size = textSize
  ), 
  plot_grid(
    malePercChangeBodyMass_ALPS_plot
    , maleRelAdrenalMassPM_ALPS_plot
    , maleRelSeminalVesicleMassPM_ALPS_plot
    , maleRelTestesMassPM_ALPS_plot
    , ncol = 1
    , align = "v"
    , axis = "lr"
    , labels = c("B", "D", "F", "H")
    , label_fontfamily = "Arial"
    , label_size = textSize
  )
  , ncol = 2
  , rel_widths = c(1, 1)
)
figMaleMassALPS
```


```{r}
flexSave(
  "figMaleMassALPS"
  , plot = figMaleMassALPS
  , width = twoCols
  , height = 18
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Count

```{r}
tbl <- maleMass_ALPSAM_counts_flexTable
tbl
tbl <- maleMass_ALPSPM_counts_flexTable
tbl
```

```{r}
tableCaption <- "Number of litters and male mice with mass measurements on the day of adult treatment. Abbreviations: STD, standard-reared; LBN, limited bedding and nesting; CON, adult control; ALPS, acute, layered, psychosocial stress in adulthood."
```

```{r}
maleMass_ALPS_countsNum <- "4-3"
tableNum <- maleMass_ALPS_countsNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```


## lmm

```{r}
tbl <- maleALPS_RelPM_flexTable
tbl
```


```{r}
tableCaption <- "Statistics from linear mixed models of male masses on day of adult treatment. Data were fit with the formula `feature ~ early-life treatment * adult treatment + (1 | dam)`."
```

```{r}
maleMass_ALPS_lmm_num <- "4-4"
tableNum <- maleMass_ALPS_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 4-2 - Female masses

```{r}
figFemalesMasses_plots <- align_plots(
    femaleBodyMassAM_ALPS_plot + rremove("legend") 
    , femalePercChangeBodyMass_ALPS_plot
    , femaleAdrenalMass_ALPS_plot
    , femaleUterineMass_ALPS_plot
    , femaleRelAdrenalMassPM_ALPS_plot
    , femaleRelUterineMassPM_ALPS_plot
    , align = "hv"
    , axis = "lrtb"
)

figFemalesMasses_plots_left <- align_plots(
    femaleBodyMassAM_ALPS_plot + rremove("legend") 
    , femaleAdrenalMass_ALPS_plot
    , femaleUterineMass_ALPS_plot
    , align = "hv"
    , axis = "lrtb"
)

figFemalesMasses_plots_right <- align_plots(
    femalePercChangeBodyMass_ALPS_plot
    , femaleRelAdrenalMassPM_ALPS_plot
    , femaleRelUterineMassPM_ALPS_plot
    , align = "hv"
    , axis = "lrtb"
)

figFemalesMasses <- plot_grid(
  # get_legend(femaleBodyMassAM_ALPS_plot)
  plot_grid(
    figFemalesMasses_plots_left[[1]]
    , figFemalesMasses_plots_right[[1]]
    , ncol = 2
    , labels = c("A", "B")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , rel_widths = c(0.95, 1)
  )
  , plot_grid(
    figFemalesMasses_plots_left[[2]]
    , figFemalesMasses_plots_right[[2]]
    , ncol = 2
    , labels = c("C", "D")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , rel_widths = c(0.95, 1)
  )
  , plot_grid(
    figFemalesMasses_plots_left[[3]]
    , figFemalesMasses_plots_right[[3]]
    , ncol = 2
    , labels = c("E", "F")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , rel_widths = c(0.95, 1)
  )
  , nrow = 3
  , rel_heights = c(1, 1, 1)
  # , nrow = 4
  # , rel_heights = c(0.1, 1, 1, 1)
)
figFemalesMasses
```

```{r}
flexSave(
  "figFemalesMasses"
  , plot = figFemalesMasses
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Count

```{r}
tbl <- femaleMass_ALPSPM_counts_flexTable
tbl
```


```{r}
tableCaption <- "Number of litters and female mice with mass measurements on the day of adult treatment. Abbreviations: STD, standard-reared; LBN, limited bedding and nesting; CON, adult control; ALPS, acute, layered, psychosocial stress in adulthood."
```

```{r}
femaleMass_ALPS_countsNum <- "4-5"
tableNum <- femaleMass_ALPS_countsNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## LMM

```{r}
tbl <- femaleALPS_RelPM_flexTable
tbl
```

```{r}
tableCaption <- "Statistics from linear mixed models of female masses on day of adult treatment. Data were fit with the formula `feature ~ early-life treatment * adult treatment * cycle stage + (1 | dam)`."
```

```{r}
femaleMass_ALPS_lmm_num <- "4-6"
tableNum <- femaleMass_ALPS_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 4-3 - Male cort administration

```{r}
figMaleCortAdmin_left <- align_plots(
  maleAdrenalMass_dosage_plot
  , maleRelAdrenalMassPM_dosage_plot
  , align = "v"
  , axis = "l"
)
figMaleCortAdmin_middle <- align_plots(
  maleSeminalVesicleMass_dosage_plot
  , maleRelSeminalVesicleMassPM_dosage_plot
  , align = "v"
  , axis = "l"
)
figMaleCortAdmin_right <- align_plots(
  maleTestesMass_dosage_plot
  , maleRelTestesMassPM_dosage_plot
  , align = "v"
  , axis = "l"
)

figMaleCortAdmin_row1 <- plot_grid(
  maleBodyMassAM_dosage_plot
  , cortAdmin_cort
  , malePercChangeBodyMass_dosage_plot
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("A", "B", "C")
  , rel_widths = c(1, 2, 1)
  , label_fontfamily = "Arial"
  , label_size = textSize
)
figMaleCortAdmin_row2 <- plot_grid(
  figMaleCortAdmin_left[[1]]
  , figMaleCortAdmin_middle[[1]]
  , figMaleCortAdmin_right[[1]]
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("D", "F", "H")
  , label_fontfamily = "Arial"
  , label_size = textSize
)
figMaleCortAdmin_row3 <- plot_grid(
  figMaleCortAdmin_left[[2]]
  , figMaleCortAdmin_middle[[2]]
  , figMaleCortAdmin_right[[2]]
  , nrow = 1
  , align = "h"
  , axis = "tb"
  , labels = c("E", "G", "I")
  , label_fontfamily = "Arial"
  , label_size = textSize
)

figMaleCortAdmin <- plot_grid(
  figMaleCortAdmin_row1
  , figMaleCortAdmin_row2
  , figMaleCortAdmin_row3
  , nrow = 3
  , rel_heights = c(1, 1, 1)
)

figMaleCortAdmin
```


```{r}
flexSave(
  "figMaleCortAdmin"
  , plot = figMaleCortAdmin
  , width = twoCols
  , height = fullLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Mass count 

```{r}
tbl <- maleMassCortAM_counts_flexTable 
tbl
tbl <- maleMassCortPM_counts_flexTable
tbl
```

## mass LMM

```{r}
tbl <- male_dosage_RelPM_flexTable
tbl
```

```{r}
tableCaption <- "Statistics from linear mixed models of male masses on day of vehicle (0mg/kg) or corticosterone (2mg/kg) treatment. Data were fit with the formula `feature ~ dosage + (1 | dam)`."
```

```{r}
maleCortAdmin_mass_lmm_num <- "4-7"
tableNum <- maleCortAdmin_mass_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Cort count

```{r}
tbl <- malesCortAdmin_cortCount_flexTable
tbl
```

## Cort LMM 

```{r}
tbl <- maleCortAdmin_cort_flexTable
tbl
```

```{r}
maleCortAdmin_cort_formula <-  getLMMFormula(maleCortAdmin_cort_lmm)

tableCaption <- paste0("Statistics for serum corticosterone in males with vehicle or corticosterone administration. Data were fit with the linear mixed model equation `", maleCortAdmin_cort_formula, "`.")
```
```{r}
malesCortAdmin_cortLMM_num <- "4-8"
tableNum <- malesCortAdmin_cortLMM_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 5 - LH
```{r}
figLH_left <- align_plots(
  figLH_diAfternoon
  , figLH_samplingTime
  , align = "v"
  , axis = "l"
)

figLH <- plot_grid(
  plot_grid(
    figLH_left[[1]]
    , figLH_samplingMax
    , figLH_samplingSurged
    , align = "h"
    , axis = "tb"
    , labels = c("A", "B", "C")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , nrow = 1
  )
  , figLH_left[[2]]
  , nrow = 2
  , labels = c("", "D")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , rel_heights = c(1.2, 1)
)

figLH

```


```{r}
flexSave(
  "figLH"
  , plot = figLH
  , width = twoCols
  , height = twoThirdsLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Count

```{r}
tbl <- LHCount_flexTable
tbl
```


## Di LMM
```{r}
tbl <- LH_diAfternoon_flexTable
tbl
```


```{r}
tableCaption <- "Statistics from linear mixed models of average afternoon (2.5h before lights out and at lights out) LH on day of adult treatment in diestrous females. Data were fit with the formula `average LH ~ early-life treatment * adult treatment + (1 | dam)`."
```

```{r}
LH_di_lmm_num <- "5-1"
tableNum <- LH_di_lmm_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## Prop surged 

```{r}
summary(propSurged_extendedSampling_glmm$full_model)

propSurged_extendedSampling_glmm
```

# Figure 6 - GABA PSCs - passives

```{r}
figGABA1stRow <- plot_grid(
  figGABAa_model
  , figGABAb_model
  , figGABAc_model
  , figGABAd_model
  , ncol = 4
  , labels = c("A", "B", "C", "D")
  , label_fontfamily = "Arial"
  , label_size = textSize
  , align = "vh"
  , axis = "lrtb"
)

figGABA <- figGABA1stRow

figGABA
```

```{r}
flexSave(
  "figGABA"
  , plot = figGABA
  , width = twoCols
  # , height = 28/2
  , height = halfLength
  , units = "cm"
  , filePath = manuscriptFolder
)
```

## Count 
Not making table for paper

```{r}
tbl <- GABApsc_cellCounts_flexTable
tbl
```

## LMMs
```{r}
tbl <- pscLMMs_flexTable
tbl
```


```{r}
tableCaption <- "Statistics from linear mixed models of electrophysiology properties on day of adult treatment. The mean value for each cell was calculated, and data were fit with the formula `feature ~ early-life treatment * adult treatment + (1 | dam) + (1 | mouseID)`."
```

```{r}
psc_LMM_num <- "6-1"
tableNum <- psc_LMM_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

## # of events

```{r}
tbl <- numEvents_nb.GLMM_Anova_flexTable
tbl
```

```{r}
numEvents_formula <-  getLMMFormula(numEvents_nb.GLMM_sum)

numEvents_formula <- gsub("numEvents", "# events per 240s", numEvents_formula)

tableCaption <- paste0("Statistics for number of post-synaptic current (PSC) events per 240s in GnRH neurons on the day of adult treatment. As the frequency data were skewed right and included zeros, a generalized linear mixed effects negative binomial model was used. Data were fit with the model equation `", numEvents_formula, "`. The joint_tests function of the emmeans package was used to obtain these p-value estimates from the model." )
```

```{r}
numEvents_GLMM_num <- "7-1"
tableNum <- numEvents_GLMM_num
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```

# Figure 7 - PSC properties

```{r}
figGABA2_left <- align_plots(
  figGABA_freq_model
  , bootstrapRes_iterations5000_maxPerCellNone_interval$errorPlots$interval +
    labs(
      y = "mean\n95%CI"
    ) +
    theme(
      axis.text.y = element_blank()
      , axis.title.y = element_text(angle = 90)
    )
  , bootstrapRes_iterations5000_maxPerCellNone_interval$cumulativeFreqPlots$interval +
    theme(
      legend.position = "none"
    )
  , align = "v"
  , axis = "l"
)

figGABA2_middle <- align_plots(
  figGABA_amp_model
  , bootstrapRes_iterations5000_maxPerCellNone_amplitude$errorPlots$amplitude +
    labs(
      y = "mean\n95%CI"
    ) +
    theme(
      axis.text.y = element_blank()
      , axis.title.y = element_text(angle = 90)
  )
  , bootstrapRes_iterations5000_maxPerCellNone_amplitude$cumulativeFreqPlots$amplitude +
    theme(
      legend.position = "none"
    )
  , align = "v"
  , axis = "l"
)

figGABA2 <- plot_grid(
  plot_grid(
    # figGABA_freq_model
    figGABA2_left[[1]]
    , figGABA_int_model
    , figGABA2_middle[[1]]
    , figGABA_decayTime_model
    , nrow = 1
    , labels = c("C", "D", "E", "F")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , align = "h"
    , axis = "tb"
  )
  , plot_grid(
     figGABA2_left[[2]]
    , figGABA2_middle[[2]]
    , labels = c("G", "H")
    , label_fontfamily = "Arial"
    , label_size = textSize
    , align = "h"
    , axis = "tb"
    , nrow = 1
  )
  , plot_grid(
    figGABA2_left[[3]]
    , figGABA2_middle[[3]]
    , nrow = 1
    , align = "h"
    , axis = "tb"
  )
  , nrow = 3
  , rel_heights = c(2.2, 1, 2)
)

figGABA2 <- ggdraw() +
  draw_plot(
    figGABA2
  ) +
  draw_plot(
    bootstrapRes_iterations5000_maxPerCellNone_interval$cumulativeFreqPlots_full$interval +
      theme(
        legend.position = "none"
        , axis.title.x = element_blank()
        , axis.title.y = element_blank()
      )
    , x = 0.25
    , y = 0.075
    , width = 0.25
    , height = 0.2
  ) +
  draw_plot(
    bootstrapRes_iterations5000_maxPerCellNone_amplitude$cumulativeFreqPlots_full$amplitude +
      theme(
        legend.position = "none"
        , axis.title.x = element_blank()
        , axis.title.y = element_blank()
      )
    , x = 0.75
    , y = 0.075
    , width = 0.25
    , height = 0.2
  )

figGABA2
```


```{r}
flexSave(
  "figPSC_props"
  , plot = figGABA2
  , width = twoCols
  , height = 12.3
  , units = "cm"
  , filePath = manuscriptFolder
)
```


```{r}
tbl <- psc_pairwisePs_flexTable
tbl
```

```{r}
psc_pairwiseNum <- "7-2"
tableNum <- psc_pairwiseNum
```

```{r}
doc <- addTableAndCaptionToDoc(tbl, tableCaption, tableNum, doc)
```



